### 2017-11-12 cs6735/project/draft.tex
init draft

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}

\title{Generative Adversarial Networks}
\author{Jacob Smith}
\date{December 12, 2017}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}
\maketitle

\begin{abstract}
    General Adversarial Networks have
\end{abstract}

\section{Introduction}
Deep learning have made astounding progress within the past decade. Discriminative models have recently surpassed the abilities of human within the domain of pattern recognition \citep{2014arXiv1404.7828S}. These successes can attributed to vast, high dimension datasets in conjunction with large neural networks using linear activation functions, dropout regularization techniques and backpropagation to update the parameters \citep{2014arXiv1406.2661G}. However, deep learning posses many more ambitious goals. Until recently, success has mostly been seen with supervised classifiers; however, deep generative now competitively rival their discriminative counterpartsdfs.

Generative models learn the joint probability distribution $p(x,y)$ of an input $x$ and label $y$ whereas discriminative models directly learn the conditional probability $p{y|x}$. Knowledge of the probability distribution is created both explicitly and implicitly \citep{Goodfellow-et-al-2016}. Those which do not directly model a probability distribution offer mechanisms which require implicit knowledge of the underlying distribution, such as creating a sample from that distribution \citep{Goodfellow-et-al-2016}. Generative models may be used as classifiers using Bayes rules to calculate $p(x,y)$ \citep{NIPS2001_2020}.

\begin{figure}[h!]
\centering
\includegraphics[scale=1.7]{pdf.jpg}
\caption{The process density estimation of one-dimensional data and a Gaussian distribution \citep{2017arXiv170100160G}. Generative models take a dataset $D$, sourced from a distribution $p_data$, a create an estimate of that distribution $p_model$.}
\label{fig:pdf}
\end{figure}

\section{Conclusion}
Generative Adversarial Networks

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2017-11-12 cs6735/project/draft.tex
finished a few paragraphs

@@
 \usepackage{graphicx}
+
+\usepackage{parskip}
+
+\graphicspath{{./img/}}
 
@@
 These successes can attributed to vast, high dimension datasets in conjunction with large neural networks using linear activation functions, dropout regularization techniques and backpropagation to update the parameters \citep{2014arXiv1406.2661G}.
-However, deep learning posses many more ambitious goals.
-Until recently, success has mostly been seen with supervised classifiers; however, deep generative now competitively rival their discriminative counterpartsdfs.
+However, deep learning possesses many more ambitious goals.
+Until recently, success has mostly been seen with supervised classifiers; however, deep generative models now competitively rival their discriminative counterparts.
 
-Generative models learn the joint probability distribution $p(x,y)$ of an input $x$ and label $y$ whereas discriminative models directly learn the conditional probability $p{y|x}$.
-Knowledge of the probability distribution is created both explicitly and implicitly \citep{Goodfellow-et-al-2016}.
+Generative models learn the joint probability distribution $p(x,y)$ of an input $x$ and label $y$ whereas discriminative models directly learn the conditional probability $p(y|x)$.
+Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(x,y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
+Depending on the model, knowledge of the probability distribution can be created both explicitly and implicitly \citep{Goodfellow-et-al-2016}.
 Those which do not directly model a probability distribution offer mechanisms which require implicit knowledge of the underlying distribution, such as creating a sample from that distribution \citep{Goodfellow-et-al-2016}.
-Generative models may be used as classifiers using Bayes rules to calculate $p(x,y)$ \citep{NIPS2001_2020}.
+As humans, we are able to understand the world around us with tremendous precision.
+It is easy to underestimate the complexity of the data we process to accomplish this feat.
+Although progress within the machine learning field is rapidly advancing, computers still have limited understanding of the data the process.
+Generative models, especially deep generative models, offer promising results towards this goal \citep{genmodelingopenai}.
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\includegraphics[scale=1.7]{pdf.jpg}
+\includegraphics[scale=0.7]{pdf}
 \caption{The process density estimation of one-dimensional data and a Gaussian distribution \citep{2017arXiv170100160G}.
-Generative models take a dataset $D$, sourced from a distribution $p_data$, a create an estimate of that distribution $p_model$.}
+Generative models take a dataset $D$, sourced from a distribution $p_{data}$, a create an estimate of that distribution $p_{model}$.}
 \label{fig:pdf}
@@
 
+The process of training a generative model is very similar to a discriminative model.
+Using large amounts of data collected from a specific domain, we train the model to generate data from that domain.
+As these models have fewer parameters than that the number of data samples, they are forced to internalize some representation of the data.
+Although, unlike supervised training, there exists no explicit desired output.
+The problem becomes defining a cost function which forces the generative model to produce data more like that of the domain.
+
+Generative adversarial networks (GANs), first introduced in 2014, offer a new framework for estimating generative models with use of an adversarial process \citep{2014arXiv1406.2661G}.
+These models offer a clever approach to solving the aforementioned problem of explicitly defining a cost function.
+Rather than training a single model, a discriminator is introduced.
+These two networks are pitted against each other in a minimax game.
+The generative model $G$ attempts to produce data that resembles that of the training set while the discriminative model $D$ attempts to classify whether or not a sample was real of generated.
+To train this network, $G$ attempts to maximize the error rate of $D$ whereas $D$ attempts to minimize it.
+Backpropagation is used to update the parameters and to train each model.
+In the ideal case, $D$ is unable to distinguish the generated samples from the real samples and produces an error rate of $\frac{1}{2}$ \citep{2014arXiv1406.2661G}.
+
 \section{Conclusion}
-Generative Adversarial Networks
+Generative models are currently being applied to many problems \citep{genmodelingopenai}; however, they offer many more possibilities due to their ability to understand the data they are given.
 

### 2017-11-12 cs6735/project/draft.tex
finishe motivation sectin

@@
 \begin{abstract}
-    General Adversarial Networks have
+    Deep generative networks have often fallen short, especial when compared to discriminative models.
+Since their conception in 2014, generative adversarial networks have seen exponential growth in research.
+These networks offer promising results for both unsupervised learning and generative models.
+This research paper presents an overview of generative adversarial networks.
+Specifically, we will examine the motivation behind GANs, their theoretical justification, the current state of GANs and the research frontiers that have yet to be explored.
 \end{abstract}
@@
 
+\section{Motivations}
+There exists several compelling reasons for studying generative modeling \citep{2017arXiv170100160G}.
+These models are extremely useful when your goal is understand the underlying distribution parameters.
+For example, joint probability distributions of high dimensional data is relevant to both applied math and engineering \citep{2017arXiv170100160G}.
+Generative models are also applicable to reinforcement learning, particularly model-based learning algorithms.
+A time series generative model, one which predicts future states of an environment given the current state of the environment and an agents actions, are of particular interest \citep{2017arXiv170100160G}.
+An agent may learn the best action to take in a given scenario by querying this generative model and choosing the one which outputs the best state of the world.
+Furthermore, generative models, especially GANs, have recently excelled at semi-supervised learning.
+
+Proposed in the original GAN paper \citep{2014arXiv1406.2661G}, semi-supervised techniques used in conjunction with GANs have recently proven themselves as a reputable technique.
+The premise involves training the discriminator to classify images into $n + 1$ classes where $n$ is the number of class labels and the additional $1$ is the class of a fake image.
+This algorithm is able to obtain great performance on relatively small labeled datasets when compared to labeled datasets typically state of the art supervised algorithms \citep{2017arXiv170100160G}.
+Currently, the best performing semi-supervised GAN are feature matching GANs, where the new objective of the generative model is to minimize the distance between a layer $l$ of the discriminator \citep{2016arXiv160603498S}.
+
+Many applications require multi-modal outputs.
+For example, predicting the next action of a self-driving car.
+Within this context, it is important the model not be trained by traditional methods, such as using mean squared error to minimize the distance between the expected and predicted actions.
+These models cannot be used in situations where there is more than one appropriate prediction.
+Generative modeling, especially GAN, allow machine learning to function the scenarios where one input corresponds to multiple acceptable outputs \citep{2017arXiv170100160G}.
+
+Tasks which involve image generation, modification or translation are all highly applicable to generative models.
+Although GANs may be used to generate any type of data, images remain the most commonly used source of training data.
+Research conducted within the past three years demonstrates the capabilities of GANs to perform these tasks \citep{2017arXiv170100160G, 2016arXiv161102200T, 2014arXiv1411.1784M}.
+For example, GANs have recently been shown to be capable of translating aerial photographs into maps and sketches into realistic images \citep{2017arXiv170100160G}.
+
 \section{Conclusion}

### 2017-11-12 cs6735/project/draft.tex
init background section

@@
 
+When compared to other generative models, especially deep generative models, GANs possess several advantages... quicker? no Markov chains?
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.65]{img2img}
+\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
+This approach makes use of conditional generative adversarial networks to map image domains.}
+\label{fig:Image to Image Examples}
+\end{figure}
+
+\section{Background}
+
 \section{Conclusion}

### 2017-11-13 cs6735/project/draft.tex
updated background

@@
 \section{Background}
+Generative adversarial networks may use any differentiable functions for the models; however, the optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
+We first define a vector $z$ such that $z~p_z(z)$.
+This vector becomes the argument of the generator $G(z;\theta_g)$ where $G$ is a differentiable funciton and $\theta_g$ is its parameters.
+Another differentiable function $D(x;\theta_d)$ for the discriminator.
+This function takes as input a vector $x$, either from the output of $G$ or a sample from the training set, and is parameratized by $\theta_d$.
+The output of the discriminator is a scaler number representating the probability that the arguments were derived from the training data.
+In this situation, there exists a minimax game where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize $\log(1-D(G(z)))$.
+
+$$\min{G}\max{D}V(D, G) = \mathbb{E}_{x~p_{data}(x)}[\log(D(x))] + \mathbb{E}_{z~p_z(z)}[\log(1-D(G(z)))]$$
 

### 2017-11-13 cs6735/project/draft.tex
updated background

@@
 
+In this minimax version of the loss functions, the generator suffers from a vanishing gradient when the descriminator confidently rejects the generated data.
+The initial solution proposed by Goodfellow was to train the generator to maximize $log(D(G(z)))$ rather than minimize $log(1-D(G(z)))$ \citep{2014arXiv1406.2661G}; however, even this new cost function does not completly remove the gradients problems \citep{2017arXiv170104862A}.
+
 \section{Conclusion}

### 2017-11-13 cs6735/project/draft.tex
add algorithm

--- 2017-11-12 cs6735/project/draft.tex
@@
 \usepackage{graphicx}
-
+\usepackage[options ]{algorithm2e}
 \usepackage{parskip}
@@
 \section{Background}
+hello
+
+\begin{algorithm}[H]
+  \SetAlgoLined
+  \Input{$n$: The number of training iterations} \linebreak
+  \Input{$k$: The number of discriminator iterations} \linebreak
+  \For{training iteration in n} {
+    \For{discriminator iteration in k} {
+      sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
+      sample $m$ vectors $\{x^{(1)},...,x^{(m)}\}$ from the training samples\;
+      update the discriminator using its stochastic gradient
+      $$\nabla_{\theta_d}\frac{1}{m}\sum_{i=1}^{m}[\log(D(x^{(i)}))+\log(1-D(G(z^{(i)})))]$$
+    }
+    sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
+    update the generator using its stochastic gradient\;
+    $$\nabla_{\theta_g}\frac{1}{m}\sum_{i=1}^{m}[\log(1-D(G(z^{(i)})))]$$
+  }
+  \caption{The initial generative adversarial network algorithm developed by Goodfellow \textit{et al.} in 2014 \citep{2014arXiv1406.2661G}.
+Multiple variations of this algorithm have since been produced.
+One of the benefits of adversarial networks is that they may be updated using regular gradient descent.}
+\end{algorithm}
+
+This algorithm presents the initial training algorithm used by Goodfellow \textit{et al.} when GANs were introduced in 2014 \citep{2014arXiv1406.2661G}.
+Many modifications have been made by various sources.
+The first step in the algorithm is to optimize the discriminator $D$.
+Optimally, one would train $D$ to completion; however, this is unrealistic in practice.
+The number of discriminator training iterations becomes a hyperparameter of the algorithm.
+For the initial GAN experiments, this number was set to $1$ to reduce computation time.
+
+\section{Issues}
+Generative adversarial networks are often characterized by their instability. The training process of
+
+Shape, count, orientation
+
+\section{Improvements}
+
+\section{Model Variations}
+
+\section{Research Frontiers}
 

### 2017-11-14 cs6735/project/draft.tex

@@
 \section{Background}
-hello
+Generative adversarial networks may use any differentiable functions for the models; however, the optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
+We first define a vector $z$ such that $z~p_z(z)$.
+This vector becomes the argument of the generator $G(z;\theta_g)$ where $G$ is a differentiable funciton and $\theta_g$ is its parameters.
+Another differentiable function $D(x;\theta_d)$ for the discriminator.
+This function takes as input a vector $x$, either from the output of $G$ or a sample from the training set, and is parameratized by $\theta_d$.
+The output of the discriminator is a scaler number representating the probability that the arguments were derived from the training data.
+In this situation, there exists a minimax game where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize $\log(1-D(G(z)))$.
+
+$$\min{G}\max{D}V(D, G) = \mathbb{E}_{x~p_{data}(x)}[\log(D(x))] + \mathbb{E}_{z~p_z(z)}[\log(1-D(G(z)))]$$
+
+In this minimax version of the loss functions, the generator suffers from a vanishing gradient when the descriminator confidently rejects the generated data.
+The initial solution proposed by Goodfellow was to train the generator to maximize $log(D(G(z)))$ rather than minimize $log(1-D(G(z)))$ \citep{2014arXiv1406.2661G}; however, even this new cost function does not completly remove the gradients problems \citep{2017arXiv170104862A}.
 

### 2017-11-14 cs6735/project/draft.tex
added plan to draft
update background

--- 2017-11-13 cs6735/project/draft.tex
@@
 \section{Background}
-hello
+Generative adversarial networks may use any differentiable functions for the models; however, the optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
+We first define a vector $z$ such that $z~p_z(z)$.
+This vector becomes the argument of the generator $G(z;\theta_g)$ where $G$ is a differentiable function and $\theta_g$ is its parameters.
+Another differentiable function $D(x;\theta_d)$ for the discriminator.
+This function takes as input a vector $x$, either from the output of $G$ or a sample from the training set, and is parametrized by $\theta_d$.
+The output of the discriminator is a scalar number representation the probability that the arguments were derived from the training data.
+In this situation, there exists a minimax game where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize $\log(1-D(G(z)))$.
+The networks $G$ and $D$ play a minimax game with the value function $V(D,G)$:
+
+$$\min_{G}\max_{D}V(D, G) = \mathbb{E}_{x\sim p_{data}(x)}[\log(D(x))] + \mathbb{E}_{z\sim p_z(z)}[\log(1-D(G(z)))]$$
+
+For the training step, any variant of gradient descent may be used with respect to the individual cost functions \citep{2017arXiv170100160G}.
+The first updates $\theta_D$ while attempting to minimize the discriminator cost function $J_D$ while the other updates $\theta_G$ while attempting to minimize the generator cost function $J_G$.
+There exist several variations of the cost function that may be used for training purposes; however, the discriminator cost has remained the same for each.
+
+$$J_d(\theta_D,\theta\G) = -\frac{1}{2}\mathbb{E}_{x\sim p_{data}(x)}[\log(D(x))] - \frac{1}{2}\mathbb{E}_{z\sim p_{z}(z)}[\log(1-D(G(z)))]$$
+
+This is a standard cross entropy cost function that is trained on two minibatches, one from the dataset and one from the generator.
+For this to become a zero-sum game, a minimax game, the cost function of the generator is simply the negation of the discriminator.
+
+$$J_g(\theta_D,\theta\G) = -J_d(\theta_D,\theta\G)$$
+
+This version of the generator loss function is particularly useful for theoretical analysis as shown in the first GAN paper \citep{2014arXiv1406.2661G}.
+It can be shown that the minimax game is the same as minimizing the Jensen-Shannon divergence and that each player will eventually converge if both players are able to directly update the function space as oppose to the parameters within a neural network \citep{2017arXiv170100160G}.
+However, in this minimax version, the loss function of the generator suffers from a vanishing gradient when the discriminator confidently rejects the generated data.
+The solution proposed by Goodfellow is to train the generator to maximize $log(D(G(z)))$ rather than minimize $log(1-D(G(z)))$ \citep{2014arXiv1406.2661G}.
+This function is heuristically motivated as to provide strong gradients when either the generator or discriminator is not functioning optimally.
+
+$$J_g(\theta_D,\theta\G) = -\frac{1}{2}\mathbb{E}_{z\sim p_{z}(z)}[\log(D(G(z)))]$$
 
@@
 For the initial GAN experiments, this number was set to $1$ to reduce computation time.
+The preferable value for this hyperparameter is still largely debated amongst researchers \citep{2017arXiv170100160G}.
 
@@
 \section{Improvements}
+Feature matching
 
 \section{Model Variations}
+Deep Convolutional GAN
+
+Wasserstein GAN to improve stability
+
+Reccurent GAN
+
+Conditinal GAN
+
+Growing GANs
 
 \section{Research Frontiers}
+GANs are an exciting idea that are currently leading the frontier of deep generative models.
+
+Hiton's Capsule Network
+
+Improving the stability of GANs
 

### 2017-11-14 cs6735/project/draft.tex
added a bit to the paper

@@
 
+Maximum likelihood learning is another option for training GANs \citep{2017arXiv170100160G}.
+In this situation, we would be minimizing the Kullback-Leibler divergence between $p_{data}$ and $p_{model}$.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.65]{costfunc}
+\caption{The cost of the generator................}
+\label{fig:Image to Image Examples}
+\end{figure}
+
+This following algorithm presents initial training algorithm used by Goodfellow \textit{et al.} when GANs were introduced in 2014 \citep{2014arXiv1406.2661G}.
+Many modifications have been made by various sources.
+The first step in the algorithm is to optimize the discriminator $D$.
+Initially, many thought it would be optimal to train $D$ to completion; however, as previously mentioned, this is still a controversial topic among researchers \citep{2017arXiv170100160G}.
+For the initial GAN experiments, this number was set to $1$ to reduce computation time.
+
 \begin{algorithm}[H]
@@
 Multiple variations of this algorithm have since been produced.
-One of the benefits of adversarial networks is that they may be updated using regular gradient descent.}
+One of the benefits of adversarial networks is that they may be updated using back propogation.}
 \end{algorithm}
-
-This algorithm presents the initial training algorithm used by Goodfellow \textit{et al.} when GANs were introduced in 2014 \citep{2014arXiv1406.2661G}.
-Many modifications have been made by various sources.
-The first step in the algorithm is to optimize the discriminator $D$.
-Optimally, one would train $D$ to completion; however, this is unrealistic in practice.
-The number of discriminator training iterations becomes a hyperparameter of the algorithm.
-For the initial GAN experiments, this number was set to $1$ to reduce computation time.
-The preferable value for this hyperparameter is still largely debated amongst researchers \citep{2017arXiv170100160G}.
 

### 2017-11-18 cs2383/assignment2/MergeSort.java
finished merge sort

@@ -1,0 +1,57 @@
+public class MergeSort {
+  public static void main(String[] args) {
+    int[] A = {3, 6, 10, 18, 8, 7, 25, 40};
+    int[] B;
+    B = A;
+    sort(A);
+    show(A); // display the sorted result A
+  }
+
+  public static void sort(int[] A) {
+    mergeSort(A);
+  }
+
+  public static void mergeSort(int[] A) {
+    if(A.length == 1) return;
+    int[] A1 = new int[A.length/2];
+    int[] A2 = new int[A.length/2 + A.length%2];
+    System.arraycopy(A, 0, A1, 0, A1.length);
+    System.arraycopy(A, A.length/2, A2, 0, A2.length);
+    mergeSort(A1);
+    mergeSort(A2);
+    merge(A, A1, A2);
+  }
+
+  public static void merge(int[] A, int[] A1, int[] A2) {
+    int i = 0;
+    int j = 0;
+    while(i < A1.length && j < A2.length) {
+      if(A1[i] < A2[j]) {
+        A[i+j] = A1[i];
+        i++;
+      } else {
+        A[i+j] = A2[j];
+        j++;
+      }
+    }
+
+    for(int k = i; k < A1.length; k++) {
+      A[k+j] = A1[k];
+    }
+    for(int k = j; k < A2.length; k++) {
+      A[i+k] = A2[k];
+    }
+  }
+
+  public static void show(int[] A) {
+    for(int i = 0; i < A.length; i++) {
+      System.out.print(A[i]);
+      if(i != A.length-1) {
+        System.out.print(", ");
+      } else {
+        System.out.println();
+      }
+    }
+  }
+
+}

### 2017-11-18 cs2383/assignment2/HeapSort.java
finished heapsort

@@ -1,0 +1,65 @@
+public class HeapSort {
+  public static void main(String[] args) {
+    int[] A = {3, 6, 10, 18, 8, 7, 25, 40};
+    int[] B;
+    B = A;
+    sort(A);
+    show(A); // display the sorted result A
+  }
+
+  public static void sort(int[] A) {
+    for(int i = A.length-1; i >= 0; i--) {
+      heapify(A, 0, i+1);
+      swap(A, 0, i);
+    }
+  }
+
+  public static void heapify(int[] A, int i, int n) {
+    int i1 = i*2+1;
+    int i2 = i*2+2;
+
+    if(i1 < n) heapify(A, i1, n);
+    if(i2 < n) heapify(A, i2, n);
+    siftDown(A, i, n);
+  }
+
+  public static void siftDown(int[] A, int i, int n) {
+    int i1 = i*2+1;
+    int i2 = i*2+2;
+
+    if(n <= i2) {
+      return;
+    } else if(n <= i1) {
+      if(A[i] < A[i1]) {
+        swap(A, i, i1);
+      }
+      return;
+    }
+
+    if(A[i1] > A[i2] && A[i1] > A[i]) {
+      swap(A, i, i1);
+      siftDown(A, i1, n);
+    } else if(A[i2] > A[i]) {
+      swap(A, i, i2);
+      siftDown(A, i2, n);
+    }
+  }
+
+  public static void swap(int[] A, int i, int j) {
+    int t = A[i];
+    A[i] = A[j];
+    A[j] = t;
+  }
+
+  public static void show(int[] A) {
+    for(int i = 0; i < A.length; i++) {
+      System.out.print(A[i]);
+      if(i != A.length-1) {
+        System.out.print(", ");
+      } else {
+        System.out.println();
+      }
+    }
+  }
+
+}

### 2017-11-18 cs2383/assignment2/MergeSort.java

@@ -8,17 +8,13 @@ public class MergeSort {
   }
 
   public static void sort(int[] A) {
-    mergeSort(A);
-  }
-
-  public static void mergeSort(int[] A) {
     if(A.length == 1) return;
     int[] A1 = new int[A.length/2];
     int[] A2 = new int[A.length/2 + A.length%2];
     System.arraycopy(A, 0, A1, 0, A1.length);
     System.arraycopy(A, A.length/2, A2, 0, A2.length);
-    mergeSort(A1);
-    mergeSort(A2);
+    sort(A1);
+    sort(A2);
     merge(A, A1, A2);
   }
 

### 2017-11-18 cs2383/assignment2/CheckBST.java
finished q2, q3 for a2

@@ -1,0 +1,69 @@
+public class CheckBST {
+  public static void main(String[] args) {
+    Node[] nodes1 = new Node[8];
+    nodes1[1] = new Node(1, 13, 0, 2, 3);
+    nodes1[2] = new Node(2, 10, 1, 0, 4);
+    nodes1[3] = new Node(3, 19, 1, 5, 0);
+    nodes1[4] = new Node(4, 12, 2, 0, 0);
+    nodes1[5] = new Node(5, 15, 3, 6, 7);
+    nodes1[6] = new Node(6, 14, 5, 0, 0);
+    nodes1[7] = new Node(7, 18, 5, 0, 0);
+
+    Node[] nodes2 = new Node[8];
+    nodes2[1] = new Node(1, 12, 0, 2, 3);
+    nodes2[2] = new Node(2, 10, 1, 0, 4);
+    nodes2[3] = new Node(3, 19, 1, 5, 0);
+    nodes2[4] = new Node(4, 13, 2, 0, 0);
+    nodes2[5] = new Node(5, 15, 3, 6, 7);
+    nodes2[6] = new Node(6, 14, 5, 0, 0);
+    nodes2[7] = new Node(7, 18, 5, 0, 0);
+
+    System.out.println("Min value of Trees: " + minValue(nodes1, nodes1[1]));
+    System.out.println("Max value of Trees: " + maxValue(nodes1, nodes1[1]));
+
+    System.out.println("Tree one is a BST: " + isBST(nodes1, nodes1[1]));
+    System.out.println("Tree two is a BST: " + isBST(nodes2, nodes2[1]));
+  }
+
+  public static boolean isBST(Node[] nodes, Node root) {
+    if(root == null) return true;
+
+    Node left = nodes[root.left];
+    if(root.data < maxValue(nodes, left)) return false;
+    if(!isBST(nodes, left)) return false;
+
+    Node right = nodes[root.right];
+    if(root.data > minValue(nodes, right)) return false;
+    if(!isBST(nodes, right)) return false;
+
+    return true;
+  }
+
+  public static int minValue(Node[] nodes, Node root) {
+    if(root == null) return 100000000;
+
+    int minRight = minValue(nodes, nodes[root.right]);
+    int minLeft = minValue(nodes, nodes[root.left]);
+    if(minLeft < minRight && minLeft < root.data) {
+      return minLeft;
+    } else if(minRight < root.data) {
+      return minRight;
+    } else {
+      return root.data;
+    }
+  }
+
[…]

### 2017-11-18 cs2383/assignment2/Node.java

@@ -1,0 +1,15 @@
+public class Node {
+  int id;
+  int data;
+  int parent;
+  int left;
+  int right;
+
+  public Node(int id, int data, int parent, int left, int right) {
+    this.id = id;
+    this.data = data;
+    this.parent = parent;
+    this.left = left;
+    this.right = right;
+  }
+}

### 2017-11-18 cs2383/assignment2/QuickSort.java

@@ -1,0 +1,56 @@
+public class QuickSort {
+  public static void main(String[] args) {
+    int[] A = {3, 6, 10, 18, 8, 7, 25, 40};
+    int[] B;
+    B = A;
+    sort(A);
+    show(A); // display the sorted result A
+  }
+
+  public static void sort(int[] A) {
+    quickSort(A, 0, A.length);
+  }
+
+  public static void quickSort(int[] A, int s, int e) {
+    if(e-s <= 1) {
+      return;
+    }
+
+    int partition = partition(A, 0, e);
+    quickSort(A, s, partition);
+    quickSort(A, partition+1, e);
+  }
+
+  public static int partition(int[] A, int s, int e) {
+    int pivot = A[e-1];
+
+    int j = 0; // index to place next value
+    for(int i = s; i < e-1; i++) {
+      if(A[i] <= pivot) {
+        swap(A, i, j);
+        j++;
+      }
+    }
+    swap(A, j, e-1);
+
+    return j;
+  }
+
+  public static void swap(int[] A, int i, int j) {
+    int t = A[i];
+    A[i] = A[j];
+    A[j] = t;
+  }
+
+  public static void show(int[] A) {
+    for(int i = 0; i < A.length; i++) {
+      System.out.print(A[i]);
+      if(i != A.length-1) {
+        System.out.print(", ");
+      } else {
+        System.out.println();
+      }
+    }
+  }
+
+}

### 2017-11-18 cs2383/assignment2/TreeOrder.java

@@ -1,0 +1,46 @@
+public class TreeOrder {
+  public static void main(String[] args) {
+    Node[] nodes = new Node[8];
+    nodes[1] = new Node(1, 12, 0, 2, 3);
+    nodes[2] = new Node(2, 10, 1, 0, 4);
+    nodes[3] = new Node(3, 19, 1, 5, 0);
+    nodes[4] = new Node(4, 13, 2, 0, 0);
+    nodes[5] = new Node(5, 15, 3, 6, 7);
+    nodes[6] = new Node(6, 14, 5, 0, 0);
+    nodes[7] = new Node(7, 18, 5, 0, 0);
+
+    System.out.println("--- Pre Order ---");
+    preOrder(nodes[1], nodes);
+
+    System.out.println("\n--- In Order ---");
+    inOrder(nodes[1], nodes);
+
+    System.out.println("\n--- Post Order ---");
+    postOrder(nodes[1], nodes);
+    //postOrder(nodes[1], nodes);
+  }
+
+  public static void preOrder(Node root, Node[] nodes) {
+    if(root != null) {
+      System.out.println(root.data + " ");
+      preOrder(nodes[root.left], nodes);
+      preOrder(nodes[root.right], nodes);
+    }
+  }
+
+  public static void inOrder(Node root, Node[] nodes) {
+    if(root != null) {
+      inOrder(nodes[root.left], nodes);
+      System.out.println(root.data + " ");
+      inOrder(nodes[root.right], nodes);
+    }
+  }
+
+  public static void postOrder(Node root, Node[] nodes) {
+    if(root != null) {
+      postOrder(nodes[root.left], nodes);
+      postOrder(nodes[root.right], nodes);
+      System.out.println(root.data + " ");
+    }
+  }
+}

### 2017-11-20 cs2383/assignment2/HeapSort.java
slight change

@@ -8,9 +8,10 @@ public class HeapSort {
   }
 
   public static void sort(int[] A) {
+    heapify(A, 0, A.length);
     for(int i = A.length-1; i >= 0; i--) {
-      heapify(A, 0, i+1);
       swap(A, 0, i);
+      siftDown(A, 0, i);
     }
   }
 
@@ -27,21 +28,18 @@ public class HeapSort {
     int i1 = i*2+1;
     int i2 = i*2+2;
 
-    if(n <= i2) {
-      return;
-    } else if(n <= i1) {
-      if(A[i] < A[i1]) {
-        swap(A, i, i1);
-      }
-      return;
+    int max = i;
+    if(i1 < n && A[i1] > A[max]) {
+      i1 = max;
     }
 
-    if(A[i1] > A[i2] && A[i1] > A[i]) {
-      swap(A, i, i1);
-      siftDown(A, i1, n);
-    } else if(A[i2] > A[i]) {
-      swap(A, i, i2);
-      siftDown(A, i2, n);
+    if(i2 < n && A[i2] > A[max]) {
+      i2 = max;
+    }
+
+    if(i != max) {
+      swap(A, i, max);
+      siftDown(A, max, n);
     }
   }
 

### 2017-11-20 cs2383/assignment2/HeapSort.java
fixed heap bug

@@ -30,11 +30,11 @@ public class HeapSort {
 
     int max = i;
     if(i1 < n && A[i1] > A[max]) {
-      i1 = max;
+      max = i1;
     }
 
     if(i2 < n && A[i2] > A[max]) {
-      i2 = max;
+      max = i2;
     }
 
     if(i != max) {

### 2017-11-21 cs6735/assignment/report.tex
init assignment report

--- 2017-11-14 cs6735/project/draft.tex
@@
 
-\begin{abstract}
-    Deep generative networks have often fallen short, especial when compared to discriminative models.
-Since their conception in 2014, generative adversarial networks have seen exponential growth in research.
-These networks offer promising results for both unsupervised learning and generative models.
-This research paper presents an overview of generative adversarial networks.
-Specifically, we will examine the motivation behind GANs, their theoretical justification, the current state of GANs and the research frontiers that have yet to be explored.
-\end{abstract}
+\section{Introduction}
 
-\section{Introduction}
-Deep learning have made astounding progress within the past decade.
-Discriminative models have recently surpassed the abilities of human within the domain of pattern recognition \citep{2014arXiv1404.7828S}.
-These successes can attributed to vast, high dimension datasets in conjunction with large neural networks using linear activation functions, dropout regularization techniques and backpropagation to update the parameters \citep{2014arXiv1406.2661G}.
-However, deep learning possesses many more ambitious goals.
-Until recently, success has mostly been seen with supervised classifiers; however, deep generative models now competitively rival their discriminative counterparts.
+\section{Algorithms}
 
-Generative models learn the joint probability distribution $p(x,y)$ of an input $x$ and label $y$ whereas discriminative models directly learn the conditional probability $p(y|x)$.
-Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(x,y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
-Depending on the model, knowledge of the probability distribution can be created both explicitly and implicitly \citep{Goodfellow-et-al-2016}.
-Those which do not directly model a probability distribution offer mechanisms which require implicit knowledge of the underlying distribution, such as creating a sample from that distribution \citep{Goodfellow-et-al-2016}.
-As humans, we are able to understand the world around us with tremendous precision.
-It is easy to underestimate the complexity of the data we process to accomplish this feat.
-Although progress within the machine learning field is rapidly advancing, computers still have limited understanding of the data the process.
-Generative models, especially deep generative models, offer promising results towards this goal \citep{genmodelingopenai}.
+\section{Data}
 
-\begin{figure}
-\centering
-\includegraphics[scale=0.7]{pdf}
-\caption{The process density estimation of one-dimensional data and a Gaussian distribution \citep{2017arXiv170100160G}.
-Generative models take a dataset $D$, sourced from a distribution $p_{data}$, a create an estimate of that distribution $p_{model}$.}
-\label{fig:pdf}
-\end{figure}
+\section{Technical Details}
 
-The process of training a generative model is very similar to a discriminative model.
-Using large amounts of data collected from a specific domain, we train the model to generate data from that domain.
-As these models have fewer parameters than that the number of data samples, they are forced to internalize some representation of the data.
-Although, unlike supervised training, there exists no explicit desired output.
-The problem becomes defining a cost function which forces the generative model to produce data more like that of the domain.
+\section{Project Design}
 
-Generative adversarial networks (GANs), first introduced in 2014, offer a new framework for estimating generative models with use of an adversarial process \citep{2014arXiv1406.2661G}.
-These models offer a clever approach to solving the aforementioned problem of explicitly defining a cost function.
-Rather than training a single model, a discriminator is introduced.
-These two networks are pitted against each other in a minimax game.
-The generative model $G$ attempts to produce data that resembles that of the training set while the discriminative model $D$ attempts to classify whether or not a sample was real of generated.
-To train this network, $G$ attempts to maximize the error rate of $D$ whereas $D$ attempts to minimize it.
-Backpropagation is used to update the parameters and to train each model.
-In the ideal case, $D$ is unable to distinguish the generated samples from the real samples and produces an error rate of $\frac{1}{2}$ \citep{2014arXiv1406.2661G}.
-
-\section{Motivations}
-There exists several compelling reasons for studying generative modeling \citep{2017arXiv170100160G}.
-These models are extremely useful when your goal is understand the underlying distribution parameters.
-For example, joint probability distributions of high dimensional data is relevant to both applied math and engineering \citep{2017arXiv170100160G}.
-Generative models are also applicable to reinforcement learning, particularly model-based learning algorithms.
-A time series generative model, one which predicts future states of an environment given the current state of the environment and an agents actions, are of particular interest \citep{2017arXiv170100160G}.
-An agent may learn the best action to take in a given scenario by querying this generative model and choosing the one which outputs the best state of the world.
-Furthermore, generative models, especially GANs, have recently excelled at semi-supervised learning.
-
-Proposed in the original GAN paper \citep{2014arXiv1406.2661G}, semi-supervised techniques used in conjunction with GANs have recently proven themselves as a reputable technique.
-The premise involves training the discriminator to classify images into $n + 1$ classes where $n$ is the number of class labels and the additional $1$ is the class of a fake image.
-This algorithm is able to obtain great performance on relatively small labeled datasets when compared to labeled datasets typically state of the art supervised algorithms \citep{2017arXiv170100160G}.
-Currently, the best performing semi-supervised GAN are feature matching GANs, where the new objective of the generative model is to minimize the distance between a layer $l$ of the discriminator \citep{2016arXiv160603498S}.
-
-Many applications require multi-modal outputs.
-For example, predicting the next action of a self-driving car.
-Within this context, it is important the model not be trained by traditional methods, such as using mean squared error to minimize the distance between the expected and predicted actions.
-These models cannot be used in situations where there is more than one appropriate prediction.
-Generative modeling, especially GAN, allow machine learning to function the scenarios where one input corresponds to multiple acceptable outputs \citep{2017arXiv170100160G}.
-
-Tasks which involve image generation, modification or translation are all highly applicable to generative models.
-Although GANs may be used to generate any type of data, images remain the most commonly used source of training data.
-Research conducted within the past three years demonstrates the capabilities of GANs to perform these tasks \citep{2017arXiv170100160G, 2016arXiv161102200T, 2014arXiv1411.1784M}.
-For example, GANs have recently been shown to be capable of translating aerial photographs into maps and sketches into realistic images \citep{2017arXiv170100160G}.
-
-When compared to other generative models, especially deep generative models, GANs possess several advantages... quicker? no Markov chains?
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.65]{img2img}
-\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
-This approach makes use of conditional generative adversarial networks to map image domains.}
-\label{fig:Image to Image Examples}
-\end{figure}
-
-\section{Background}
-Generative adversarial networks may use any differentiable functions for the models; however, the optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
-We first define a vector $z$ such that $z~p_z(z)$.
-This vector becomes the argument of the generator $G(z;\theta_g)$ where $G$ is a differentiable funciton and $\theta_g$ is its parameters.
-Another differentiable function $D(x;\theta_d)$ for the discriminator.
-This function takes as input a vector $x$, either from the output of $G$ or a sample from the training set, and is parameratized by $\theta_d$.
-The output of the discriminator is a scaler number representating the probability that the arguments were derived from the training data.
-In this situation, there exists a minimax game where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize $\log(1-D(G(z)))$.
-
-$$\min{G}\max{D}V(D, G) = \mathbb{E}_{x~p_{data}(x)}[\log(D(x))] + \mathbb{E}_{z~p_z(z)}[\log(1-D(G(z)))]$$
-
-In this minimax version of the loss functions, the generator suffers from a vanishing gradient when the descriminator confidently rejects the generated data.
-The initial solution proposed by Goodfellow was to train the generator to maximize $log(D(G(z)))$ rather than minimize $log(1-D(G(z)))$ \citep{2014arXiv1406.2661G}; however, even this new cost function does not completly remove the gradients problems \citep{2017arXiv170104862A}.
-
-\begin{algorithm}[H]
-  \SetAlgoLined
-  \Input{$n$: The number of training iterations} \linebreak
-  \Input{$k$: The number of discriminator iterations} \linebreak
-  \For{training iteration in n} {
-    \For{discriminator iteration in k} {
-      sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
-      sample $m$ vectors $\{x^{(1)},...,x^{(m)}\}$ from the training samples\;
-      update the discriminator using its stochastic gradient
-      $$\nabla_{\theta_d}\frac{1}{m}\sum_{i=1}^{m}[\log(D(x^{(i)}))+\log(1-D(G(z^{(i)})))]$$
-    }
-    sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
-    update the generator using its stochastic gradient\;
-    $$\nabla_{\theta_g}\frac{1}{m}\sum_{i=1}^{m}[\log(1-D(G(z^{(i)})))]$$
-  }
-  \caption{The initial generative adversarial network algorithm developed by Goodfellow \textit{et al.} in 2014 \citep{2014arXiv1406.2661G}.
-Multiple variations of this algorithm have since been produced.
-One of the benefits of adversarial networks is that they may be updated using regular gradient descent.}
-\end{algorithm}
-
-This algorithm presents the initial training algorithm used by Goodfellow \textit{et al.} when GANs were introduced in 2014 \citep{2014arXiv1406.2661G}.
-Many modifications have been made by various sources.
-The first step in the algorithm is to optimize the discriminator $D$.
-Optimally, one would train $D$ to completion; however, this is unrealistic in practice.
-The number of discriminator training iterations becomes a hyperparameter of the algorithm.
-For the initial GAN experiments, this number was set to $1$ to reduce computation time.
-
-\section{Issues}
-Generative adversarial networks are often characterized by their instability. The training process of
-
-Shape, count, orientation
-
-\section{Improvements}
-
-\section{Model Variations}
-
-\section{Research Frontiers}
-
-\section{Conclusion}
-Generative models are currently being applied to many problems \citep{genmodelingopenai}; however, they offer many more possibilities due to their ability to understand the data they are given.
+\section{Results}
 

### 2017-11-21 cs6735/assignment/report.tex
updating assignment report

@@
 \section{Introduction}
+This report details the experimental study conducted for the CS6735 programming project.
+Six machine learning algorithms were implemented, including both regular and ensemble learning algorithms.
+Each was evaluated on five datasets from the UCI machine learning data repository using 10 times 5-fold cross validation.
+The technical details of the implementation will be described and the results will be analyzed.
 
 \section{Algorithms}
+For this study, six different algorithms; however, only the five unique algorithms are described in this section.
+Both the ID3 decision tree and Naïve Bayes algorithms were applied to the adaboost ensemble algorithm as weak learners.
+
+\subsection{ID3}
+\subsection{Naïve Bayes}
+\subsection{Adaboost}
+\subsection{Random Forest}
+\subsection{K-Nearest Neighbors}
 
 \section{Data}
+\subsection{Breast Cancer Data}
+\subsection{Car Data}
+Transformed to integer values
+
+\subsection{E. Coli Data}
+Removed categorical values
+
+\subsection{Letter Recognition Data}
+\subsection{Mushroom Data}
 
 \section{Technical Details}
+Identification information was removed ...
+No discretization was performed ...
+Unknown variables from the breast cancer dataset were replaced ...
+Limitations placed on trees ...
+Distributions used for Naïve Bayes ...
+C4.5 continuous variable implementation ...
+Number of trees for random forest ... & size of datasets
+Number of weak learners for adaboost ... & size of datasets
+How many neighbors ...
 
 \section{Project Design}
+A Java machine learning framework was first created ...
+The external dependencies include JUnit for unit tests and slfj4 for logging.
+Both work independently of the code written for the machine learning algorithms.
+They functioned as tools to write code and may be completely removed if necessary ...
+
+An `Algorithm` interface and `Model` abstract class were created as the high level objects that all algorithms and models implement.
+This abstraction proved extremely useful for ensemble implementation and general code cleanliness.
+The main class where the algorithms are implemented on the datasets is extremely easy to read.
+
+A `KFold` object was created which implements the cross validation algorithm. This object generates a `Report` on a given algorithm and dataset ...
+
+\subsection{Math Package}
+Data was particularly difficult to handle.
+Whereas Java is a statically typed language, difficulties arose in handling both floating point and integer values.
+To manage this, a math package was created which implements useful data structures such as vectors and matrices.
+These object were used to abstract away from the underlying data structures.
+Furthermore, the `Vector` object provided many useful methods for vector arithmetic such as element-wise multiplication, division and exponents.
+These methods also support broadcasting, where a vector can be multiplied by a single number.
+These objects are used throughout the library in place of primitive arrays and ArrayLists and have were essential to the code quality.
+Often, methods it was necessary to have two associated objects held in one data structure.
+For example, there exists a method within the DataSet object which splits itself into two parts based on a pivot point.
+This method would preferably return a pair of datasets; however, many common data structures such as arrays, lists and maps seemed did not seem to adequate.
+To accomplish this task, a simple Tuple data structure was created.
+
+Several other useful objects were implemented within the math package such as distance function objects, distribution objects and an object containing useful static methods.
+The purpose of these objects will be elaborated within Naïve Bayes package design section.
+The utility object implemented useful functions not available within the Java math package.
+
+\subsection{Decision Tree Package}
+
+\subsection{Naïve Bayes Package}
+\subsection{Ensemble Package}
+\subsection{Neighbors Package}
 
 \section{Results}
+table of results ...
+graph of hyperparameter search ...
 

### 2017-11-22 cs2383/assignment2/CheckBST.java
fixed BST

@@ -18,52 +18,22 @@ public class CheckBST {
     nodes2[6] = new Node(6, 14, 5, 0, 0);
     nodes2[7] = new Node(7, 18, 5, 0, 0);
 
-    System.out.println("Min value of Trees: " + minValue(nodes1, nodes1[1]));
-    System.out.println("Max value of Trees: " + maxValue(nodes1, nodes1[1]));
-
     System.out.println("Tree one is a BST: " + isBST(nodes1, nodes1[1]));
     System.out.println("Tree two is a BST: " + isBST(nodes2, nodes2[1]));
   }
 
   public static boolean isBST(Node[] nodes, Node root) {
+    return isBSTUtil(nodes, root, Integer.MIN_VALUE, Integer.MAX_VALUE);
+  }
+
+  public static boolean isBSTUtil(Node[] nodes, Node root, int min, int max) {
     if(root == null) return true;
 
-    Node left = nodes[root.left];
-    if(root.data < maxValue(nodes, left)) return false;
-    if(!isBST(nodes, left)) return false;
+    if(root.data <= min || root.data >= max) return false;
 
-    Node right = nodes[root.right];
-    if(root.data > minValue(nodes, right)) return false;
-    if(!isBST(nodes, right)) return false;
+    if(!isBSTUtil(nodes, nodes[root.left], min, root.data)) return false;
+    if(!isBSTUtil(nodes, nodes[root.right], root.data, max)) return false;
 
     return true;
-  }
-
-  public static int minValue(Node[] nodes, Node root) {
-    if(root == null) return 100000000;
-
-    int minRight = minValue(nodes, nodes[root.right]);
-    int minLeft = minValue(nodes, nodes[root.left]);
-    if(minLeft < minRight && minLeft < root.data) {
-      return minLeft;
-    } else if(minRight < root.data) {
-      return minRight;
-    } else {
-      return root.data;
-    }
-  }
-
-  public static int maxValue(Node[] nodes, Node root) {
-    if(root == null) return -100000000;
-
-    int maxRight = maxValue(nodes, nodes[root.right]);
-    int maxLeft = maxValue(nodes, nodes[root.left]);
-    if(maxLeft > maxRight && maxLeft > root.data) {
-      return maxLeft;
-    } else if(maxRight > root.data) {
-      return maxRight;
-    } else {
-      return root.data;
-    }
   }
 }

### 2017-11-22 cs2383/assignment2/TreeOrder.java

@@ -22,7 +22,7 @@ public class TreeOrder {
 
   public static void preOrder(Node root, Node[] nodes) {
     if(root != null) {
-      System.out.println(root.data + " ");
+      System.out.print(root.data + " ");
       preOrder(nodes[root.left], nodes);
       preOrder(nodes[root.right], nodes);
     }
@@ -31,7 +31,7 @@ public class TreeOrder {
   public static void inOrder(Node root, Node[] nodes) {
     if(root != null) {
       inOrder(nodes[root.left], nodes);
-      System.out.println(root.data + " ");
+      System.out.print(root.data + " ");
       inOrder(nodes[root.right], nodes);
     }
   }
@@ -40,7 +40,7 @@ public class TreeOrder {
     if(root != null) {
       postOrder(nodes[root.left], nodes);
       postOrder(nodes[root.right], nodes);
-      System.out.println(root.data + " ");
+      System.out.print(root.data + " ");
     }
   }
 }

### 2017-11-27 cs6735/project/draft.tex

@@
 \section{Issues}
-Generative adversarial networks are often characterized by their instability. The training process of
+There exist several issues that characterize generative adversarial networks.
+Some are related design of GANs or their underlying network implementations.
+These issues lay at the forfront of GAN research.
 
+\subsection{Instability}
+Generative adversarial networks are often characterized by their instability \citep{2017arXiv170100160G}.
+The training process makes use of gradient descent which does not guarentee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players.
+This is different than network optimization which is common in disciminative models.
+When each network trains, even if the specified network improves, the other may regress.
+This sometimes leads to the scenario where each network repeatadly undos the other's progress.
+This problem is not specific to GANs, but to any game situations \citep{2017arXiv170100160G}.
+It was shown in the first paper that congergenve was guarenteed if updates could be made to the function space, but no theoretical justification was been found that guarentees convergence within the parameter space \citep{2014arXiv1406.2661G}.
+However, there is no theoretical proof that that these games should not converge \citep{2017arXiv170100160G}.
+Typically, adversarial networks often oscilatte between different kinds of samples without converging to an equilibrium.
+
+\subsection{Mode Collapse}
+Mode collapse occurs when several different latent space vectors $z$ map to the similiar outputs.
+For example, the generator may create two images that only differ by colour but were generated with very different latent vectors.
+Full mode collpase is rare; however, partial mode collapse always occurs and varies by intensity.
+This occurs ...
+
+$$G^* = min_Gmax_DV(F, D)$$
+
+$$G^* = max_Dmin_GV(F, D)$$
+
+\subsection{Image Quality}
 Shape, count, orientation
 
-\section{Improvements}
-Feature matching
+\subsection{Evaluation}
+\subsection{Discrete Data}
 
 \section{Model Variations}
-Deep Convolutional GAN
+Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014.
+Significant improvements are being made with image quality and new applitcations are being found every month.
 
-Wasserstein GAN to improve stability
+\begin{figure}
+\centering
+\includegraphics[scale=0.65]{cumulative_gans}
+\caption{The cumulative amount of papers written about generative adversarial networks.
+The graph shows the exponential growth of GANs within the past three years.
+Image maintined by Avinash Hindipur \citep{November2017GANZoo}.}
+\label{fig:Cumulative Number of GAN papers by Month}
+\end{figure}
 
-Reccurent GAN
-
-Conditinal GAN
-
-Growing GANs
+\subsection{Deep Convolutional GANs}
+\subsection{Wasserstein GANs}
+\subsection{Conditional GANs}
+\subsection{Progrssive GANs}
 
@@
 
+\subsection{Divergence Measures}
+\subsection{Image Quality}
 Hiton's Capsule Network
+Progressive GANs
 
-Improving the stability of GANs
+\subsection{Semi-Supervised Learning}
+\subsection{Feature Learning}
+\subsection{Semi-Supervised Learning}
+\subsection{Reinforcement Learning}
 

### 2017-11-27 cs6735/project/draft.tex
continued report

@@
 Some are related design of GANs or their underlying network implementations.
-These issues lay at the forfront of GAN research.
+These issues lay at the forefront of GAN research.
 
@@
 Generative adversarial networks are often characterized by their instability \citep{2017arXiv170100160G}.
-The training process makes use of gradient descent which does not guarentee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players.
-This is different than network optimization which is common in disciminative models.
+The training process makes use of gradient descent which does not guarantee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players.
+This is different than network optimization which is common in discriminative models.
 When each network trains, even if the specified network improves, the other may regress.
-This sometimes leads to the scenario where each network repeatadly undos the other's progress.
+This sometimes leads to the scenario where each network repeatedly undo's the other's progress.
 This problem is not specific to GANs, but to any game situations \citep{2017arXiv170100160G}.
-It was shown in the first paper that congergenve was guarenteed if updates could be made to the function space, but no theoretical justification was been found that guarentees convergence within the parameter space \citep{2014arXiv1406.2661G}.
+It was shown in the first paper that convergence was guaranteed if updates could be made to the function space, but no theoretical justification was been found that guarantees convergence within the parameter space \citep{2014arXiv1406.2661G}.
 However, there is no theoretical proof that that these games should not converge \citep{2017arXiv170100160G}.
-Typically, adversarial networks often oscilatte between different kinds of samples without converging to an equilibrium.
+Typically, adversarial networks often oscillate between different kinds of samples without converging to an equilibrium in a phenomenon called mode collapse.
 
 \subsection{Mode Collapse}
-Mode collapse occurs when several different latent space vectors $z$ map to the similiar outputs.
+Mode collapse occurs when the generator collapses several different latent space vectors $z$ map to the same outputs.
+Full mode collapse is rare; however, partial mode collapse always occurs and varies by intensity.
 For example, the generator may create two images that only differ by colour but were generated with very different latent vectors.
-Full mode collpase is rare; however, partial mode collapse always occurs and varies by intensity.
-This occurs ...
+This occurs when the capacity of the generator is superior to that of the discriminator.
+Backpropagation does not necessarily follow the minimax game mentioned earlier and may behave like the maximin version.
 
-$$G^* = min_Gmax_DV(F, D)$$
+$$G^* = max_{D}min_{G}V(F, D)$$
 
-$$G^* = max_Dmin_GV(F, D)$$
+When this occurs, the generator attempts to map every latent vector to the one $x$ variable the discriminator is most likely to guess is real.
+When training, one can only hope the behavior resembles the minimax version.
+It is often speculated that the root cause of the issue the particular divergence measure used.
+Specifically, it is often asserted that mode collapse is caused by the use of Jenson-Shannon divergence; however, the use of Kullback-Leibler divergence has be shown to worsen the problem \citep{2017arXiv170100160G}.
+As mode collapse is currently an unavoidable reality for GANs, their applications are limited to situations where it is acceptable to generate only a small number of distant samples \citep{2017arXiv170100160G}.
+A potential solution to this problem is discussed in the following section.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.8]{modecollapse}
+\caption{An example of mode collapse as demonstrated by Metz \textit{et al.} \citep{2016arXiv161102163M}.
+The generated samples cluster around only one of the modes and do not spread out as they should.
+Throughout the training process, this cycle continues does not reach an equilibrium.}
+\label{fig:Mode Collapse Example}
+\end{figure}
 
 \subsection{Image Quality}
-Shape, count, orientation
+When generating images, problems often arise due to the generators difficulties with perspective, counting and structure \citep{2017arXiv170100160G}.
+For example, an generated animal may not have a 3D structure, have misplaced limbs or have too many of a specific body part.
+These issues arise due to the underlying model architecture and are not an inherent problem the adversarial network.
+Furthermore, generated image resolution has remained relatively low; however, recent improvements outlined in the following section show improvements with regard to resolution \citep{2017arXiv171010196K}.
 
 \subsection{Evaluation}
+The evaluation procedure for generative adversarial networks remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}.
+For example, models with high likelihood may produce poor samples and models with low likelihood may produce realistic samples.
+Several variations of the GANs examine the tradeoffs of divergence measures other than the original Kullback-Leibler divergence \citep{2015arXiv151101844T}.
+It can be shown that different metrics favor different models.
+Therefore, it is important to asses one's model within the context of the whole application \citep{2015arXiv151101844T}.
+
 \subsection{Discrete Data}
+
+\section{Improvements}
+
+\subsection{Mini-Batch Features}
 
@@
 Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014.
-Significant improvements are being made with image quality and new applitcations are being found every month.
+Significant improvements are being made with image quality and new applications are being found every month.
 
@@
 \centering
-\includegraphics[scale=0.65]{cumulative_gans}
+\includegraphics[scale=0.5]{cumulative_gans}
 \caption{The cumulative amount of papers written about generative adversarial networks.

### 2017-11-28 cs6735/project/draft.tex
continued report
updated cost

@@
 To train this network, $G$ attempts to maximize the error rate of $D$ whereas $D$ attempts to minimize it.
+The goal of the GAN algorithm is to reduce the distance between the data and generated probability distributions.
 Backpropagation is used to update the parameters and to train each model.
@@
 \centering
-\includegraphics[scale=0.65]{img2img}
+\includegraphics[scale=0.55]{img2img}
 \caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
-This approach makes use of conditional generative adversarial networks to map image domains.}
+This technique makes use of conditional generative adversarial networks to map across image domains.}
 \label{fig:Image to Image Examples}
@@
 
-$$\min_{G}\max_{D}V(D, G) = \mathbb{E}_{x\sim p_{data}(x)}[\log(D(x))] + \mathbb{E}_{z\sim p_z(z)}[\log(1-D(G(z)))]$$
+$$\min_{G}\max_{D}V(D, G) = \mathbb{E}_{x\sim p_{data}(x)}\Big[\log(D(x))\Big] + \mathbb{E}_{z\sim p_z(z)}\Big[\log(1-D(G(z)))\Big]$$
 
@@
 
-$$J_d(\theta_D,\theta\G) = -\frac{1}{2}\mathbb{E}_{x\sim p_{data}(x)}[\log(D(x))] - \frac{1}{2}\mathbb{E}_{z\sim p_{z}(z)}[\log(1-D(G(z)))]$$
+$$J^{(D)}(\theta_D,\theta\G) = -\frac{1}{2}\mathbb{E}_{x\sim p_{data}(x)}\Big[\log(D(x))\Big] - \frac{1}{2}\mathbb{E}_{z\sim p_{z}(z)}\Big[\log(1-D(G(z)))\Big]$$
 
 This is a standard cross entropy cost function that is trained on two minibatches, one from the dataset and one from the generator.
-For this to become a zero-sum game, a minimax game, the cost function of the generator is simply the negation of the discriminator.
+For this to become a zero-sum game, the cost function of the generator is simply the negation of the discriminator.
 
-$$J_g(\theta_D,\theta\G) = -J_d(\theta_D,\theta\G)$$
+$$J^{(G)}(\theta_D,\theta\G) = -J_d(\theta_D,\theta\G)$$
 
 This version of the generator loss function is particularly useful for theoretical analysis as shown in the first GAN paper \citep{2014arXiv1406.2661G}.
-It can be shown that the minimax game is the same as minimizing the Jensen-Shannon divergence and that each player will eventually converge if both players are able to directly update the function space as oppose to the parameters within a neural network \citep{2017arXiv170100160G}.
+Goodfellow demonstrated that the minimax game is the same as minimizing the Jensen-Shannon divergence and that each player will eventually converge if both players are able to directly update the function space as oppose to the parameters within the network \citep{2017arXiv170100160G}.
 However, in this minimax version, the loss function of the generator suffers from a vanishing gradient when the discriminator confidently rejects the generated data.
@@
 This function is heuristically motivated as to provide strong gradients when either the generator or discriminator is not functioning optimally.
+In this version, the generator attempts to maximize the log probability of a misclassification whereas the minimax version attempts to minimize the log probability of the discriminator being correct.
 
-$$J_g(\theta_D,\theta\G) = -\frac{1}{2}\mathbb{E}_{z\sim p_{z}(z)}[\log(D(G(z)))]$$
+$$J^{(G)}(\theta_D,\theta\G) = -\frac{1}{2}\mathbb{E}_{z\sim p_{z}(z)}\Big[\log(D(G(z)))\Big]$$
 
-Maximum likelihood learning is another option for training GANs \citep{2017arXiv170100160G}.
-In this situation, we would be minimizing the Kullback-Leibler divergence between $p_{data}$ and $p_{model}$.
+A maximum likelihood cost is another option for training GANs \citep{2017arXiv170100160G}.
+It can be shown that that this cost function minimizes the Kullback-Leibler divergence between $p_{data}$ and $p_{model}$ instead of the Jensen-Shannon divergence.
+This cost estimator is useful as it allows for comparison with other generative models; however, it behaves similarly to the minimax cost function as seen in \ref{fig:CostFunc}.
+
+$$J^{(G)}(\theta_D,\theta\G) = -\frac{1}{2}\mathbb{E}_{z\sim p_{z}(z)}\Big[\exp(\sigma^{-1}(D(G(z))))\Big]$$
 
@@
 \centering
-\includegraphics[scale=0.65]{costfunc}
-\caption{The cost of the generator................}
-\label{fig:Image to Image Examples}
+\includegraphics[scale=0.5]{costfunc}
+\caption{A comparison of the generator cost function for generative adversarial networks.
+When $D(G(z))$ is close to $0$, the gradient is saturated for both the minimax and maximum likelihood cost functions.
+This situation occurs when the discriminator $D$ confidently rejects the generated value $G(z)$ as fake.
+Therefore, the non-saturated heuristic cost function is the only one which works well in practice.
+Image retrieved from Goodfellow NIPs tutorial \citep{2017arXiv170100160G}.}
+\label{fig:CostFunc}
 \end{figure}
@@
 It is often speculated that the root cause of the issue the particular divergence measure used.
-Specifically, it is often asserted that mode collapse is caused by the use of Jenson-Shannon divergence; however, the use of Kullback-Leibler divergence has be shown to worsen the problem \citep{2017arXiv170100160G}.
+Specifically, it is often asserted that mode collapse is caused by the use of Jensen-Shannon divergence; however, the use of Kullback-Leibler divergence has be shown to worsen the problem \citep{2017arXiv170100160G}.
 As mode collapse is currently an unavoidable reality for GANs, their applications are limited to situations where it is acceptable to generate only a small number of distant samples \citep{2017arXiv170100160G}.
@@
 \subsection{Discrete Data}
+GANs assume a model implementation that is differentiable due to it's use of back propagation. Therefore, this restricts their ability to generate discrete data.
 

### 2017-11-28 cs6735/project/draft.tex
init training improvements
added a few training improvements

@@
 \usepackage{graphicx}
+\usepackage{bm}
 \usepackage[options ]{algorithm2e}
@@
 Therefore, the non-saturated heuristic cost function is the only one which works well in practice.
+Furthermore, the maximum likelihood cost function may produce high variance due to the rapid decrease as $D(G(z))$ nears $1$.
 Image retrieved from Goodfellow NIPs tutorial \citep{2017arXiv170100160G}.}
@@
 
-$$G^* = max_{D}min_{G}V(F, D)$$
+$$G^* = \max_{D}\min_{G}V(F, D)$$
 
@@
 \subsection{Discrete Data}
-GANs assume a model implementation that is differentiable due to it's use of back propagation. Therefore, this restricts their ability to generate discrete data.
+GANs assume a model implementation that is differentiable due to it's use of back propagation.
+Therefore, this restricts their ability to generate discrete data.
+Goodfellow proposes several solutions such as algorithm modifications, discretization and the use of concrete distributions or Gumbel-softmax \citep{2017arXiv170100160G}.
 
-\section{Improvements}
+\section{Training Improvements}
+A substantial amount of research has been conducted within the past three years with regards to improving GAN training procedures.
+A paper released by Goodfellow approximately one year after the debut of GANs outlines several techniques that can be applied to improve the training process \citep{2016arXiv160603498S}.
+As previously mentioned, the optimal solution for GANs remains convergence of the Nash equilibrium of the minimax game; however, gradient descent attempts to find a local minima.
+The following techniques introduced by Goodfellow \textit{et al.} address the instability of GANs and attempt to increase the probability of convergence.
 
-\subsection{Mini-Batch Features}
+\subsection{Feature Matching}
+Feature matching involves the definition of a new cost function for GANs such that they do not overtrain on the current discriminator \citep{2016arXiv160603498S}.
+Instead of optimizing on the output of the discriminator, the new objective requires the generator to minimize the difference between the expected value on some intermediate layer.
+The objective function can be described as $\Big|\Big|\mathbb{E}_{x\sim p_{data}(x)}\Big[f(x)\Big] - \mathbb{E}_{z\sim p_{z}(z)}\Big[f(G(z))\Big]\Big|\Big|_2^2$ where $f(x)$ is the output of the activation function of some layer.
+Experimental evidence has been gathered that demonstrates the usefulness of this technique, especially when the training process becomes instable \citep{2016arXiv160603498S}.
+Furthermore, feature matching is useful for semi-supervised GAN applications as will later be described in section \ref{sec:semisupervised}.
+
+\subsection{Minibatch Discrimination}
+Minibatch discrimination attempts to minimize the issues caused by mode collapse.
+This problem occurs as the discriminator processes each value $x$ independently of each other value.
+The gradient of each will point in the same direction thus leading to mode collapse.
+This technique involves the use of a minibatch in place of a single value to allow to discriminator to examine multiple data examples at one time.
+The discriminator is then able to examine the distance between each sample in conjunction with the samples themselves and look for abnormal minibatch distributions.
+Successful application of this technique allows for visually appealing images to be generated much quicker than by previous training techniques \citep{2016arXiv160603498S}.
+Preliminary results also show great reduction of mode collapse issues \citep{2017arXiv170100160G}.
+
+\subsection{Historical Averaging}
+Historical averaging introduces an extra term for each player's cost function such that they are penalized when choosing new parameters that differ from the historical mean value \citep{2016arXiv160603498S}.
+This new term $||\bm{\theta} - \frac{1}{t}\sum_{i=1}^{t}\bm{\theta}[i]||^2$ where $t$ is the total number of iterations performed and $\bm{\theta}[i]$ is the value of the parameters at iteration $i$.
+This technique has been demonstrated to help low dimensionality games reach an equilibrium where normal gradient descent has failed \citep{2016arXiv160603498S}.
+
+\subsection{Label Smoothing}
+\subsection{Virtual Batch Normalization}
 
@@
 \centering
-\includegraphics[scale=0.5]{cumulative_gans}
+\includegraphics[scale=0.45]{cumulative_gans}
 \caption{The cumulative amount of papers written about generative adversarial networks.
 The graph shows the exponential growth of GANs within the past three years.
-Image maintined by Avinash Hindipur \citep{November2017GANZoo}.}
+Image maintained by Avinash Hindipur \citep{November2017GANZoo}.}
 \label{fig:Cumulative Number of GAN papers by Month}
@@
 
-\subsection{Semi-Supervised Learning}
+\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
 \subsection{Feature Learning}

### 2017-12-01 cs6735/project/draft.tex
continued draft

@@
 \subsection{Label Smoothing}
+Label smoothing was a technique first introduced in the 1980s which involves replacing the 0 and 1 targets with \textit{smoother} values such as 0.1 and 0.9 respectively \citep{2016arXiv160603498S}.
+This technqiue is used to improve the networks resistance to adversarial examples.
+Specifically, it is recommendended to use one-sided label smoothing by using 0.9 label instead of 1 for the real data.
+By altering the label for fake data, this may lead to problems when $p_{data}(x)$ nears $0$ and $p_{model}(x)$ becomes large for some sample $x$ \citep{2016arXiv160603498S}.
+
 \subsection{Virtual Batch Normalization}
+Batch normalization is a technique which involves applying normalization for each training minibatch.
+This allows for much higher learning rates, more stable training and reduces problems associated with parameter initializtion \citep{2015arXiv150203167I}.
+This normalization technique was shown to successful for Deep Convolutional GANs; however, this causes a dependance relationship between the samples of the minibatch \citep{2016arXiv160603498S}...
 
-\section{Model Variations}
+\section{Architecture Variations}
 Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014.
@@
 
-\subsection{Deep Convolutional GANs}
-\subsection{Wasserstein GANs}
-\subsection{Conditional GANs}
+\subsection{Fully Connected GANs}
+\subsection{Convolutional GANs}
+\subsection{Inference GANs}
 \subsection{Progrssive GANs}

### 2017-12-02 cs6735/project/draft.tex
continued draft

@@
 \author{Jacob Smith}
-\date{December 12, 2017}
+\date{December 5, 2017}
 
@@
 Label smoothing was a technique first introduced in the 1980s which involves replacing the 0 and 1 targets with \textit{smoother} values such as 0.1 and 0.9 respectively \citep{2016arXiv160603498S}.
-This technqiue is used to improve the networks resistance to adversarial examples.
+This technique is used to improve the networks resistance to adversarial examples.
 Specifically, it is recommendended to use one-sided label smoothing by using 0.9 label instead of 1 for the real data.
@@
 Batch normalization is a technique which involves applying normalization for each training minibatch.
-This allows for much higher learning rates, more stable training and reduces problems associated with parameter initializtion \citep{2015arXiv150203167I}.
-This normalization technique was shown to successful for Deep Convolutional GANs; however, this causes a dependance relationship between the samples of the minibatch \citep{2016arXiv160603498S}...
+This allows for much higher learning rates, more stable training and reduces problems associated with parameter initialization \citep{2015arXiv150203167I}.
+This normalization technique was shown to successful for Deep Convolutional GANs; however, it causes a dependence relationship between the samples of the minibatch \citep{2016arXiv160603498S}.
+When implementation virtual batch normalization, a reference batch of samples is randomly chosen at the start of training and used throughout to normalize the current sample.
+However, this technique is computationally expensive as it requires forwarding two minibatches.
 
@@
 Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014.
-Significant improvements are being made with image quality and new applications are being found every month.
+Significant improvements are being made with respect to image quality and training stability.
+Hundreds of papers have been released since 2014 as seen in figure \ref{fig:CumulativeNumberofGANPapersbyMonth} which propose numerous architecture variations.
 
@@
 Image maintained by Avinash Hindipur \citep{November2017GANZoo}.}
-\label{fig:Cumulative Number of GAN papers by Month}
+\label{fig:CumulativeNumberofGANPapersbyMonth}
 \end{figure}
@@
 \subsection{Fully Connected GANs}
+The first generative adversarial network paper by Goodfellow \textit{et al.} made use of relatively simple fully connected neural networks for the generator and discriminator models.
+These are networks where each neuron in one layer is connected to every neuron in the following layer.
+This design is able to generate simple images and useful for proof of concept; however, several other architectures have overtaken this implementation \citep{2017arXiv171007035C}.
+
 \subsection{Convolutional GANs}
+Although convolutional neural networks (CNNs) seem well suited for the image generation tasks associated with GANs, difficulties associated with training initially constrained the use of convolutional models for both the discriminator and generator \citep{2017arXiv171007035C}.
+When implementing standard CNNs, one is often is unable to generate the same level of capacity and representational power.
+One solution proposed by Denton \textit{et al.} made use of Laplacian pyramids (LAPGAN), a type of image representation which repeatedly smooths and downsamples an image forming a sort of pyramid of images.
+At each layer of the pyramid, a conditional convolutional GAN is trained given generator output of the above layer.
+Another solution to this problem was proposed by Radford \textit{et al.}  simply made alterations to the existing deep convolutional network architecture \citep{2015arXiv151106434R}.
+Max pooling is replaced with strided layers within the discriminator and fractionally-strided layers within the generator.
+Furthermore, LeakyReLUs are used for all layers of the discriminator in place of the standard ReLU non-linearity function.
+The fractionally strided convolutions replicate within the generator replicate the benefits of the progressive upscaling within the Laplacian pyramid.
+The strided layers allow both the generator and discriminator to learn both the down-sampling and up-sampling operators during training \citep{2017arXiv171007035C}.
+Their architecture, called DCGAN, has become the base model for most GANs today \citep{2017arXiv170100160G}.
+
+\subsection{Conditional GANs}
+Initially proposed by Goodfellow as a straightforward extension of the first GAN architecture \citep{2014arXiv1406.2661G}, Mirza \textit{et al.} successfully implemented the conditional generative model in late 2014 \citep{2014arXiv1411.1784M}.
+Conditional generative models are constructed by feeding the additional parameter $\bm{c}$ to both to generator $G(\bm{z}|\bm{c})$ and discriminator $D(\bm{x}|\bm{c})$ to \textit{condition} the GAN.
+These architectures are better suited for multi-modal output \citep{2017arXiv171007035C}.
+By conditioning the GAN, it is possible to control the data generation process.
+These additional input may be class labels or other items such as text or an image.
+In section \ref{sec:img2img}, we will see how conditional GANs may be applied to image translation tasks.
+The new objective function of a conditional GAN becomes:
+
+$$\min_{G}\max_{D}V(D, G) = \mathbb{E}_{x\sim p_{data}(x)}\Big[\log(D(\bm{x}|\bm{c}))\Big] + \mathbb{E}_{z\sim p_z(z)}\Big[\log(1-D(G(\bm{z}|\bm{c})))\Big]$$
+
 \subsection{Inference GANs}
-\subsection{Progrssive GANs}
+The first GAN architectures lacked methods to convert
 
-\section{Research Frontiers}
+\subsection{Progressive GANs}
+
+\section{Applications}
 GANs are an exciting idea that are currently leading the frontier of deep generative models.
-
 \subsection{Divergence Measures}
 \subsection{Image Quality}
-Hiton's Capsule Network
+Hinton's Capsule Network
 Progressive GANs
-
 \subsection{Semi-Supervised Learning} \label{sec:semisupervised}
@@
 \subsection{Reinforcement Learning}
+\subsection{Image to Image Translation} \label{sec:img2img}
+
+\section{Research Frontiers}
+Evaluation, instability, mode collapse
+
+Reinforcement learning
 

### 2017-12-02 cs6735/project/draft.tex
finished inference models

@@
 At each layer of the pyramid, a conditional convolutional GAN is trained given generator output of the above layer.
+
 Another solution to this problem was proposed by Radford \textit{et al.}  simply made alterations to the existing deep convolutional network architecture \citep{2015arXiv151106434R}.
@@
 \subsection{Inference GANs}
-The first GAN architectures lacked methods to convert
-
-\subsection{Progressive GANs}
+The first GAN architectures lacked the ability to map an sample $\bm{x}$ to the associated latent vector $\bm{z}$.
+This feature of GANs is often referred to as an inference mechanism \citep{2017arXiv171007035C}.
+In 2016, two new architecture were independently proposed which introduce an adversarial learned inference by proposing the addition of another generator network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
+The paper by Dumoulin \textit{et al.} proposes a network which learns the mapping of $\bm{x}$ to $\bm{z}$ and generates a set of continuous variables.
+For example, if the vector $\bm{z}$ is of length $n$, then $n$ means and $n$ variances will be generated.
+This allows for a probability distribution for each value of $\bm{z}$.
+Furthermore, the discriminator is now trained upon both a sample $\bm{x}$ and latent space vector $\bm{z}$ and has to discriminate between a real and fake pairs.
+The reconstructed images remain of poor quality \citep{2017arXiv171007035C}.
 

### 2017-12-02 cs6735/project/draft.tex
added progressive

@@
 
+\subsection{Progressive GANs}
+Progressive GANs offer extend the DCGAN architecture by altering their training process.
+Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within both the generator and discriminator.
+Each new convolution is \texit{blended in} and is added after the current GAN converges which permits the generator to progressively discover the image distribution.
+Combined with new normalization techniques, progressive GANs allow for much higher resolution images to be generated \citep{2017arXiv171010196K}.
+The experimental results offer promising new directions for GAN research and applications.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.45]{progrssive_growing}
+\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \texit{et al.} \citep{2017arXiv171010196K}.
+The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
+\label{fig:CumulativeNumberofGANPapersbyMonth}
+\end{figure}
+
+\section{Latent Space}
 \section{Applications}
 GANs are an exciting idea that are currently leading the frontier of deep generative models.
-\subsection{Divergence Measures}
-\subsection{Image Quality}
-Hinton's Capsule Network
-Progressive GANs
+
 \subsection{Semi-Supervised Learning} \label{sec:semisupervised}
-\subsection{Feature Learning}
-\subsection{Semi-Supervised Learning}
-\subsection{Reinforcement Learning}
+\subsection{Image Generation}
 \subsection{Image to Image Translation} \label{sec:img2img}
+\subsection{Super Resolution}
 
@@
 Evaluation, instability, mode collapse
-
+\subsection{Divergence Measures}
+\subsection{Image Quality}
+\subsection{Reinforcement Learning}
 Reinforcement learning
@@
 \end{document}
+
+GANs build their own representations of the data they
+are trained on, and in doing so produce structured geometric
+vector spaces for different domains

### 2017-12-02 cs6735/project/draft.tex
finished semisupervised section

@@
 
-\subsection{Inference GANs}
+\subsection{Inference GANs} \label{sec:inferencegan}
 The first GAN architectures lacked the ability to map an sample $\bm{x}$ to the associated latent vector $\bm{z}$.
@@
 In 2016, two new architecture were independently proposed which introduce an adversarial learned inference by proposing the addition of another generator network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
-The paper by Dumoulin \textit{et al.} proposes a network which learns the mapping of $\bm{x}$ to $\bm{z}$ and generates a set of continuous variables.
+The paper by Dumoulin \textit{et al.} proposes a new generator network, referred to as an encoder, which learns the mapping of $\bm{x}$ to $\bm{z}$ and generates a set of continuous variables.
 For example, if the vector $\bm{z}$ is of length $n$, then $n$ means and $n$ variances will be generated.
@@
 \centering
-\includegraphics[scale=0.45]{progrssive_growing}
+\includegraphics[scale=0.45]{progressive_growing}
 \caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \texit{et al.} \citep{2017arXiv171010196K}.
 The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
-\label{fig:CumulativeNumberofGANPapersbyMonth}
+\label{fig:ProgressiveGrowingGAN}
 \end{figure}
@@
 \section{Applications}
-GANs are an exciting idea that are currently leading the frontier of deep generative models.
+Although GANs are a relatively new topic, many different applications have been discovered since their inception. Several of the reoccurring themes are elaborated within this section.
 
 \subsection{Semi-Supervised Learning} \label{sec:semisupervised}
+There exist several methods for training a classifier using a GAN.
+These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning and offer a quantitative method to rank different GAN models.
+One general transfer learning technique involves the use of discriminator within classification tasks as a feature extractor.
+A new machine learning model, such as a SVM, is subsequently able to be trained on the extracted features of some layer $l$ of the discriminator.
+Another transfer learning approach makes use of the inference GANs mentioned in section \ref{sec:inferencegan}.
+Another machine learning model is trained on the last three hidden layers of the of the encoder.
+These techniques have both received state-of-the-art classification results \citep{2017arXiv171007035C}.
+
+Another general approach to semi-supervised learning transforms the discriminator into a classifier of $k + 1$ classes where $k$ is the amount of real object classes.
+In this format, the $k + 1$ class is associated with a fake image.
+When a real image is given to the discriminator, it attempts to classify the sample as one of the k classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real.
+Typical supervised models need more than $50,000$ labels whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ in size \citep{2017arXiv170100160G}.
+
 \subsection{Image Generation}
@@
 \subsection{Super Resolution}
-
-\section{Research Frontiers}
-Evaluation, instability, mode collapse
-\subsection{Divergence Measures}
-\subsection{Image Quality}
 \subsection{Reinforcement Learning}

### 2017-12-02 cs6735/project/draft.tex
finished image generation

@@
 This technique makes use of conditional generative adversarial networks to map across image domains.}
-\label{fig:Image to Image Examples}
+\label{fig:img2img}
 \end{figure}
@@
 
-\subsection{Image Generation}
-\subsection{Image to Image Translation} \label{sec:img2img}
-\subsection{Super Resolution}
+\subsection{Image Generation} \label{sec:img2img}
+Image generation is extremely useful as many tasks intrinsically require the ability to generate realistic samples \citep{2017arXiv170100160G}.
+Most research conducted with respect the GANs attempts to improve the quality of the synthesized images \citep{2017arXiv171007035C}.
+As such, several useful and fascinating applications have already been found.
+
+Image super-resolution is the process of generating a high resolution image from a lower resolution image by inferring details.
+For each sample, there are multiple possible outputs.
+Due to this characteristic, GANs are optimally suited for this task to due their ability to model multi-model outputs.
+The SRGAN model proposed by Ledig \textit{et al.} trains a generator to fool discriminator which attempts to classify real images from super-resolution images \citep{2016arXiv160904802L}.
+SRGANs infer photo characteristics with respect to domain of training set \citep{2017arXiv171007035C}.
+
+Image-to-image translation has shown astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
+This includes to process of translating from a source domain $X$ to the target domain $Y$.
+An example of this process can be visualized in figure \ref{fig:img2img}.
+Conditional networks are well suited for this task and are used within several different GAN architectures which attempt to solve this problem \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}.
+Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) ≈ X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}.
+Furthermore, research recently released by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}.
+Generated images from semantic maps are now almost indistinguishable from real images.
+
 \subsection{Reinforcement Learning}

### 2017-12-02 cs6735/project/draft.tex
finished img2img
finished latent space section

@@
 \section{Latent Space}
+The generator model of a GAN must internalize a representation of the data they are trained on.
+This quality is shared with variatinal autoencoders word linguistic models such as \textit{word2vec} \citep{2017arXiv171007035C}.
+One interesting characteristic about the latent space is that it is typically of lower dimension than the training data \citep{2017arXiv171007035C}.
+This forces the model to effectively represent the training data by extracting only useful features.
+As long as the effects of mode collapse are minimal, the latent space can be highly structured \citep{2017arXiv171007035C}.
+Often, interpolations allow for semantic transformations.
+For example, movement of the latent vector in certain directions may alter rotation, produce colour changes or see the addition of attributes such as eyeglasses \citep{2017arXiv171007035C}.
+
+As mentioned in section \ref{sec:inferencegan}, it is possible to train an encoder to map a sample $\br{x}$ to a latent vector $\br{z}$.
+This is an extremely useful feature for exploring the latent space.
+One may discover \textit{concept vectors} such as "wearing glasses" or "wearing a hat" and apply them to the vectors associated with humans.
+This is a fascinating and practical property \citep{2017arXiv171007035C}.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.45]{smile_concept_vector}
+\caption{The addition of the "smile" concept vector (far right) to a vector associated with a woman (far left).
+The images in-between were created through an interpolation of the two vectors.
+Example retrieved form Dumoulin \texit{et al.} \citep{2016arXiv160600704D}.}
+\label{fig:conceptvector}
+\end{figure}
+
 \section{Applications}
@@
 \subsection{Reinforcement Learning}
-Reinforcement learning
+Modeling environments offers another promising application for GANs.
+This capability could potentially be used for reinforcement learning and motion planning.
+One possible method includes the use of generative models to predict possible futures \citep{2017arXiv170100160G}.
+The GAN would generate conditional distribution over future states given the current state and an hypothetical action.
+The agent would make multiple queries to the generator and then choose the action associated with the best possible future.
+This technique has already been applied by Finn and Levine in 2016 \citep{2016arXiv161000696F}.
+
+Generative models may also be used to maintain a record of past actions and visited locations to aid in future decisions.
+The connection between GANs and inverse reinforcement learning has also been investigated by Finn \textit{et al.} in 2016 \citep{2016arXiv161103852F}.
 

### 2017-12-03 cs6735/project/draft.tex
small fix
lots of editing

@@
 \begin{abstract}
-    Deep generative networks have often fallen short, especial when compared to discriminative models.
-Since their conception in 2014, generative adversarial networks have seen exponential growth in research.
-These networks offer promising results for both unsupervised learning and generative models.
-This research paper presents an overview of generative adversarial networks.
-Specifically, we will examine the motivation behind GANs, their theoretical justification, the current state of GANs and the research frontiers that have yet to be explored.
+    Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models which are now being applied to a multitude of real world applications.
+However, since their inception in 2014, generative adversarial networks (GANs) have proved themselves as promising a research avenues for deep generative models.
+These networks now offer encouraging results for both unsupervised learning and generative models.
+The goal of this research paper is to present an overview of generative adversarial networks.
+Specifically, we will examine the motivation and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
 \end{abstract}
@@
 \section{Introduction}
-Deep learning have made astounding progress within the past decade.
-Discriminative models have recently surpassed the abilities of human within the domain of pattern recognition \citep{2014arXiv1404.7828S}.
+Deep learning has made astounding progress within the past decade.
+Discriminative models have already surpassed the abilities of humans to recognize patterns within certain domains \citep{2014arXiv1404.7828S}.
 These successes can attributed to vast, high dimension datasets in conjunction with large neural networks using linear activation functions, dropout regularization techniques and backpropagation to update the parameters \citep{2014arXiv1406.2661G}.
-However, deep learning possesses many more ambitious goals.
-Until recently, success has mostly been seen with supervised classifiers; however, deep generative models now competitively rival their discriminative counterparts.
-
-Generative models learn the joint probability distribution $p(x,y)$ of an input $x$ and label $y$ whereas discriminative models directly learn the conditional probability $p(y|x)$.
-Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(x,y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
-Depending on the model, knowledge of the probability distribution can be created both explicitly and implicitly \citep{Goodfellow-et-al-2016}.
-Those which do not directly model a probability distribution offer mechanisms which require implicit knowledge of the underlying distribution, such as creating a sample from that distribution \citep{Goodfellow-et-al-2016}.
+However, deep learning possesses much more ambitious goals within the realm of unsupervised learning.
 As humans, we are able to understand the world around us with tremendous precision.
@@
 Although progress within the machine learning field is rapidly advancing, computers still have limited understanding of the data the process.
-Generative models, especially deep generative models, offer promising results towards this goal \citep{genmodelingopenai}.
+Generative models, especially deep generative models such as GANs, offer promising results towards this formidable challenge \citep{genmodelingopenai}.
+
+\subsection{Generative Modeling}
+Generative models learn the joint probability distribution $p(\br{x},y)$ of an input $\br{x}$ and label $y$ whereas discriminative models directly learn the conditional probability $p(y|x)$.
+An example of of this process can be seen in figure \ref{pdf}.
+Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(\br{x},y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
+Although, generative models offer several other applications due to their knowledge of the underlying data distribution.
+Depending on the model, knowledge of the probability distribution can be created both explicitly and implicitly \citep{Goodfellow-et-al-2016}.
+Those which do not directly model a probability distribution offer mechanisms which require implicit knowledge of the underlying distribution, such as geminating a sample from that distribution \citep{Goodfellow-et-al-2016}.
 
@@
 \caption{The process density estimation of one-dimensional data and a Gaussian distribution \citep{2017arXiv170100160G}.
-Generative models take a dataset $D$, sourced from a distribution $p_{data}$, a create an estimate of that distribution $p_{model}$.}
+Generative models take a dataset $D$, sourced from a distribution $p_{data}$ and create an estimate of the distribution $p_{model}$.}
 \label{fig:pdf}
@@
 The process of training a generative model is very similar to a discriminative model.
-Using large amounts of data collected from a specific domain, we train the model to generate data from that domain.
-As these models have fewer parameters than that the number of data samples, they are forced to internalize some representation of the data.
-Although, unlike supervised training, there exists no explicit desired output.
-The problem becomes defining a cost function which forces the generative model to produce data more like that of the domain.
+Using large amounts of data collected from a specific domain, we train the generative model to generate data from that domain.
+As these models typically have fewer parameters than that the number of data samples, they are forced to internalize some representation of the data \citep{genmodelingopenai}.
+This process within the context of GANs is elaborated in section \ref{sed:latentspace}.
+Unlike supervised training, there exists no single desired output.
+The problem becomes defining a cost function which forces the generative model to produce data more like that of the target domain \citep{genmodelingopenai}.
 
-Generative adversarial networks (GANs), first introduced in 2014, offer a new framework for estimating generative models with use of an adversarial process \citep{2014arXiv1406.2661G}.
+\subsection{Generative Adversarial Networks}
+Generative adversarial networks (GANs), first introduced in 2014 by Goodfellow \textit{et al.}, offer a new framework for estimating generative models with use of an adversarial process \citep{2014arXiv1406.2661G}.
 These models offer a clever approach to solving the aforementioned problem of explicitly defining a cost function.
 Rather than training a single model, a discriminator is introduced.
-These two networks are pitted against each other in a minimax game.
-The generative model $G$ attempts to produce data that resembles that of the training set while the discriminative model $D$ attempts to classify whether or not a sample was real of generated.
+These two networks are pitted against each other in a minimax, zero-sum game.
+The generative model $G$ attempts to produce data that resembles that of the training set while the discriminative model $D$ attempts to discriminate between a real and generated (fake) sample.
 To train this network, $G$ attempts to maximize the error rate of $D$ whereas $D$ attempts to minimize it.
@@
 
-\section{Motivations}
-There exists several compelling reasons for studying generative modeling \citep{2017arXiv170100160G}.
-These models are extremely useful when your goal is understand the underlying distribution parameters.
-For example, joint probability distributions of high dimensional data is relevant to both applied math and engineering \citep{2017arXiv170100160G}.
-Generative models are also applicable to reinforcement learning, particularly model-based learning algorithms.
-A time series generative model, one which predicts future states of an environment given the current state of the environment and an agents actions, are of particular interest \citep{2017arXiv170100160G}.
-An agent may learn the best action to take in a given scenario by querying this generative model and choosing the one which outputs the best state of the world.
-Furthermore, generative models, especially GANs, have recently excelled at semi-supervised learning.
+The adversarial process is often analogized to a counterfeiter trying to fool a detective \citep{2014arXiv1406.2661G}.
+The detective will receive both real and counterfeited money and will try and distinguish between the two.
+This leads to a competitive scenario where both parties gradually improve their abilities until the counterfeits are indistinguishable from the true currency.
 
-Proposed in the original GAN paper \citep{2014arXiv1406.2661G}, semi-supervised techniques used in conjunction with GANs have recently proven themselves as a reputable technique.
-The premise involves training the discriminator to classify images into $n + 1$ classes where $n$ is the number of class labels and the additional $1$ is the class of a fake image.
-This algorithm is able to obtain great performance on relatively small labeled datasets when compared to labeled datasets typically state of the art supervised algorithms \citep{2017arXiv170100160G}.
-Currently, the best performing semi-supervised GAN are feature matching GANs, where the new objective of the generative model is to minimize the distance between a layer $l$ of the discriminator \citep{2016arXiv160603498S}.
+\subsection{Motivations}
+There exists several compelling reasons for studying generative modeling, especially GANs \citep{2017arXiv170100160G}.
+Generative models are extremely useful when your goal is understand the underlying data generating distribution.
+The ability to learn the joint probability distribution of high dimensional data is relevant to both applied math and engineering \citep{2017arXiv170100160G}.
+Furthermore, GAN promise many real world applications.
+Several of these opportunities are expanded upon in section \ref{sec:applications}.
 
-Many applications require multi-modal outputs.
-For example, predicting the next action of a self-driving car.
-Within this context, it is important the model not be trained by traditional methods, such as using mean squared error to minimize the distance between the expected and predicted actions.
-These models cannot be used in situations where there is more than one appropriate prediction.
-Generative modeling, especially GAN, allow machine learning to function the scenarios where one input corresponds to multiple acceptable outputs \citep{2017arXiv170100160G}.
+\subsection{Related Work}
+Until the advent of GANs, most deep generative models provided a parametric specification of an probability distribution function \citep{2014arXiv1406.2661G}.
+These models could be trained using maximum likelihood estimation which often required gradient estimation.
+The most successful of these models is the deep Boltzmann machine \citep{2014arXiv1406.2661G}.
+The difficulties associated with gradient estimation motivated the development of \texit{generative machines}, models which implicitly represent the joint probability distribution by generating samples from that distribution rather than explicitly rendering a probability distribution.
 
-Tasks which involve image generation, modification or translation are all highly applicable to generative models.
-Although GANs may be used to generate any type of data, images remain the most commonly used source of training data.
-Research conducted within the past three years demonstrates the capabilities of GANs to perform these tasks \citep{2017arXiv170100160G, 2016arXiv161102200T, 2014arXiv1411.1784M}.
-For example, GANs have recently been shown to be capable of translating aerial photographs into maps and sketches into realistic images \citep{2017arXiv170100160G}.
-
-When compared to other generative models, especially deep generative models, GANs possess several advantages... quicker? no Markov chains?
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.55]{img2img}
-\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
-This technique makes use of conditional generative adversarial networks to map across image domains.}
-\label{fig:img2img}
-\end{figure}
+Deep generative stochastic networks are an example of a generative machine.
+This model, developed by Bengio \textit{et al.} in 2013 \citep{2013arXiv1306.1091B}, was able to use backpropagation during training; however, still made use Markov chains which introduced instability problems.
+GANs extend the ideas presented within generative stochastic networks by eliminating the use of Markov chains \citep{2014arXiv1406.2661G}.
 
 \section{Background}
-Generative adversarial networks may use any differentiable functions for the models; however, the optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
+GANs may use any differentiable functions for the models; however, the optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
 We first define a vector $z$ such that $z~p_z(z)$.
@@
 \centering
-\includegraphics[scale=0.45]{cumulative_gans}
+\includegraphics[scale=0.43]{cumulative_gans}
 \caption{The cumulative amount of papers written about generative adversarial networks.
@@
 
-\section{Latent Space}
+\section{Latent Space} \label{sed:latentspace}
 The generator model of a GAN must internalize a representation of the data they are trained on.
@@
 One may discover \textit{concept vectors} such as "wearing glasses" or "wearing a hat" and apply them to the vectors associated with humans.
+An example of this process can be seen in figure \ref{fig:conceptvector}.
 This is a fascinating and practical property \citep{2017arXiv171007035C}.
@@
 
-\section{Applications}
+\section{Applications} \label{sec:applications}
 Although GANs are a relatively new topic, many different applications have been discovered since their inception. Several of the reoccurring themes are elaborated within this section.
+
+\subsection{Image Generation} \label{sec:img2img}
+Image generation is extremely useful as many tasks intrinsically require the ability to generate realistic samples \citep{2017arXiv170100160G}.
+Moreover, GANs posses the ability to model multi-modal outputs (see figure \ref{fig:multimodal}) \citep{2017arXiv170100160G}.
+Most research conducted with respect the GANs attempts to improve the quality of the synthesized images \citep{2017arXiv171007035C}.
+As such, several useful and fascinating applications have already been found.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.7]{multimodal}
+\caption{An example of scenario where the ability to model multi-modal data is important.
+This image demonstrates the process of predicting the next video frame given the previous one.
+A generator trained with mean squared error (middle) produces an image which averages each possible future.
+Using an adversarial process (right), the image produced corresponds with the most likely scenario.
+Example retrieved form Lotter \texit{et al.} \citep{2015arXiv151106380L}.}
+\label{fig:multimodal}
+\end{figure}
+
+Image super-resolution is the process of generating a high resolution image from a lower resolution image by inferring details.
+For each sample, there are multiple possible outputs.
+Due to this characteristic, GANs are optimally suited for this task to due their ability to model multi-model outputs.
+The SRGAN model proposed by Ledig \textit{et al.} trains a generator to fool discriminator which attempts to classify real images from super-resolution images \citep{2016arXiv160904802L}.
+SRGANs infer photo characteristics with respect to domain of training set \citep{2017arXiv171007035C}.
+
+Image-to-image translation has shown astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
+This includes to process of translating from a source domain $X$ to the target domain $Y$.
+An example of this process can be visualized in figure \ref{fig:img2img}.
+Conditional networks are well suited for this task and are used within several different GAN architectures which attempt to solve this problem \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}.
+Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) ≈ X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}.
+Furthermore, research recently released by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}.
+Generated images from semantic maps are now almost indistinguishable from real images.
 
@@
 
-\subsection{Image Generation} \label{sec:img2img}
-Image generation is extremely useful as many tasks intrinsically require the ability to generate realistic samples \citep{2017arXiv170100160G}.
-Most research conducted with respect the GANs attempts to improve the quality of the synthesized images \citep{2017arXiv171007035C}.
-As such, several useful and fascinating applications have already been found.
-
-Image super-resolution is the process of generating a high resolution image from a lower resolution image by inferring details.
-For each sample, there are multiple possible outputs.
-Due to this characteristic, GANs are optimally suited for this task to due their ability to model multi-model outputs.
-The SRGAN model proposed by Ledig \textit{et al.} trains a generator to fool discriminator which attempts to classify real images from super-resolution images \citep{2016arXiv160904802L}.
-SRGANs infer photo characteristics with respect to domain of training set \citep{2017arXiv171007035C}.
-
-Image-to-image translation has shown astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
-This includes to process of translating from a source domain $X$ to the target domain $Y$.
-An example of this process can be visualized in figure \ref{fig:img2img}.
-Conditional networks are well suited for this task and are used within several different GAN architectures which attempt to solve this problem \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}.
-Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) ≈ X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}.
-Furthermore, research recently released by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}.
-Generated images from semantic maps are now almost indistinguishable from real images.
+\begin{figure}
+\centering
+\includegraphics[scale=0.55]{img2img}
+\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
+This technique makes use of conditional generative adversarial networks to map across image domains.}
+\label{fig:img2img}
+\end{figure}
 

### 2017-12-03 cs6735/project/temp.tex
more editing

\subsection{Motivations}
There exists several compelling reasons for studying generative modeling, especially GANs \citep{2017arXiv170100160G}. Generative models are extremely useful when your goal is understand the underlying data generating distribution. The ability to learn the joint probability distribution of high dimensional data is relevant to both applied math and engineering \citep{2017arXiv170100160G}.

Generative models are applicable to reinforcement learning, particularly model-based learning algorithms \citep{2017arXiv170100160G}. Moreover, there exits several techniques for applying GAN to semi-supervised learning problems which have proved themselves as reputable techniques. These two applications are expanded upon in section \ref{sec:applications}

Many applications require multi-modal outputs. For example, predicting the next action of a self-driving car. Within this context, it is important the model not be trained by traditional methods, such as using mean squared error to minimize the distance between the expected and predicted actions. These models cannot be used in situations where there is more than one appropriate prediction. Generative modeling, especially GAN, allow machine learning to function the scenarios where one input corresponds to multiple acceptable outputs \citep{2017arXiv170100160G}.

Tasks which involve image generation, modification or translation are all highly applicable to generative models. Although GANs may be used to generate any type of data, images remain the most commonly used source of training data. Research conducted within the past three years demonstrates the capabilities of GANs to perform these tasks \citep{2017arXiv170100160G, 2016arXiv161102200T, 2014arXiv1411.1784M}. For example, GANs have recently been shown to be capable of translating aerial photographs into maps and sketches into realistic images \citep{2017arXiv170100160G}.

### 2017-12-03 cs6735/project/report.tex
renamed draft -> report

--- 2017-12-03 cs6735/project/draft.tex
@@
 \usepackage{graphicx}
-\usepackage{bm}
 \usepackage[options ]{algorithm2e}
@@
 \subsection{Generative Modeling}
-Generative models learn the joint probability distribution $p(\br{x},y)$ of an input $\br{x}$ and label $y$ whereas discriminative models directly learn the conditional probability $p(y|x)$.
-An example of of this process can be seen in figure \ref{pdf}.
+Generative models learn the joint probability distribution $p(x,y)$ of an input $x$ and label $y$ whereas discriminative models directly learn the conditional probability $p(y|x)$.
+An example of this process can be seen in figure \ref{fig:pdf}.
 Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(\br{x},y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
@@
 \section{Background}
-GANs may use any differentiable functions for the models; however, the optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
-We first define a vector $z$ such that $z~p_z(z)$.
-This vector becomes the argument of the generator $G(z;\theta_g)$ where $G$ is a differentiable function and $\theta_g$ is its parameters.
-Another differentiable function $D(x;\theta_d)$ for the discriminator.
-This function takes as input a vector $x$, either from the output of $G$ or a sample from the training set, and is parametrized by $\theta_d$.
-The output of the discriminator is a scalar number representation the probability that the arguments were derived from the training data.
-In this situation, there exists a minimax game where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize $\log(1-D(G(z)))$.
-The networks $G$ and $D$ play a minimax game with the value function $V(D,G)$:
+The goal of the GAN training process is to determine the discriminator and generator parameters such that the classifier error is minimized and maximized respectively \citep{2017arXiv171007035C}.
+GANs may use any differentiable functions for their underlying implementation; however, optimal results are typically achieved when neural networks are used \citep{2014arXiv1406.2661G}.
+We first define a vector $z$ which is sampled from a prior noise distribution $z~p_z(z)$.
+This vector becomes the argument of the generator $G(z;\theta_g)$ where $G$ is a differentiable function and $\theta_g$ are its parameters.
+Another differentiable function $D(x;\theta_d)$ is defined for the discriminator.
+This function takes as input a vector $x$ from either the output of $G$ or a sample from the training set and is parametrized by $\theta_d$.
+The output of the discriminator is a scalar number which represents the probability that the sample $x$ was derived from the training data.
+In this situation, there exists a minimax game, a scenario derived from game theory, where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize $\log(1-D(G(z)))$.
+The value function $V(D,G)$ becomes:
 
@@
 
-For the training step, any variant of gradient descent may be used with respect to the individual cost functions \citep{2017arXiv170100160G}.
-The first updates $\theta_D$ while attempting to minimize the discriminator cost function $J_D$ while the other updates $\theta_G$ while attempting to minimize the generator cost function $J_G$.
-There exist several variations of the cost function that may be used for training purposes; however, the discriminator cost has remained the same for each.
+\subsection{Cost Functions}
+For training, any variant of gradient descent may be used \citep{2017arXiv170100160G}.
+The first part of the training step involves updating $\theta_D$ while attempting to minimize the discriminator cost function $J_D$.
+The next part involves updating $\theta_G$ while attempting to minimize the generator cost function $J_G$.
+There exist several variations of the cost function that may be used for training purposes; however, the discriminator cost has remained the same:
 
@@
 This is a standard cross entropy cost function that is trained on two minibatches, one from the dataset and one from the generator.
-For this to become a zero-sum game, the cost function of the generator is simply the negation of the discriminator.
+For this to become a zero-sum game, the cost function of the generator is simply the negation of the discriminator:
 
@@
 
-This version of the generator loss function is particularly useful for theoretical analysis as shown in the first GAN paper \citep{2014arXiv1406.2661G}.
-Goodfellow demonstrated that the minimax game is the same as minimizing the Jensen-Shannon divergence and that each player will eventually converge if both players are able to directly update the function space as oppose to the parameters within the network \citep{2017arXiv170100160G}.
+This version of the generator loss function is particularly useful for theoretical analysis as shown in the original GAN paper \citep{2014arXiv1406.2661G}.
+Goodfellow demonstrated that the learning within the minimax game is identical to minimizing the Jensen-Shannon divergence and that each player will eventually converge if both players are able to directly update the function space as oppose to the parameters within the network \citep{2017arXiv170100160G}.
 However, in this minimax version, the loss function of the generator suffers from a vanishing gradient when the discriminator confidently rejects the generated data.
@@
 This function is heuristically motivated as to provide strong gradients when either the generator or discriminator is not functioning optimally.
-In this version, the generator attempts to maximize the log probability of a misclassification whereas the minimax version attempts to minimize the log probability of the discriminator being correct.
+In this version, the generator attempts to maximize the log probability of a misclassification whereas the minimax version attempts to minimize the log probability of the discriminator being correct:
 
@@
 It can be shown that that this cost function minimizes the Kullback-Leibler divergence between $p_{data}$ and $p_{model}$ instead of the Jensen-Shannon divergence.
-This cost estimator is useful as it allows for comparison with other generative models; however, it behaves similarly to the minimax cost function as seen in \ref{fig:CostFunc}.
+This cost estimator is useful as it allows for comparison with other generative models; however, it behaves similarly to the minimax cost function as seen in figure \ref{fig:CostFunc}.
 
@@
 When $D(G(z))$ is close to $0$, the gradient is saturated for both the minimax and maximum likelihood cost functions.
-This situation occurs when the discriminator $D$ confidently rejects the generated value $G(z)$ as fake.
+This situation occurs when the discriminator $D$ confidently rejects the generated sample $G(z)$.
 Therefore, the non-saturated heuristic cost function is the only one which works well in practice.
-Furthermore, the maximum likelihood cost function may produce high variance due to the rapid decrease as $D(G(z))$ nears $1$.
-Image retrieved from Goodfellow NIPs tutorial \citep{2017arXiv170100160G}.}
+Furthermore, the maximum likelihood cost function may produce high variance due to the rapid decrease of $J^{(G)}$ as $D(G(z))$ nears $1$.
+Image retrieved from Goodfellow's NIPs tutorial \citep{2017arXiv170100160G}.}
 \label{fig:CostFunc}
@@
 
+\subsection{Algorithm}
 This following algorithm presents initial training algorithm used by Goodfellow \textit{et al.} when GANs were introduced in 2014 \citep{2014arXiv1406.2661G}.
-Many modifications have been made by various sources.
 The first step in the algorithm is to optimize the discriminator $D$.
-Initially, many thought it would be optimal to train $D$ to completion; however, as previously mentioned, this is still a controversial topic among researchers \citep{2017arXiv170100160G}.
-For the initial GAN experiments, this number was set to $1$ to reduce computation time.
+Many researchers initially held the belief that it would be optimal to train $D$ more steps than the generator; however, this is still a controversial topic among researchers \citep{2017arXiv170100160G}.
+It is Goodfellow's opinion that each model should be trained simultaneously \citep{2017arXiv170100160G}.
 
@@
 Multiple variations of this algorithm have since been produced.
-One of the benefits of adversarial networks is that they may be updated using back propogation.}
+One of the benefits of adversarial networks is that they may be updated using back propagation.}
 \end{algorithm}
@@
 The training process makes use of gradient descent which does not guarantee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players.
-This is different than network optimization which is common in discriminative models.
-When each network trains, even if the specified network improves, the other may regress.
+This training process for GANs is different than network optimization which is common in discriminative models.
+When either the generator or discriminator trains, even if that specific network improves, the other may regress.
 This sometimes leads to the scenario where each network repeatedly undo's the other's progress.
-This problem is not specific to GANs, but to any game situations \citep{2017arXiv170100160G}.
-It was shown in the first paper that convergence was guaranteed if updates could be made to the function space, but no theoretical justification was been found that guarantees convergence within the parameter space \citep{2014arXiv1406.2661G}.
-However, there is no theoretical proof that that these games should not converge \citep{2017arXiv170100160G}.
-Typically, adversarial networks often oscillate between different kinds of samples without converging to an equilibrium in a phenomenon called mode collapse.
+This problem is not specific to GANs, but to any zero-sum game situations \citep{2017arXiv170100160G}.
+
+Goodfellow has demonstrated that convergence is guaranteed if updates are made directly to the function space; however, this is obviously not what occurs.
+During training, we only ever update the parameter space \citep{2014arXiv1406.2661G}.
+As of yet, no theoretical justifications have been found that guarantee convergence or non-convergence when updates are only made to the parameters \citep{2017arXiv170100160G}.
+In practice, adversarial networks often oscillate between different kinds of samples without converging to an equilibrium in a phenomenon called mode collapse.
 
 \subsection{Mode Collapse}
-Mode collapse occurs when the generator collapses several different latent space vectors $z$ map to the same outputs.
-Full mode collapse is rare; however, partial mode collapse always occurs and varies by intensity.
-For example, the generator may create two images that only differ by colour but were generated with very different latent vectors.
+Mode collapse occurs when the generator collapses several different latent space vectors $z$ to the same outputs.
+This problem can be visualized in figure \ref{fig:modecollapse}.
+Full mode collapse is rare; however, partial mode collapse often occurs and varies by intensity \citep{2017arXiv170100160G}.
+For example, the generator may create several images that contain the same object at different perspectives, but generated with dissimilar vectors.
 This occurs when the capacity of the generator is superior to that of the discriminator.
-Backpropagation does not necessarily follow the minimax game mentioned earlier and may behave like the maximin version.
+Backpropagation does not necessarily follow the minimax game mentioned earlier and may behave like the maximin version:
 
@@
 
-When this occurs, the generator attempts to map every latent vector to the one $x$ variable the discriminator is most likely to guess is real.
-When training, one can only hope the behavior resembles the minimax version.
-It is often speculated that the root cause of the issue the particular divergence measure used.
+When this occurs, the generator attempts to map every $z$ vector to the one $x$ variable the discriminator is most likely to guess is real.
+When training, one can only hope the behavior of gradient descent resembles the minimax version.
+It is often speculated that the root cause of the issue is the particular divergence measure used \citep{2017arXiv170100160G}.
 Specifically, it is often asserted that mode collapse is caused by the use of Jensen-Shannon divergence; however, the use of Kullback-Leibler divergence has be shown to worsen the problem \citep{2017arXiv170100160G}.
-As mode collapse is currently an unavoidable reality for GANs, their applications are limited to situations where it is acceptable to generate only a small number of distant samples \citep{2017arXiv170100160G}.
-A potential solution to this problem is discussed in the following section.
+As mode collapse is currently an unavoidable reality for GANs, their applications are limited to situations where it is acceptable to generate only a small number of distinct outputs \citep{2017arXiv170100160G}.
+However, recent progress has been made to reduce this problem.
+A potential solution is discussed in section \ref{sec:minidisc}.
 
@@
 Throughout the training process, this cycle continues does not reach an equilibrium.}
-\label{fig:Mode Collapse Example}
+\label{fig:modecollapse}
 \end{figure}
@@
 
-\subsection{Minibatch Discrimination}
+\subsection{Minibatch Discrimination} \label{sec:minidisc}
 Minibatch discrimination attempts to minimize the issues caused by mode collapse.
@@
 Historical averaging introduces an extra term for each player's cost function such that they are penalized when choosing new parameters that differ from the historical mean value \citep{2016arXiv160603498S}.
-This new term $||\bm{\theta} - \frac{1}{t}\sum_{i=1}^{t}\bm{\theta}[i]||^2$ where $t$ is the total number of iterations performed and $\bm{\theta}[i]$ is the value of the parameters at iteration $i$.
+This new term $||\theta - \frac{1}{t}\sum_{i=1}^{t}\theta[i]||^2$ where $t$ is the total number of iterations performed and $\theta[i]$ is the value of the parameters at iteration $i$.
 This technique has been demonstrated to help low dimensionality games reach an equilibrium where normal gradient descent has failed \citep{2016arXiv160603498S}.
@@
 Initially proposed by Goodfellow as a straightforward extension of the first GAN architecture \citep{2014arXiv1406.2661G}, Mirza \textit{et al.} successfully implemented the conditional generative model in late 2014 \citep{2014arXiv1411.1784M}.
-Conditional generative models are constructed by feeding the additional parameter $\bm{c}$ to both to generator $G(\bm{z}|\bm{c})$ and discriminator $D(\bm{x}|\bm{c})$ to \textit{condition} the GAN.
+Conditional generative models are constructed by feeding the additional parameter $c$ to both to generator $G(z|c)$ and discriminator $D(x|c)$ to \textit{condition} the GAN.
 These architectures are better suited for multi-modal output \citep{2017arXiv171007035C}.
@@
 
-$$\min_{G}\max_{D}V(D, G) = \mathbb{E}_{x\sim p_{data}(x)}\Big[\log(D(\bm{x}|\bm{c}))\Big] + \mathbb{E}_{z\sim p_z(z)}\Big[\log(1-D(G(\bm{z}|\bm{c})))\Big]$$
+$$\min_{G}\max_{D}V(D, G) = \mathbb{E}_{x\sim p_{data}(x)}\Big[\log(D(x|c))\Big] + \mathbb{E}_{z\sim p_z(z)}\Big[\log(1-D(G(z|c)))\Big]$$
 
 \subsection{Inference GANs} \label{sec:inferencegan}
-The first GAN architectures lacked the ability to map an sample $\bm{x}$ to the associated latent vector $\bm{z}$.
+The first GAN architectures lacked the ability to map an sample $x$ to the associated latent vector $z$.
 This feature of GANs is often referred to as an inference mechanism \citep{2017arXiv171007035C}.
 In 2016, two new architecture were independently proposed which introduce an adversarial learned inference by proposing the addition of another generator network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
-The paper by Dumoulin \textit{et al.} proposes a new generator network, referred to as an encoder, which learns the mapping of $\bm{x}$ to $\bm{z}$ and generates a set of continuous variables.
-For example, if the vector $\bm{z}$ is of length $n$, then $n$ means and $n$ variances will be generated.
-This allows for a probability distribution for each value of $\bm{z}$.
-Furthermore, the discriminator is now trained upon both a sample $\bm{x}$ and latent space vector $\bm{z}$ and has to discriminate between a real and fake pairs.
+The paper by Dumoulin \textit{et al.} proposes a new generator network, referred to as an encoder, which learns the mapping of $x$ to $z$ and generates a set of continuous variables.
+For example, if the vector $z$ is of length $n$, then $n$ means and $n$ variances will be generated.
+This allows for a probability distribution for each value of $z$.
+Furthermore, the discriminator is now trained upon both a sample $x$ and latent space vector $z$ and has to discriminate between a real and fake pairs.
 The reconstructed images remain of poor quality \citep{2017arXiv171007035C}.

### 2017-12-03 cs6735/project/report.tex
more edits

@@
 The most successful of these models is the deep Boltzmann machine \citep{2014arXiv1406.2661G}.
-The difficulties associated with gradient estimation motivated the development of \texit{generative machines}, models which implicitly represent the joint probability distribution by generating samples from that distribution rather than explicitly rendering a probability distribution.
+The difficulties associated with gradient estimation motivated the development of \textit{generative machines}, models which implicitly represent the joint probability distribution by generating samples from that distribution rather than explicitly rendering a probability distribution.
 
@@
 
-\subsection{Instability}
+\subsection{Instability} \label{sec:instability}
 Generative adversarial networks are often characterized by their instability \citep{2017arXiv170100160G}.
@@
 When generating images, problems often arise due to the generators difficulties with perspective, counting and structure \citep{2017arXiv170100160G}.
-For example, an generated animal may not have a 3D structure, have misplaced limbs or have too many of a specific body part.
-These issues arise due to the underlying model architecture and are not an inherent problem the adversarial network.
-Furthermore, generated image resolution has remained relatively low; however, recent improvements outlined in the following section show improvements with regard to resolution \citep{2017arXiv171010196K}.
+For example, an generated animal may  have a 2D structure, misplaced limbs or too many of a specific body part.
+These issues arise due to the underlying model architecture, typically convolutional neural networks, and are not a direct problem of the adversarial network \citep{2017arXiv170100160G}.
+Furthermore, generated image resolution has remained relatively low; however, recent improvements outlined in section \ref{sec:proggans} show improvements with regard to resolution.
 
@@
 The evaluation procedure for generative adversarial networks remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}.
-For example, models with high likelihood may produce poor samples and models with low likelihood may produce realistic samples.
+For example, models with high likelihood may produce unrealistic samples and models with low likelihood may produce realistic samples \citep{2017arXiv170100160G}.
 Several variations of the GANs examine the tradeoffs of divergence measures other than the original Kullback-Leibler divergence \citep{2015arXiv151101844T}.
-It can be shown that different metrics favor different models.
+It has been shown that different metrics lead to different tradeoffs and different evaluations favor different models \citep{2015arXiv151101844T}.
 Therefore, it is important to asses one's model within the context of the whole application \citep{2015arXiv151101844T}.
@@
 Therefore, this restricts their ability to generate discrete data.
-Goodfellow proposes several solutions such as algorithm modifications, discretization and the use of concrete distributions or Gumbel-softmax \citep{2017arXiv170100160G}.
+Goodfellow proposes several solutions such as algorithm modifications, discretization of outputs or the use of concrete distributions or Gumbel-softmax \citep{2017arXiv170100160G}.
 
@@
 A substantial amount of research has been conducted within the past three years with regards to improving GAN training procedures.
-A paper released by Goodfellow approximately one year after the debut of GANs outlines several techniques that can be applied to improve the training process \citep{2016arXiv160603498S}.
-As previously mentioned, the optimal solution for GANs remains convergence of the Nash equilibrium of the minimax game; however, gradient descent attempts to find a local minima.
-The following techniques introduced by Goodfellow \textit{et al.} address the instability of GANs and attempt to increase the probability of convergence.
+A paper released by Salimans \textit{et al.} while at OpenAI outlines several techniques that can be applied to improve the GAN training process \citep{2016arXiv160603498S}.
+As mentioned in section \ref{sec:instability}, the optimal solution for GANs is the convergence to the Nash equilibrium of the minimax game; however, gradient descent only attempts to minimize the cost function and not to find the Nash equilibrium.
+The following techniques introduced in the paper address the instability of GANs and attempt to increase the probability of convergence.
 
 \subsection{Feature Matching}
-Feature matching involves the definition of a new cost function for GANs such that they do not overtrain on the current discriminator \citep{2016arXiv160603498S}.
-Instead of optimizing on the output of the discriminator, the new objective requires the generator to minimize the difference between the expected value on some intermediate layer.
-The objective function can be described as $\Big|\Big|\mathbb{E}_{x\sim p_{data}(x)}\Big[f(x)\Big] - \mathbb{E}_{z\sim p_{z}(z)}\Big[f(G(z))\Big]\Big|\Big|_2^2$ where $f(x)$ is the output of the activation function of some layer.
-Experimental evidence has been gathered that demonstrates the usefulness of this technique, especially when the training process becomes instable \citep{2016arXiv160603498S}.
+Feature matching involves the definition of a new cost function for GANs so that the generator does not overtrain on the current discriminator \citep{2016arXiv160603498S}.
+Instead of optimizing on the output of the discriminator, the new objective requires the generator to minimize the difference between the expected value of some intermediate layer.
+The objective function can be described as $\Big|\Big|\mathbb{E}_{x\sim p_{data}(x)}\Big[f(x)\Big] - \mathbb{E}_{z\sim p_{z}(z)}\Big[f(G(z))\Big]\Big|\Big|_2^2$ where $f(x)$ is the output of the activation function of some layer of the discriminator.
+Experimental evidence gathered has demonstrated the usefulness of this technique, especially when the training process becomes instable \citep{2016arXiv160603498S}.
 Furthermore, feature matching is useful for semi-supervised GAN applications as will later be described in section \ref{sec:semisupervised}.
@@
 This problem occurs as the discriminator processes each value $x$ independently of each other value.
-The gradient of each will point in the same direction thus leading to mode collapse.
+The gradients of discriminator will all point in the same direction, thus leading to mode collapse.
 This technique involves the use of a minibatch in place of a single value to allow to discriminator to examine multiple data examples at one time.
 The discriminator is then able to examine the distance between each sample in conjunction with the samples themselves and look for abnormal minibatch distributions.
-Successful application of this technique allows for visually appealing images to be generated much quicker than by previous training techniques \citep{2016arXiv160603498S}.
+Successful applications of this technique allow for visually appealing images to be generated much quicker than by previous training techniques \citep{2016arXiv160603498S}.
 Preliminary results also show great reduction of mode collapse issues \citep{2017arXiv170100160G}.
@@
 Historical averaging introduces an extra term for each player's cost function such that they are penalized when choosing new parameters that differ from the historical mean value \citep{2016arXiv160603498S}.
-This new term $||\theta - \frac{1}{t}\sum_{i=1}^{t}\theta[i]||^2$ where $t$ is the total number of iterations performed and $\theta[i]$ is the value of the parameters at iteration $i$.
+The new term becomes $||\theta - \frac{1}{t}\sum_{i=1}^{t}\theta[i]||^2$ where $t$ is the total number of iterations performed and $\theta[i]$ is the value of the parameters at iteration $i$.
 This technique has been demonstrated to help low dimensionality games reach an equilibrium where normal gradient descent has failed \citep{2016arXiv160603498S}.
@@
 This technique is used to improve the networks resistance to adversarial examples.
-Specifically, it is recommendended to use one-sided label smoothing by using 0.9 label instead of 1 for the real data.
-By altering the label for fake data, this may lead to problems when $p_{data}(x)$ nears $0$ and $p_{model}(x)$ becomes large for some sample $x$ \citep{2016arXiv160603498S}.
+Specifically, it is recommended one use only one-sided label smoothing by using 0.9 label instead of 1 for the real data label.
+If one alters the label for fake data, problems may arise when $p_{data}(x)$ nears $0$ and $p_{model}(x)$ becomes large for some sample $x$ \citep{2016arXiv160603498S}.
 
 \subsection{Virtual Batch Normalization}
-Batch normalization is a technique which involves applying normalization for each training minibatch.
-This allows for much higher learning rates, more stable training and reduces problems associated with parameter initialization \citep{2015arXiv150203167I}.
-This normalization technique was shown to successful for Deep Convolutional GANs; however, it causes a dependence relationship between the samples of the minibatch \citep{2016arXiv160603498S}.
-When implementation virtual batch normalization, a reference batch of samples is randomly chosen at the start of training and used throughout to normalize the current sample.
-However, this technique is computationally expensive as it requires forwarding two minibatches.
+Batch normalization is a technique that was first introduced in 2014 which involves applying normalization for each training minibatch \citep{2015arXiv150203167I}.
+It allows for much higher learning rates, a more stable training process and a reduction of problems associated with parameter initialization \citep{2015arXiv150203167I}.
+This normalization technique has proved useful for GAN training; however, it often causes a dependence relationship between the samples of the minibatch \citep{2016arXiv160603498S}.
+A new technique called virtual batch normalization (VBN) was developed where a reference batch of samples is randomly chosen at the start of the training process and used throughout to normalize each training sample.
+However, this technique is computationally expensive as it requires forwarding two minibatches and it is recommended to only use VBN for the generator \citep{2016arXiv160603498S}.
 
@@
 Significant improvements are being made with respect to image quality and training stability.
-Hundreds of papers have been released since 2014 as seen in figure \ref{fig:CumulativeNumberofGANPapersbyMonth} which propose numerous architecture variations.
+Hundreds of papers have been released since 2014 (see figure \ref{fig:CumulativeNumberofGANPapersbyMonth}) which propose numerous architectural variations.
 
@@
 \subsection{Fully Connected GANs}
-The first generative adversarial network paper by Goodfellow \textit{et al.} made use of relatively simple fully connected neural networks for the generator and discriminator models.
+The first generative adversarial network paper by Goodfellow \textit{et al.} made use of relatively simple fully connected neural networks for the generator and discriminator models \citep{2017arXiv171007035C}.
 These are networks where each neuron in one layer is connected to every neuron in the following layer.
@@
 
-\subsection{Progressive GANs}
+\subsection{Progressive GANs} \label{sec:proggans}
 Progressive GANs offer extend the DCGAN architecture by altering their training process.
 Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within both the generator and discriminator.
-Each new convolution is \texit{blended in} and is added after the current GAN converges which permits the generator to progressively discover the image distribution.
+Each new convolution is \textit{blended in} and is added after the current GAN converges which permits the generator to progressively discover the image distribution.
 Combined with new normalization techniques, progressive GANs allow for much higher resolution images to be generated \citep{2017arXiv171010196K}.
@@
 \includegraphics[scale=0.45]{progressive_growing}
-\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \texit{et al.} \citep{2017arXiv171010196K}.
+\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \textit{et al.} \citep{2017arXiv171010196K}.
 The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
@@
 \centering
-\includegraphics[scale=0.45]{smile_concept_vector}
+\includegraphics[scale=0.40]{smile_concept_vector}
 \caption{The addition of the "smile" concept vector (far right) to a vector associated with a woman (far left).
 The images in-between were created through an interpolation of the two vectors.
-Example retrieved form Dumoulin \texit{et al.} \citep{2016arXiv160600704D}.}
+Example retrieved form Dumoulin \textit{et al.} \citep{2016arXiv160600704D}.}
 \label{fig:conceptvector}
@@
 Using an adversarial process (right), the image produced corresponds with the most likely scenario.
-Example retrieved form Lotter \texit{et al.} \citep{2015arXiv151106380L}.}
+Example retrieved form Lotter \textit{et al.} \citep{2015arXiv151106380L}.}
 \label{fig:multimodal}

### 2017-12-03 cs6735/project/report.tex
more edits

@@
 An example of this process can be seen in figure \ref{fig:pdf}.
-Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(\br{x},y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
+Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(x,y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
 Although, generative models offer several other applications due to their knowledge of the underlying data distribution.
@@
 Although convolutional neural networks (CNNs) seem well suited for the image generation tasks associated with GANs, difficulties associated with training initially constrained the use of convolutional models for both the discriminator and generator \citep{2017arXiv171007035C}.
-When implementing standard CNNs, one is often is unable to generate the same level of capacity and representational power.
-One solution proposed by Denton \textit{et al.} made use of Laplacian pyramids (LAPGAN), a type of image representation which repeatedly smooths and downsamples an image forming a sort of pyramid of images.
-At each layer of the pyramid, a conditional convolutional GAN is trained given generator output of the above layer.
+When implementing CNNs within a GAN, one is often unable to train the discriminator and generator to the same level of capacity and representational power when compared to supervised CNN models \citep{2017arXiv171007035C}.
+One solution proposed by Denton \textit{et al.} made use of Laplacian pyramids (LAPGAN) to address this problem \citep{2015arXiv150605751D}.
+A Laplacian pyramid is a type of multi-scale signal representation which repeatedly smooths and downsamples an image to form a sort of pyramid of images.
+At each layer of the pyramid, a conditional convolutional GAN (see section \ref{sec:condgan}) is trained given the generator output of the above layer.
 
-Another solution to this problem was proposed by Radford \textit{et al.}  simply made alterations to the existing deep convolutional network architecture \citep{2015arXiv151106434R}.
-Max pooling is replaced with strided layers within the discriminator and fractionally-strided layers within the generator.
+Another solution to this problem was proposed by Radford \textit{et al.} made alterations to conventional deep convolutional network architecture \citep{2015arXiv151106434R}.
+Max pooling was replaced with strided layers within the discriminator and fractionally-strided layers within the generator.
 Furthermore, LeakyReLUs are used for all layers of the discriminator in place of the standard ReLU non-linearity function.
-The fractionally strided convolutions replicate within the generator replicate the benefits of the progressive upscaling within the Laplacian pyramid.
-The strided layers allow both the generator and discriminator to learn both the down-sampling and up-sampling operators during training \citep{2017arXiv171007035C}.
-Their architecture, called DCGAN, has become the base model for most GANs today \citep{2017arXiv170100160G}.
+The fractionally strided layers within the generator replicate the benefits of the progressive upscaling within the Laplacian pyramid \citep{2017arXiv171007035C}.
+The strided layers allow the GAN to learn both the down-sampling and up-sampling operators during training \citep{2017arXiv171007035C}.
+This architecture, called DCGAN, has become the base model for most GANs today \citep{2017arXiv170100160G}.
 
-\subsection{Conditional GANs}
-Initially proposed by Goodfellow as a straightforward extension of the first GAN architecture \citep{2014arXiv1406.2661G}, Mirza \textit{et al.} successfully implemented the conditional generative model in late 2014 \citep{2014arXiv1411.1784M}.
-Conditional generative models are constructed by feeding the additional parameter $c$ to both to generator $G(z|c)$ and discriminator $D(x|c)$ to \textit{condition} the GAN.
-These architectures are better suited for multi-modal output \citep{2017arXiv171007035C}.
-By conditioning the GAN, it is possible to control the data generation process.
-These additional input may be class labels or other items such as text or an image.
-In section \ref{sec:img2img}, we will see how conditional GANs may be applied to image translation tasks.
+\subsection{Conditional GANs} \label{sec:condgan}
+Initially proposed by Goodfellow as a straightforward extension of the first GAN architecture \citep{2014arXiv1406.2661G}, Mirza \textit{et al.} successfully implemented a conditional generative model in late 2014 \citep{2014arXiv1411.1784M}.
+A generative model differs from a conventional models as an additional parameter $c$ is given to both the generator $G(z|c)$ and discriminator $D(x|c)$ to condition the GAN.
 The new objective function of a conditional GAN becomes:
@@
 
+These architectures are better suited for multi-modal output as they are able to provide better data representations \citep{2017arXiv171007035C}.
+By conditioning the GAN, it is possible to control the data generation process.
+This additional input may be class label or other items such as text or an image.
+In section \ref{sec:img2img}, we will see how conditional GANs are applied to image translation tasks.
+
 \subsection{Inference GANs} \label{sec:inferencegan}
-The first GAN architectures lacked the ability to map an sample $x$ to the associated latent vector $z$.
-This feature of GANs is often referred to as an inference mechanism \citep{2017arXiv171007035C}.
-In 2016, two new architecture were independently proposed which introduce an adversarial learned inference by proposing the addition of another generator network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
-The paper by Dumoulin \textit{et al.} proposes a new generator network, referred to as an encoder, which learns the mapping of $x$ to $z$ and generates a set of continuous variables.
-For example, if the vector $z$ is of length $n$, then $n$ means and $n$ variances will be generated.
+The first GAN architectures lacked the ability to map an sample $x$ to its associated latent vector $z$.
+The ability to do this is often referred to as having an \textit{inference mechanism} \citep{2017arXiv171007035C}.
+In 2016, two new architectures were independently proposed which introduced this mechanism by adding an inference network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
+This new architecture involves two generative models, a decoder and encoder, which work together to fool the discriminator.
+The discriminator is now trained with a sample $x$ and latent space vector $z$ and has to decide if the pair is a real sample and its encoding or generated image and its associated latent space input.
+This architecture allows the encode to learn the mapping of $x$ to $z$.
+Furthermore, it generates a set of continuous variables.
+That is, if the vector $z$ is of length $n$, then $n$ means and $n$ variances will be generated.
 This allows for a probability distribution for each value of $z$.
-Furthermore, the discriminator is now trained upon both a sample $x$ and latent space vector $z$ and has to discriminate between a real and fake pairs.
-The reconstructed images remain of poor quality \citep{2017arXiv171007035C}.
+However, the reconstructed images still remain of poor quality \citep{2017arXiv171007035C}.
 
 \subsection{Progressive GANs} \label{sec:proggans}
-Progressive GANs offer extend the DCGAN architecture by altering their training process.
+Progressive GANs do not offer an architecture variation but a new training methodology for training GANs.
 Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within both the generator and discriminator.
-Each new convolution is \textit{blended in} and is added after the current GAN converges which permits the generator to progressively discover the image distribution.
+Each new convolution is only added after the previous GAN converges.
+This permits the generator to progressively discover the image distribution, increases the training speed and reduces training instability \citep{2017arXiv171010196K}.
 Combined with new normalization techniques, progressive GANs allow for much higher resolution images to be generated \citep{2017arXiv171010196K}.
@@
 \section{Latent Space} \label{sed:latentspace}
-The generator model of a GAN must internalize a representation of the data they are trained on.
-This quality is shared with variatinal autoencoders word linguistic models such as \textit{word2vec} \citep{2017arXiv171007035C}.
-One interesting characteristic about the latent space is that it is typically of lower dimension than the training data \citep{2017arXiv171007035C}.
-This forces the model to effectively represent the training data by extracting only useful features.
+The generator model of a GAN must internalize a representation of the data that it is trained on.
+This quality is shared with variatinal autoencoders and word linguistic models such as \textit{word2vec} \citep{2017arXiv171007035C}.
+One interesting characteristic of the latent space is that it is typically of lower dimension than the training data \citep{2017arXiv171007035C}.
+This forces the model to efficiently represent the training data by extracting only useful features.
 As long as the effects of mode collapse are minimal, the latent space can be highly structured \citep{2017arXiv171007035C}.
-Often, interpolations allow for semantic transformations.
+We often observe semantic transformations when interpolations are conducted.
 For example, movement of the latent vector in certain directions may alter rotation, produce colour changes or see the addition of attributes such as eyeglasses \citep{2017arXiv171007035C}.
 
-As mentioned in section \ref{sec:inferencegan}, it is possible to train an encoder to map a sample $\br{x}$ to a latent vector $\br{z}$.
-This is an extremely useful feature for exploring the latent space.
-One may discover \textit{concept vectors} such as "wearing glasses" or "wearing a hat" and apply them to the vectors associated with humans.
-An example of this process can be seen in figure \ref{fig:conceptvector}.
-This is a fascinating and practical property \citep{2017arXiv171007035C}.
+As mentioned in section \ref{sec:inferencegan}, it is possible to train an encoder to map a sample $x$ to a latent vector $z$.
+This is an extremely useful feature for exploring the latent space \citep{2017arXiv171007035C}.
+For example, one may discover \textit{concept vectors} such as "wearing glasses" or "wearing a hat" and apply them to a vector associated with a human.
+An example of this process is illustrated in figure \ref{fig:conceptvector}.
 
@@
 \section{Applications} \label{sec:applications}
-Although GANs are a relatively new topic, many different applications have been discovered since their inception. Several of the reoccurring themes are elaborated within this section.
+Although GANs are a relatively new invention, many different applications have already been discovered. Several of the reoccurring themes are elaborated within this section.
 
@@
 Image generation is extremely useful as many tasks intrinsically require the ability to generate realistic samples \citep{2017arXiv170100160G}.
-Moreover, GANs posses the ability to model multi-modal outputs (see figure \ref{fig:multimodal}) \citep{2017arXiv170100160G}.
-Most research conducted with respect the GANs attempts to improve the quality of the synthesized images \citep{2017arXiv171007035C}.
-As such, several useful and fascinating applications have already been found.
+Moreover, image generator often requires the ability to model multi-modal outputs (see figure \ref{fig:multimodal}) \citep{2017arXiv170100160G}.
+GANs are well suited for both of these tasks.
+Most research conducted with respect the GANs attempts to improve the quality of synthesized images \citep{2017arXiv171007035C}.
+As such, several useful and fascinating image applications have already been found.
 
@@
 \centering
-\includegraphics[scale=0.7]{multimodal}
-\caption{An example of scenario where the ability to model multi-modal data is important.
-This image demonstrates the process of predicting the next video frame given the previous one.
+\includegraphics[scale=0.9]{multimodal}
+\caption{An example of scenario where the ability to model multi-modal data is incredibly important.
+This figure demonstrates the process of predicting the next video frame given the previous one.
 A generator trained with mean squared error (middle) produces an image which averages each possible future.
-Using an adversarial process (right), the image produced corresponds with the most likely scenario.
+When using an adversarial process (right), the image produced corresponds with the most likely scenario.
 Example retrieved form Lotter \textit{et al.} \citep{2015arXiv151106380L}.}
@@
 
+\subsubsection{Image Super-Resolution}
 Image super-resolution is the process of generating a high resolution image from a lower resolution image by inferring details.
-For each sample, there are multiple possible outputs.
-Due to this characteristic, GANs are optimally suited for this task to due their ability to model multi-model outputs.
-The SRGAN model proposed by Ledig \textit{et al.} trains a generator to fool discriminator which attempts to classify real images from super-resolution images \citep{2016arXiv160904802L}.
+For each lower resolution sample, there exists multiple possible correct outputs.
+Due to this characteristic, GANs are optimally suited for this task.
+The Super-Resolution GAN (SRGAN) proposed by Ledig \textit{et al.} remains similiar to other GANs; however, the discriminator is trained to distinguish real images from super-resolution images \citep{2016arXiv160904802L}.
 SRGANs infer photo characteristics with respect to domain of training set \citep{2017arXiv171007035C}.
+Therefore, it is essential to train different models for each domain of images.
 
+\subsubsection{Image-to-Image Translation}
 Image-to-image translation has shown astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
@@
 Conditional networks are well suited for this task and are used within several different GAN architectures which attempt to solve this problem \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}.
-Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) ≈ X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}.
-Furthermore, research recently released by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}.
+Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) \approx X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}.
+Furthermore, research recently released in November 2017 by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}.
 Generated images from semantic maps are now almost indistinguishable from real images.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.55]{img2img}
+\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
+This technique makes use of conditional generative adversarial networks to map across image domains.}
+\label{fig:img2img}
+\end{figure}
 
@@
 Typical supervised models need more than $50,000$ labels whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ in size \citep{2017arXiv170100160G}.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.55]{img2img}
-\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
-This technique makes use of conditional generative adversarial networks to map across image domains.}
-\label{fig:img2img}
-\end{figure}
 

### 2017-12-03 cs6735/project/report.tex
finished editing

@@
 \begin{abstract}
-    Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models which are now being applied to a multitude of real world applications.
+    Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models.
 However, since their inception in 2014, generative adversarial networks (GANs) have proved themselves as promising a research avenues for deep generative models.
@@
 \subsubsection{Image-to-Image Translation}
-Image-to-image translation has shown astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
-This includes to process of translating from a source domain $X$ to the target domain $Y$.
-An example of this process can be visualized in figure \ref{fig:img2img}.
-Conditional networks are well suited for this task and are used within several different GAN architectures which attempt to solve this problem \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}.
+Image-to-image translation has made astounding progress and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
+This process includes the translation of images from a source domain $X$ to the target domain $Y$.
+The translated images are then compared against images from the target domain and the generator parameters are updated as to reduce the distance between the translated and real images.
+An example of this operation can be visualized in figure \ref{fig:img2img}.
+Conditional networks are well suited for this task and there exists several different GAN architectures which take advantage of their characteristics to preform these translations \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}.
 Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) \approx X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}.
-Furthermore, research recently released in November 2017 by Wang \textit{et al.} further improve the quality of synthesized images \citep{2017arXiv171111585W}.
-Generated images from semantic maps are now almost indistinguishable from real images.
+Furthermore, research released in November 2017 by Wang \textit{et al.} further improve the general quality of synthesized images \citep{2017arXiv171111585W}.
+Their semantic map translations are now almost indistinguishable from real images.
 
@@
 \subsection{Semi-Supervised Learning} \label{sec:semisupervised}
-There exist several methods for training a classifier using a GAN.
-These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning and offer a quantitative method to rank different GAN models.
-One general transfer learning technique involves the use of discriminator within classification tasks as a feature extractor.
-A new machine learning model, such as a SVM, is subsequently able to be trained on the extracted features of some layer $l$ of the discriminator.
+There exist several techniques for training a classifier using a GAN.
+These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning.
+The ability to use GAN for unsupervised learning also offers a quantitative method to rank different GAN models.
+
+One method involves the use of transfer learning.
+After the GAN training process has completed, the discriminator may be used within classification tasks as a feature extractor.
+A new machine learning model, such as a support vector machine (SVM), is trained on the extracted features of some layer $l$ of the discriminator.
 Another transfer learning approach makes use of the inference GANs mentioned in section \ref{sec:inferencegan}.
-Another machine learning model is trained on the last three hidden layers of the of the encoder.
-These techniques have both received state-of-the-art classification results \citep{2017arXiv171007035C}.
+Similar to the previous technique, a new machine learning model is trained on the last three hidden layers of the of the encoder.
+These methods have both received state-of-the-art classification results \citep{2017arXiv171007035C}.
 
-Another general approach to semi-supervised learning transforms the discriminator into a classifier of $k + 1$ classes where $k$ is the amount of real object classes.
-In this format, the $k + 1$ class is associated with a fake image.
-When a real image is given to the discriminator, it attempts to classify the sample as one of the k classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real.
-Typical supervised models need more than $50,000$ labels whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ in size \citep{2017arXiv170100160G}.
+Another general approach to semi-supervised learning involves the transformation of the discriminator into a classifier.
+Given that there are $k$ different labels, the new classifier will have $k + 1$ classes where the $k + 1$ class is associated with a fake image.
+When a real image is given to the discriminator, it attempts to classify the sample as one of the $k$ classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real.
+In this situation, the classifier reverts back to its discriminative behavior.
+Typical supervised models need more than $50,000$ samples whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ samples using this technique \citep{2017arXiv170100160G}.
 
 \subsection{Reinforcement Learning}
-Modeling environments offers another promising application for GANs.
+Modeling environments offers another promising application of GANs.
 This capability could potentially be used for reinforcement learning and motion planning.
 One possible method includes the use of generative models to predict possible futures \citep{2017arXiv170100160G}.
-The GAN would generate conditional distribution over future states given the current state and an hypothetical action.
-The agent would make multiple queries to the generator and then choose the action associated with the best possible future.
+The GAN would learn a conditional distribution over future states given the current state and a hypothetical action.
+An agent could make multiple queries to the generator and subsequently choose the action associated with the best possible future.
 This technique has already been applied by Finn and Levine in 2016 \citep{2016arXiv161000696F}.
-
-Generative models may also be used to maintain a record of past actions and visited locations to aid in future decisions.
-The connection between GANs and inverse reinforcement learning has also been investigated by Finn \textit{et al.} in 2016 \citep{2016arXiv161103852F}.
+Generative models may also be used to maintain a record of past actions and visited locations to aid in future decisions \citep{2017arXiv170100160G}.
 
 \section{Conclusion}
-Generative models are currently being applied to many problems \citep{genmodelingopenai}; however, they offer many more possibilities due to their ability to understand the data they are given.
+GANs are generative models which allow us to parametrize complicated probability distribution functions.
+They can be used to generate, modify and manipulate images.
+Furthermore, they allow for the use novel techniques within the context of reinforcement learning and unsupervised learning.
+Today, they are already being applied to many problems \citep{genmodelingopenai}; however, the majority of their applications have yet to be discovered.
+As long as the research effort continues, GANs promise exciting new avenues within the field of machine learning.
 

### 2017-12-04 cs6735/project/report.tex
updated intro

@@
     Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models.
-However, since their inception in 2014, generative adversarial networks (GANs) have proved themselves as promising a research avenues for deep generative models.
-These networks now offer encouraging results for both unsupervised learning and generative models.
-The goal of this research paper is to present an overview of generative adversarial networks.
-Specifically, we will examine the motivation and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
+However, generative adversarial networks (GANs), first introduced in 2014 by Goodfollow \textit{et al.} \citep{2014arXiv1406.2661G}, have proved themselves as a promising research avenue for deep generative models.
+GANs present a new architecuture which allows for the unsupervised training of a generative model through backpropogation.
+Due to the current research effort, state-of-the-art results are now being acheived on a regular basis \citep{2017arXiv171010196K, 2017arXiv171111585W}; however, GANs still encounter instability during training and do not yet poccess the ability to produce completly realistic images.
+Nevertheless, these networks offer encouraging results for unsupervised learning, semi-supervised, reinforcement learning and several image generation tasks.
+This research paper will examine the motivations and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
 \end{abstract}

### 2017-12-04 cs6735/project/report.tex
edited up to the algorithm

@@
 Discriminative models have already surpassed the abilities of humans to recognize patterns within certain domains \citep{2014arXiv1404.7828S}.
-These successes can attributed to vast, high dimension datasets in conjunction with large neural networks using linear activation functions, dropout regularization techniques and backpropagation to update the parameters \citep{2014arXiv1406.2661G}.
+These successes can attributed to vast, high dimension datasets in conjunction with large neural networks using linear activation functions, dropout regularization techniques and backpropagation to update their parameters \citep{2014arXiv1406.2661G}.
 However, deep learning possesses much more ambitious goals within the realm of unsupervised learning.
@@
 It is easy to underestimate the complexity of the data we process to accomplish this feat.
-Although progress within the machine learning field is rapidly advancing, computers still have limited understanding of the data the process.
+Although progress within the machine learning field is rapidly advancing, computers maintain a limited understanding of the data they process.
 Generative models, especially deep generative models such as GANs, offer promising results towards this formidable challenge \citep{genmodelingopenai}.
@@
 Generative models learn the joint probability distribution $p(x,y)$ of an input $x$ and label $y$ whereas discriminative models directly learn the conditional probability $p(y|x)$.
-An example of this process can be seen in figure \ref{fig:pdf}.
-Generative models may be used as classifiers using Bayes rules to calculate the conditional probability $p(x,y)$ which can then be used to make predictions \citep{NIPS2001_2020}.
-Although, generative models offer several other applications due to their knowledge of the underlying data distribution.
+An example of this process is illustrated in figure \ref{fig:pdf}.
+Generative models may be used as classifiers by applying Bayes rules to calculate the conditional probability $p(y|x)$ \citep{NIPS2001_2020}.
+However, generative models offer several other applications due to their knowledge of the underlying data distribution.
 Depending on the model, knowledge of the probability distribution can be created both explicitly and implicitly \citep{Goodfellow-et-al-2016}.
-Those which do not directly model a probability distribution offer mechanisms which require implicit knowledge of the underlying distribution, such as geminating a sample from that distribution \citep{Goodfellow-et-al-2016}.
+Those which do not directly model a probability distribution offer mechanisms which require some implicit knowledge of the underlying distribution, such as generating samples from that distribution \citep{Goodfellow-et-al-2016}.
 
@@
 As these models typically have fewer parameters than that the number of data samples, they are forced to internalize some representation of the data \citep{genmodelingopenai}.
-This process within the context of GANs is elaborated in section \ref{sed:latentspace}.
 Unlike supervised training, there exists no single desired output.
-The problem becomes defining a cost function which forces the generative model to produce data more like that of the target domain \citep{genmodelingopenai}.
+Therefore, the problem becomes defining a cost function which forces the generative model to produce data more like that of the target domain \citep{genmodelingopenai}.
 
@@
 These two networks are pitted against each other in a minimax, zero-sum game.
-The generative model $G$ attempts to produce data that resembles that of the training set while the discriminative model $D$ attempts to discriminate between a real and generated (fake) sample.
+The generative model $G$ attempts to produce data that resembles that of the training set while the discriminative model $D$ attempts to discriminate between a real and fake (generated) sample.
 To train this network, $G$ attempts to maximize the error rate of $D$ whereas $D$ attempts to minimize it.
-The goal of the GAN algorithm is to reduce the distance between the data and generated probability distributions.
-Backpropagation is used to update the parameters and to train each model.
-In the ideal case, $D$ is unable to distinguish the generated samples from the real samples and produces an error rate of $\frac{1}{2}$ \citep{2014arXiv1406.2661G}.
+The goal of the GAN algorithm is to reduce the distance between the real data and generated data probability distributions.
+Backpropagation is used to update the parameters of both the descriminator and generator.
+In the ideal case, $D$ is unable to distinguish generated samples from real samples and produces an error rate of $\frac{1}{2}$ \citep{2014arXiv1406.2661G}.
 
 The adversarial process is often analogized to a counterfeiter trying to fool a detective \citep{2014arXiv1406.2661G}.
-The detective will receive both real and counterfeited money and will try and distinguish between the two.
+The detective will receive both real and counterfeited money and will attempt to distinguish between the two.
 This leads to a competitive scenario where both parties gradually improve their abilities until the counterfeits are indistinguishable from the true currency.
@@
 Generative models are extremely useful when your goal is understand the underlying data generating distribution.
-The ability to learn the joint probability distribution of high dimensional data is relevant to both applied math and engineering \citep{2017arXiv170100160G}.
-Furthermore, GAN promise many real world applications.
-Several of these opportunities are expanded upon in section \ref{sec:applications}.
+The ability to learn the joint probability distribution of high dimensional data is relevant to both applied math and engineering, in addition to many other fields \citep{2017arXiv170100160G}.
+Furthermore, GANs promise numerous real world applications which act as key motivators for their research.
+Several of these applications are expanded upon in section \ref{sec:applications}.
 
@@
 These models could be trained using maximum likelihood estimation which often required gradient estimation.
-The most successful of these models is the deep Boltzmann machine \citep{2014arXiv1406.2661G}.
-The difficulties associated with gradient estimation motivated the development of \textit{generative machines}, models which implicitly represent the joint probability distribution by generating samples from that distribution rather than explicitly rendering a probability distribution.
+The most successful of these models was the deep Boltzmann machine \citep{2014arXiv1406.2661G}.
+The difficulties associated with gradient estimation motivated the development of \textit{generative machines}.
+These new models implicitly represent the joint probability distribution by generating samples from that distribution rather than explicitly rendering a probability distribution.
 
@@
 Another differentiable function $D(x;\theta_d)$ is defined for the discriminator.
-This function takes as input a vector $x$ from either the output of $G$ or a sample from the training set and is parametrized by $\theta_d$.
+This function takes as input a vector $x$ from either the output of $G$ or the training set and is parametrized by $\theta_d$.
 The output of the discriminator is a scalar number which represents the probability that the sample $x$ was derived from the training data.
-In this situation, there exists a minimax game, a scenario derived from game theory, where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize $\log(1-D(G(z)))$.
+In this situation, there exists a minimax game, a scenario derived from game theory, where $D$ attempts to maximize the probability of assigning a correct label and $G$ attempts to minimize that same probability.
 The value function $V(D,G)$ becomes:
@@
 
-This is a standard cross entropy cost function that is trained on two minibatches, one from the dataset and one from the generator.
+This is a standard cross entropy cost function of a neural network that is trained on two minibatches, one from the training dataset and the other from the generator.
 For this to become a zero-sum game, the cost function of the generator is simply the negation of the discriminator:
@@
 This version of the generator loss function is particularly useful for theoretical analysis as shown in the original GAN paper \citep{2014arXiv1406.2661G}.
-Goodfellow demonstrated that the learning within the minimax game is identical to minimizing the Jensen-Shannon divergence and that each player will eventually converge if both players are able to directly update the function space as oppose to the parameters within the network \citep{2017arXiv170100160G}.
+Goodfellow demonstrated that learning within this minimax game is identical to minimizing the Jensen-Shannon divergence and that the game will eventually converge if both players are able to directly update the function space as oppose to the parameters within the network \citep{2017arXiv170100160G}.
 However, in this minimax version, the loss function of the generator suffers from a vanishing gradient when the discriminator confidently rejects the generated data.
@@
 This cost estimator is useful as it allows for comparison with other generative models; however, it behaves similarly to the minimax cost function as seen in figure \ref{fig:CostFunc}.
+The cost function for this version becomes:
 
@@
 \subsection{Algorithm}
-This following algorithm presents initial training algorithm used by Goodfellow \textit{et al.} when GANs were introduced in 2014 \citep{2014arXiv1406.2661G}.
+The following algorithm presents the initial training algorithm as introduced by Goodfellow \textit{et al.} in 2014 \citep{2014arXiv1406.2661G}.
 The first step in the algorithm is to optimize the discriminator $D$.
-Many researchers initially held the belief that it would be optimal to train $D$ more steps than the generator; however, this is still a controversial topic among researchers \citep{2017arXiv170100160G}.
+Many researchers initially held the belief that it would be optimal to train $D$ for several iterations before training the generator; however, this is still a controversial topic among researchers \citep{2017arXiv170100160G}.
 It is Goodfellow's opinion that each model should be trained simultaneously \citep{2017arXiv170100160G}.

### 2017-12-04 cs6735/project/report.tex
small updates (computer is crashing)

@@
 Multiple variations of this algorithm have since been produced.
-One of the benefits of adversarial networks is that they may be updated using back propagation.}
+One of the benefits of adversarial networks is that they are able to make use of back propagation for training.}
 \end{algorithm}
@@
 \section{Issues}
-There exist several issues that characterize generative adversarial networks.
-Some are related design of GANs or their underlying network implementations.
+There exist several issues that characterize GANs.
+Some are due to the architecture of GANs while others to implementations of the generator and descriminator.
 These issues lay at the forefront of GAN research.
@@
 \subsection{Instability} \label{sec:instability}
-Generative adversarial networks are often characterized by their instability \citep{2017arXiv170100160G}.
+GANs are often characterized by their instability \citep{2017arXiv170100160G}.
 The training process makes use of gradient descent which does not guarantee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players.
@@
 \subsection{Evaluation}
-The evaluation procedure for generative adversarial networks remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}.
+The evaluation procedure for GANs remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}.
 For example, models with high likelihood may produce unrealistic samples and models with low likelihood may produce realistic samples \citep{2017arXiv170100160G}.
@@
 \section{Architecture Variations}
-Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014.
+Research within the field of deep generative modeling has increased exponentially since the debut of GANs in 2014.
 Significant improvements are being made with respect to image quality and training stability.
@@
 \includegraphics[scale=0.43]{cumulative_gans}
-\caption{The cumulative amount of papers written about generative adversarial networks.
+\caption{The cumulative amount of papers written about generative adversarial networks by month.
 The graph shows the exponential growth of GANs within the past three years.
@@
 \subsection{Fully Connected GANs}
-The first generative adversarial network paper by Goodfellow \textit{et al.} made use of relatively simple fully connected neural networks for the generator and discriminator models \citep{2017arXiv171007035C}.
+The first GAN paper by Goodfellow \textit{et al.} made use of relatively simple fully connected neural networks for the generator and discriminator models \citep{2017arXiv171007035C}.
 These are networks where each neuron in one layer is connected to every neuron in the following layer.

### 2017-12-04 cs6735/project/report.tex
small updates (computer is crashing)

@@
     Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models.
-However, generative adversarial networks (GANs), first introduced in 2014 by Goodfollow \textit{et al.} \citep{2014arXiv1406.2661G}, have proved themselves as a promising research avenue for deep generative models.
-GANs present a new architecuture which allows for the unsupervised training of a generative model through backpropogation.
-Due to the current research effort, state-of-the-art results are now being acheived on a regular basis \citep{2017arXiv171010196K, 2017arXiv171111585W}; however, GANs still encounter instability during training and do not yet poccess the ability to produce completly realistic images.
+However, generative adversarial networks (GANs), first introduced in 2014 by Goodfellow \textit{et al.} \citep{2014arXiv1406.2661G}, have proved themselves as a promising research avenue for deep generative models.
+GANs present a new architecture which allows for the unsupervised training of a generative model through backpropogation.
+Due to the current research effort, state-of-the-art results are now being achieved on a regular basis \citep{2017arXiv171010196K, 2017arXiv171111585W}; however, GANs still encounter instability during training and do not yet poccess the ability to produce completely realistic images.
 Nevertheless, these networks offer encouraging results for unsupervised learning, semi-supervised, reinforcement learning and several image generation tasks.
@@
 The goal of the GAN algorithm is to reduce the distance between the real data and generated data probability distributions.
-Backpropagation is used to update the parameters of both the descriminator and generator.
+Backpropagation is used to update the parameters of both the discriminator and generator.
 In the ideal case, $D$ is unable to distinguish generated samples from real samples and produces an error rate of $\frac{1}{2}$ \citep{2014arXiv1406.2661G}.
@@
 
-\section{Background}
+\section{Background} \label{sec:background}
 The goal of the GAN training process is to determine the discriminator and generator parameters such that the classifier error is minimized and maximized respectively \citep{2017arXiv171007035C}.
@@
 There exist several issues that characterize GANs.
-Some are due to the architecture of GANs while others to implementations of the generator and descriminator.
+Some are due to their architecture while others to implementations of the generator and discriminator.
 These issues lay at the forefront of GAN research.
@@
 The training process makes use of gradient descent which does not guarantee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players.
-This training process for GANs is different than network optimization which is common in discriminative models.
+This training process is different than network optimization which is common in discriminative models.
 When either the generator or discriminator trains, even if that specific network improves, the other may regress.
@@
 
-Goodfellow has demonstrated that convergence is guaranteed if updates are made directly to the function space; however, this is obviously not what occurs.
-During training, we only ever update the parameter space \citep{2014arXiv1406.2661G}.
-As of yet, no theoretical justifications have been found that guarantee convergence or non-convergence when updates are only made to the parameters \citep{2017arXiv170100160G}.
+Goodfellow has demonstrated that convergence is guaranteed if updates are made directly to the function space; however, this is not what occurs in practice.
+During training, we make updates to the parameter space rather than the function space \citep{2014arXiv1406.2661G}.
+As of yet, no theoretical justifications have been found that guarantee convergence or non-convergence when updates are made to the parameters \citep{2017arXiv170100160G}.
 In practice, adversarial networks often oscillate between different kinds of samples without converging to an equilibrium in a phenomenon called mode collapse.
@@
 This occurs when the capacity of the generator is superior to that of the discriminator.
-Backpropagation does not necessarily follow the minimax game mentioned earlier and may behave like the maximin version:
+Backpropagation does not necessarily follow the minimax game mentioned is section \ref{sec:background} and may behave like the maximin version:
 
@@
 
-When this occurs, the generator attempts to map every $z$ vector to the one $x$ variable the discriminator is most likely to guess is real.
-When training, one can only hope the behavior of gradient descent resembles the minimax version.
+When this occurs, the generator attempts to map every $z$ vector to the sample $x$ that which the discriminator is most likely to guess is real.
+When training, one can only hope that the behavior of gradient descent resembles that of the minimax game \citep{2017arXiv170100160G}.
 It is often speculated that the root cause of the issue is the particular divergence measure used \citep{2017arXiv170100160G}.
-Specifically, it is often asserted that mode collapse is caused by the use of Jensen-Shannon divergence; however, the use of Kullback-Leibler divergence has be shown to worsen the problem \citep{2017arXiv170100160G}.
-As mode collapse is currently an unavoidable reality for GANs, their applications are limited to situations where it is acceptable to generate only a small number of distinct outputs \citep{2017arXiv170100160G}.
+Specifically, it is often asserted that mode collapse is caused by the use of Jensen-Shannon divergence; however, the use of Kullback-Leibler divergence has been shown to worsen the problem \citep{2017arXiv170100160G}.
+As partial mode collapse is currently an unavoidable reality, the applications of GANs are limited to situations where it is acceptable to generate only a small number of distinct outputs \citep{2017arXiv170100160G}.
 However, recent progress has been made to reduce this problem.
@@
 \caption{An example of mode collapse as demonstrated by Metz \textit{et al.} \citep{2016arXiv161102163M}.
-The generated samples cluster around only one of the modes and do not spread out as they should.
-Throughout the training process, this cycle continues does not reach an equilibrium.}
+The generated samples cluster around only one of the modes and do not spread out as would be expected.
+Throughout the training process, this cycle continues and does not reach an equilibrium.}
 \label{fig:modecollapse}

### 2017-12-04 cs6735/project/report.tex
small updates (computer is crashing)

@@
 For example, an generated animal may  have a 2D structure, misplaced limbs or too many of a specific body part.
-These issues arise due to the underlying model architecture, typically convolutional neural networks, and are not a direct problem of the adversarial network \citep{2017arXiv170100160G}.
-Furthermore, generated image resolution has remained relatively low; however, recent improvements outlined in section \ref{sec:proggans} show improvements with regard to resolution.
+These issues arise due to the underlying generator architecture, typically deconvolutional neural networks, and are not an inherent problem of the adversarial network \citep{2017arXiv170100160G}.
+Furthermore, generated image resolution has remained relatively low; however, recent improvements outlined in section \ref{sec:proggans} show drastic improvements with regard to resolution.
 
 \subsection{Evaluation}
-The evaluation procedure for GANs remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}.
-For example, models with high likelihood may produce unrealistic samples and models with low likelihood may produce realistic samples \citep{2017arXiv170100160G}.
-Several variations of the GANs examine the tradeoffs of divergence measures other than the original Kullback-Leibler divergence \citep{2015arXiv151101844T}.
+The evaluation procedure for GANs remains an open debate as there exist no clear quantitative measurement to evaluate generative models \citep{2017arXiv170100160G}.
+For example, models with a high likelihood may produce unrealistic samples whereas models with a low likelihood may produce realistic samples \citep{2017arXiv170100160G}.
 It has been shown that different metrics lead to different tradeoffs and different evaluations favor different models \citep{2015arXiv151101844T}.
-Therefore, it is important to asses one's model within the context of the whole application \citep{2015arXiv151101844T}.
+Therefore, it is important to asses one's generative model within the context of the whole application \citep{2015arXiv151101844T}.
 
 \subsection{Discrete Data}
-GANs assume a model implementation that is differentiable due to it's use of back propagation.
+GANs assume a model implementation that is differentiable due to their use of back propagation.
 Therefore, this restricts their ability to generate discrete data.
@@
 A paper released by Salimans \textit{et al.} while at OpenAI outlines several techniques that can be applied to improve the GAN training process \citep{2016arXiv160603498S}.
-As mentioned in section \ref{sec:instability}, the optimal solution for GANs is the convergence to the Nash equilibrium of the minimax game; however, gradient descent only attempts to minimize the cost function and not to find the Nash equilibrium.
+As mentioned in section \ref{sec:instability}, the optimal solution for GANs is the convergence to the Nash equilibrium of the minimax game; however, gradient descent attempts to minimize the cost function and will not necessarily find the Nash equilibrium.
 The following techniques introduced in the paper address the instability of GANs and attempt to increase the probability of convergence.
@@
 \subsection{Feature Matching}
-Feature matching involves the definition of a new cost function for GANs so that the generator does not overtrain on the current discriminator \citep{2016arXiv160603498S}.
+Feature matching involves the definition of a new cost function for GANs to reduce the probability that the generator will not overtrain on the current discriminator \citep{2016arXiv160603498S}.
 Instead of optimizing on the output of the discriminator, the new objective requires the generator to minimize the difference between the expected value of some intermediate layer.
-The objective function can be described as $\Big|\Big|\mathbb{E}_{x\sim p_{data}(x)}\Big[f(x)\Big] - \mathbb{E}_{z\sim p_{z}(z)}\Big[f(G(z))\Big]\Big|\Big|_2^2$ where $f(x)$ is the output of the activation function of some layer of the discriminator.
+The new objective function can be described as $\Big|\Big|\mathbb{E}_{x\sim p_{data}(x)}\Big[f(x)\Big] - \mathbb{E}_{z\sim p_{z}(z)}\Big[f(G(z))\Big]\Big|\Big|_2^2$ where $f(x)$ is the output of the activation function of some layer of the discriminator.
 Experimental evidence gathered has demonstrated the usefulness of this technique, especially when the training process becomes instable \citep{2016arXiv160603498S}.
@@
 Minibatch discrimination attempts to minimize the issues caused by mode collapse.
-This problem occurs as the discriminator processes each value $x$ independently of each other value.
-The gradients of discriminator will all point in the same direction, thus leading to mode collapse.
-This technique involves the use of a minibatch in place of a single value to allow to discriminator to examine multiple data examples at one time.
+This issue occurs as the discriminator processes each sample $x$ independently of each other sample.
+Therefore, the gradients of discriminator will all point in the same direction, thus leading to mode collapse.
+This technique involves the use of a minibatch in place of a single sample to allow to discriminator to examine multiple data examples at one time.
 The discriminator is then able to examine the distance between each sample in conjunction with the samples themselves and look for abnormal minibatch distributions.
-Successful applications of this technique allow for visually appealing images to be generated much quicker than by previous training techniques \citep{2016arXiv160603498S}.
-Preliminary results also show great reduction of mode collapse issues \citep{2017arXiv170100160G}.
+Successful applications of this technique allow for visually appealing images to be generated much quicker than previous training techniques \citep{2016arXiv160603498S}.
+Preliminary results also show a great reduction of mode collapse \citep{2017arXiv170100160G}.
 
 \subsection{Historical Averaging}
-Historical averaging introduces an extra term for each player's cost function such that they are penalized when choosing new parameters that differ from the historical mean value \citep{2016arXiv160603498S}.
-The new term becomes $||\theta - \frac{1}{t}\sum_{i=1}^{t}\theta[i]||^2$ where $t$ is the total number of iterations performed and $\theta[i]$ is the value of the parameters at iteration $i$.
-This technique has been demonstrated to help low dimensionality games reach an equilibrium where normal gradient descent has failed \citep{2016arXiv160603498S}.
+Historical averaging introduces an extra term to each player's cost function such that they are penalized when choosing new parameters that differ from the historical mean value \citep{2016arXiv160603498S}.
+The new term added is $||\theta - \frac{1}{t}\sum_{i=1}^{t}\theta[i]||^2$ where $t$ is the total number of iterations performed and $\theta[i]$ is the value of the parameters at iteration $i$.
+This technique has been demonstrated to help low dimensionality games reach the Nash equilibrium where normal gradient descent would have failed \citep{2016arXiv160603498S}.
 
 \subsection{Label Smoothing}
-Label smoothing was a technique first introduced in the 1980s which involves replacing the 0 and 1 targets with \textit{smoother} values such as 0.1 and 0.9 respectively \citep{2016arXiv160603498S}.
+Label smoothing is a technique that was first introduced in the 1980s which involves replacing the 0 and 1 targets with \textit{smoother} values such as 0.1 and 0.9 respectively \citep{2016arXiv160603498S}.
 This technique is used to improve the networks resistance to adversarial examples.
-Specifically, it is recommended one use only one-sided label smoothing by using 0.9 label instead of 1 for the real data label.
+Specifically, it is recommended to use only one-sided label smoothing by replacing the 0.9 label instead of 1 for the real data label.
 If one alters the label for fake data, problems may arise when $p_{data}(x)$ nears $0$ and $p_{model}(x)$ becomes large for some sample $x$ \citep{2016arXiv160603498S}.
@@
 \subsection{Virtual Batch Normalization}
-Batch normalization is a technique that was first introduced in 2014 which involves applying normalization for each training minibatch \citep{2015arXiv150203167I}.
+Batch normalization (BN), a technique that was first introduced in 2014, involves normalizing each training minibatch \citep{2015arXiv150203167I}.
 It allows for much higher learning rates, a more stable training process and a reduction of problems associated with parameter initialization \citep{2015arXiv150203167I}.
-This normalization technique has proved useful for GAN training; however, it often causes a dependence relationship between the samples of the minibatch \citep{2016arXiv160603498S}.
-A new technique called virtual batch normalization (VBN) was developed where a reference batch of samples is randomly chosen at the start of the training process and used throughout to normalize each training sample.
-However, this technique is computationally expensive as it requires forwarding two minibatches and it is recommended to only use VBN for the generator \citep{2016arXiv160603498S}.
+BN has proved useful for GAN training; however, it often causes a dependence relationship between the samples of the minibatch \citep{2016arXiv160603498S}.
+A new technique called virtual batch normalization (VBN) resembles BN; however, a reference batch of samples is randomly chosen at the start of the training process and used throughout to normalize each training sample.
+This technique is computationally expensive as it requires forwarding two minibatches and it is recommended that one only use VBN for the generator \citep{2016arXiv160603498S}.
 
-\section{Architecture Variations}
+\section{Architecture & Training Variations}
 Research within the field of deep generative modeling has increased exponentially since the debut of GANs in 2014.
-Significant improvements are being made with respect to image quality and training stability.
-Hundreds of papers have been released since 2014 (see figure \ref{fig:CumulativeNumberofGANPapersbyMonth}) which propose numerous architectural variations.
+Significant improvements have been made with respect to image quality and training stability.
+Hundreds of papers have been released on the subject of GANs (see figure \ref{fig:CumulativeNumberofGANPapersbyMonth}) which propose numerous architectural and training variations.
 
@@
 \includegraphics[scale=0.43]{cumulative_gans}
-\caption{The cumulative amount of papers written about generative adversarial networks by month.
-The graph shows the exponential growth of GANs within the past three years.
+\caption{The cumulative amount of papers written about generative adversarial networks (GANs) by month.
+The graph shows the exponential growth of GAN research that has occurred within the past three and a half years.
 Image maintained by Avinash Hindipur \citep{November2017GANZoo}.}
@@
 These are networks where each neuron in one layer is connected to every neuron in the following layer.
-This design is able to generate simple images and useful for proof of concept; however, several other architectures have overtaken this implementation \citep{2017arXiv171007035C}.
+This design is able to generate simple images and is useful for proof of concept; however, several other architectures regularly outperform this implementation \citep{2017arXiv171007035C}.
 
 \subsection{Convolutional GANs}
-Although convolutional neural networks (CNNs) seem well suited for the image generation tasks associated with GANs, difficulties associated with training initially constrained the use of convolutional models for both the discriminator and generator \citep{2017arXiv171007035C}.
-When implementing CNNs within a GAN, one is often unable to train the discriminator and generator to the same level of capacity and representational power when compared to supervised CNN models \citep{2017arXiv171007035C}.
-One solution proposed by Denton \textit{et al.} made use of Laplacian pyramids (LAPGAN) to address this problem \citep{2015arXiv150605751D}.
+Although convolutional neural networks (CNNs) seem well suited for the image generation tasks often associated with GANs, difficulties with training initially constrained the use of convolutional models for both the discriminator and generator \citep{2017arXiv171007035C}.
+When implementing CNNs within a GAN, one is unable to train the discriminator and generator to the same level of capacity and representational power as supervised CNN models \citep{2017arXiv171007035C}.
+One solution proposed by Denton \textit{et al.} made use of Laplacian pyramids to address this problem \citep{2015arXiv150605751D}.
 A Laplacian pyramid is a type of multi-scale signal representation which repeatedly smooths and downsamples an image to form a sort of pyramid of images.
@@
 
-Another solution to this problem was proposed by Radford \textit{et al.} made alterations to conventional deep convolutional network architecture \citep{2015arXiv151106434R}.
+Another solution to this problem proposed by Radford \textit{et al.} made alterations to the conventional deep convolutional network architecture \citep{2015arXiv151106434R}.
 Max pooling was replaced with strided layers within the discriminator and fractionally-strided layers within the generator.
-Furthermore, LeakyReLUs are used for all layers of the discriminator in place of the standard ReLU non-linearity function.
+Furthermore, LeakyReLUs were used for all layers of the discriminator in place of the standard ReLU non-linearity function.
 The fractionally strided layers within the generator replicate the benefits of the progressive upscaling within the Laplacian pyramid \citep{2017arXiv171007035C}.
@@
 \subsection{Conditional GANs} \label{sec:condgan}
-Initially proposed by Goodfellow as a straightforward extension of the first GAN architecture \citep{2014arXiv1406.2661G}, Mirza \textit{et al.} successfully implemented a conditional generative model in late 2014 \citep{2014arXiv1411.1784M}.
-A generative model differs from a conventional models as an additional parameter $c$ is given to both the generator $G(z|c)$ and discriminator $D(x|c)$ to condition the GAN.
-The new objective function of a conditional GAN becomes:
+Initially proposed by Goodfellow as a straightforward extension of the first GAN architecture \citep{2014arXiv1406.2661G}, Mirza \textit{et al.} successfully implemented a conditional GAN (CGAN) in late 2014 \citep{2014arXiv1411.1784M}.
+CGANs differ from conventional models due to the additional parameter $c$ that is given to both the generator $G(z|c)$ and discriminator $D(x|c)$ to condition the GAN.
+The new objective function of a CGAN becomes:
 
@@
 
-These architectures are better suited for multi-modal output as they are able to provide better data representations \citep{2017arXiv171007035C}.
+These architectures are better suited for multi-modal output (see section \ref{sec:img2img}) as they are able to provide better data representations \citep{2017arXiv171007035C}.
 By conditioning the GAN, it is possible to control the data generation process.
 This additional input may be class label or other items such as text or an image.
+For example, given that a CGAN was conditioned on sentences, one may be able to describe a scenario and have that scenario synthesized as an image \citep{2016arXiv160505396R}.
 In section \ref{sec:img2img}, we will see how conditional GANs are applied to image translation tasks.

### 2017-12-04 cs6735/project/report.tex
small updates (computer is crashing)

@@
 This additional input may be class label or other items such as text or an image.
-For example, given that a CGAN was conditioned on sentences, one may be able to describe a scenario and have that scenario synthesized as an image \citep{2016arXiv160505396R}.
-In section \ref{sec:img2img}, we will see how conditional GANs are applied to image translation tasks.
+For example, given that a CGAN was conditioned on sentences, one may be able to describe a scenario and have that specific scenario synthesized as an image \citep{2016arXiv160505396R}.
+In section \ref{sec:img2img}, we will see how CGANs are applied to image translation tasks.
 
@@
 The ability to do this is often referred to as having an \textit{inference mechanism} \citep{2017arXiv171007035C}.
-In 2016, two new architectures were independently proposed which introduced this mechanism by adding an inference network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
+In 2016, two new architectures were independently proposed which both introduced this mechanism by adding an inference network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
 This new architecture involves two generative models, a decoder and encoder, which work together to fool the discriminator.
-The discriminator is now trained with a sample $x$ and latent space vector $z$ and has to decide if the pair is a real sample and its encoding or generated image and its associated latent space input.
-This architecture allows the encode to learn the mapping of $x$ to $z$.
-Furthermore, it generates a set of continuous variables.
+Instead of only receiving a sample $x$, the discriminator is also trained on a latent space vector $z$ and has to decide if the pair is a real sample and its encoding or generated sample and its associated latent space vector.
+This architecture allows the encoder to learn the mapping of $x$ to $z$.
+Furthermore, the encoder generates a set of continuous variables.
 That is, if the vector $z$ is of length $n$, then $n$ means and $n$ variances will be generated.
@@
 \subsection{Progressive GANs} \label{sec:proggans}
-Progressive GANs do not offer an architecture variation but a new training methodology for training GANs.
-Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within both the generator and discriminator.
-Each new convolution is only added after the previous GAN converges.
-This permits the generator to progressively discover the image distribution, increases the training speed and reduces training instability \citep{2017arXiv171010196K}.
+Progressive GANs do not offer an architecture variation but a new training methodology.
+Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within the generator and discriminator.
+A new convolution is added after the previous generator converges until a limit is reached.
+This permits the generator to progressively discover the image distribution.
+This technique also increases training speed and improves training stability \citep{2017arXiv171010196K}.
 Combined with new normalization techniques, progressive GANs allow for much higher resolution images to be generated \citep{2017arXiv171010196K}.
-The experimental results offer promising new directions for GAN research and applications.
+The experimental results received by Karras offer promising new directions for GAN research and applications.
 
@@
 \caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \textit{et al.} \citep{2017arXiv171010196K}.
-The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
+The generator and discriminator begin at $4x4$ resolution and progressively grow to generate and discriminate $1024x1024$ resolution images.}
 \label{fig:ProgressiveGrowingGAN}
@@
 This forces the model to efficiently represent the training data by extracting only useful features.
-As long as the effects of mode collapse are minimal, the latent space can be highly structured \citep{2017arXiv171007035C}.
-We often observe semantic transformations when interpolations are conducted.
+As long as the effects of mode collapse are minimal, the latent space is often highly structured \citep{2017arXiv171007035C}.
+We may observe semantic transformations when interpolations are conducted.
 For example, movement of the latent vector in certain directions may alter rotation, produce colour changes or see the addition of attributes such as eyeglasses \citep{2017arXiv171007035C}.
@@
 The images in-between were created through an interpolation of the two vectors.
-Example retrieved form Dumoulin \textit{et al.} \citep{2016arXiv160600704D}.}
+Example retrieved from Dumoulin \textit{et al.} \citep{2016arXiv160600704D}.}
 \label{fig:conceptvector}
@@
 \section{Applications} \label{sec:applications}
-Although GANs are a relatively new invention, many different applications have already been discovered. Several of the reoccurring themes are elaborated within this section.
+Although GANs are a relatively new in the field of machine learning, many different applications have already been discovered. Several of the reoccurring themes are elaborated within this section.
 
@@
 A generator trained with mean squared error (middle) produces an image which averages each possible future.
-When using an adversarial process (right), the image produced corresponds with the most likely scenario.
+When using an adversarial process (right), the image produced corresponds with the most likely scenario and is not blurry unlike the image generated using MSE.
 Example retrieved form Lotter \textit{et al.} \citep{2015arXiv151106380L}.}
@@
 Due to this characteristic, GANs are optimally suited for this task.
-The Super-Resolution GAN (SRGAN) proposed by Ledig \textit{et al.} remains similiar to other GANs; however, the discriminator is trained to distinguish real images from super-resolution images \citep{2016arXiv160904802L}.
-SRGANs infer photo characteristics with respect to domain of training set \citep{2017arXiv171007035C}.
+The Super-Resolution GAN (SRGAN) proposed by Ledig \textit{et al.} uses the conditional GAN architecture.
+The discriminator is trained to distinguish real images from super-resolution images \citep{2016arXiv160904802L}.
+SRGANs infer photo characteristics with respect to tje domain of training set \citep{2017arXiv171007035C}.
 Therefore, it is essential to train different models for each domain of images.
@@
 \subsubsection{Image-to-Image Translation}
-Image-to-image translation has made astounding progress and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
+Image-to-image translation has made astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}.
 This process includes the translation of images from a source domain $X$ to the target domain $Y$.
@@
 \caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}.
-This technique makes use of conditional generative adversarial networks to map across image domains.}
+This method makes use of conditional generative adversarial networks to map across image domains.}
 \label{fig:img2img}
@@
 These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning.
-The ability to use GAN for unsupervised learning also offers a quantitative method to rank different GAN models.
+The ability to use GAN for semi-supervised learning also offers a quantitative method to rank different GAN models.
 
@@
 After the GAN training process has completed, the discriminator may be used within classification tasks as a feature extractor.
-A new machine learning model, such as a support vector machine (SVM), is trained on the extracted features of some layer $l$ of the discriminator.
-Another transfer learning approach makes use of the inference GANs mentioned in section \ref{sec:inferencegan}.
-Similar to the previous technique, a new machine learning model is trained on the last three hidden layers of the of the encoder.
+A new machine learning model, such as a support vector machine, is trained on the extracted features of some layer $l$ of the discriminator.
+Another transfer learning approach makes use of inference GANs.
+A new machine learning model is trained on the last three hidden layers of the of the encoder.
 These methods have both received state-of-the-art classification results \citep{2017arXiv171007035C}.
@@
 Another general approach to semi-supervised learning involves the transformation of the discriminator into a classifier.
-Given that there are $k$ different labels, the new classifier will have $k + 1$ classes where the $k + 1$ class is associated with a fake image.
-When a real image is given to the discriminator, it attempts to classify the sample as one of the $k$ classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real.
+Given that there are $k$ different labels for some classification task, the new classifier will have $k + 1$ classes where the $k + 1$ class is associated with a fake sample.
+When a real sample is given to the discriminator, it attempts to classify the sample as one of the $k + 1$ classes; however, when a generated or unlabeled sample is given, the probabilities of the k classes are summed together to represent the probability of the sample being real.
 In this situation, the classifier reverts back to its discriminative behavior.
-Typical supervised models need more than $50,000$ samples whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ samples using this technique \citep{2017arXiv170100160G}.
+Typical supervised models need more than $50,000$ samples whereas state-of-the-art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ samples using this technique \citep{2017arXiv170100160G}.
 
@@
 They can be used to generate, modify and manipulate images.
-Furthermore, they allow for the use novel techniques within the context of reinforcement learning and unsupervised learning.
+Furthermore, they allow for the use novel techniques within the context of reinforcement learning and semi-supervised learning.
 Today, they are already being applied to many problems \citep{genmodelingopenai}; however, the majority of their applications have yet to be discovered.
-As long as the research effort continues, GANs promise exciting new avenues within the field of machine learning.
+As long as the research effort continues, GANs promise exciting new research avenues within the field of machine learning.
 

### 2017-12-05 cs6735/project/report.tex
done exam notes

@@
 
-\section{Architecture & Training Variations}
+\section{Architecture \& Training Variations}
 Research within the field of deep generative modeling has increased exponentially since the debut of GANs in 2014.

### 2017-12-05 cs6735/project/report.tex
edits

@@
 GANs present a new architecture which allows for the unsupervised training of a generative model through backpropogation.
-Due to the current research effort, state-of-the-art results are now being achieved on a regular basis \citep{2017arXiv171010196K, 2017arXiv171111585W}; however, GANs still encounter instability during training and do not yet poccess the ability to produce completely realistic images.
-Nevertheless, these networks offer encouraging results for unsupervised learning, semi-supervised, reinforcement learning and several image generation tasks.
+Due to the current research effort, state-of-the-art results are now being achieved on a regular basis \citep{2017arXiv171010196K, 2017arXiv171111585W}; however, GANs still encounter instability during training and do not yet possess the ability to produce completely realistic images.
+Nevertheless, these networks offer encouraging results for unsupervised learning, semi-supervised learning, reinforcement learning and several image generation tasks.
 This research paper will examine the motivations and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
@@
 Using large amounts of data collected from a specific domain, we train the generative model to generate data from that domain.
-As these models typically have fewer parameters than that the number of data samples, they are forced to internalize some representation of the data \citep{genmodelingopenai}.
+As these models typically have fewer parameters than the number of data samples, they are forced to internalize some representation of the data \citep{genmodelingopenai}.
 Unlike supervised training, there exists no single desired output.
@@
 \subsection{Related Work}
-Until the advent of GANs, most deep generative models provided a parametric specification of an probability distribution function \citep{2014arXiv1406.2661G}.
+Until the advent of GANs, most deep generative models provided a parametric specification of a probability distribution function \citep{2014arXiv1406.2661G}.
 These models could be trained using maximum likelihood estimation which often required gradient estimation.
@@
 A maximum likelihood cost is another option for training GANs \citep{2017arXiv170100160G}.
-It can be shown that that this cost function minimizes the Kullback-Leibler divergence between $p_{data}$ and $p_{model}$ instead of the Jensen-Shannon divergence.
+It can be shown that this cost function minimizes the Kullback-Leibler divergence between $p_{data}$ and $p_{model}$ instead of the Jensen-Shannon divergence.
 This cost estimator is useful as it allows for comparison with other generative models; however, it behaves similarly to the minimax cost function as seen in figure \ref{fig:CostFunc}.
@@
 The first step in the algorithm is to optimize the discriminator $D$.
-Many researchers initially held the belief that it would be optimal to train $D$ for several iterations before training the generator; however, this is still a controversial topic among researchers \citep{2017arXiv170100160G}.
+Many researchers initially held the belief that it would be optimal to train $D$ for several iterations before training the generator; however, this is still a controversial topic amongst researchers \citep{2017arXiv170100160G}.
 It is Goodfellow's opinion that each model should be trained simultaneously \citep{2017arXiv170100160G}.
@@
 \subsection{Feature Matching}
-Feature matching involves the definition of a new cost function for GANs to reduce the probability that the generator will not overtrain on the current discriminator \citep{2016arXiv160603498S}.
+Feature matching involves the definition of a new cost function for GANs to reduce the probability that the generator will overtrain on the current discriminator \citep{2016arXiv160603498S}.
 Instead of optimizing on the output of the discriminator, the new objective requires the generator to minimize the difference between the expected value of some intermediate layer.
@@
 This technique is used to improve the networks resistance to adversarial examples.
-Specifically, it is recommended to use only one-sided label smoothing by replacing the 0.9 label instead of 1 for the real data label.
+Specifically, it is recommended to use only one-sided label smoothing by replacing the 1 with 0.9 for the real data label.
 If one alters the label for fake data, problems may arise when $p_{data}(x)$ nears $0$ and $p_{model}(x)$ becomes large for some sample $x$ \citep{2016arXiv160603498S}.
@@
 \subsection{Inference GANs} \label{sec:inferencegan}
-The first GAN architectures lacked the ability to map an sample $x$ to its associated latent vector $z$.
+The first GAN architectures lacked the ability to map a sample $x$ to its associated latent vector $z$.
 The ability to do this is often referred to as having an \textit{inference mechanism} \citep{2017arXiv171007035C}.
 In 2016, two new architectures were independently proposed which both introduced this mechanism by adding an inference network \citep{2016arXiv160509782D, 2016arXiv160600704D}.
-This new architecture involves two generative models, a decoder and encoder, which work together to fool the discriminator.
+This new architecture involved two generative models, a decoder and encoder, which work together to fool the discriminator.
 Instead of only receiving a sample $x$, the discriminator is also trained on a latent space vector $z$ and has to decide if the pair is a real sample and its encoding or generated sample and its associated latent space vector.
@@
 Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within the generator and discriminator.
-A new convolution is added after the previous generator converges until a limit is reached.
+A new convolution is added after the previous generator converges.
 This permits the generator to progressively discover the image distribution.
@@
 This is an extremely useful feature for exploring the latent space \citep{2017arXiv171007035C}.
-For example, one may discover \textit{concept vectors} such as "wearing glasses" or "wearing a hat" and apply them to a vector associated with a human.
+For example, one may discover \textit{concept vectors} such as ``wearing glasses'' or ``wearing a hat'' and apply them to a vector associated with a human.
 An example of this process is illustrated in figure \ref{fig:conceptvector}.
@@
 \includegraphics[scale=0.40]{smile_concept_vector}
-\caption{The addition of the "smile" concept vector (far right) to a vector associated with a woman (far left).
-The images in-between were created through an interpolation of the two vectors.
+\caption{The addition of the ``smile'' concept vector (far right) to a vector associated with a woman (far left).
+The images in between were created through an interpolation of the two vectors.
 Example retrieved from Dumoulin \textit{et al.} \citep{2016arXiv160600704D}.}
@@
 \section{Applications} \label{sec:applications}
-Although GANs are a relatively new in the field of machine learning, many different applications have already been discovered. Several of the reoccurring themes are elaborated within this section.
+Although GANs are a relatively new idea within the field of machine learning, many different applications have already been discovered.
+Several of the reoccurring themes are elaborated within this section.
 
 \subsection{Image Generation} \label{sec:img2img}
-Image generation is extremely useful as many tasks intrinsically require the ability to generate realistic samples \citep{2017arXiv170100160G}.
-Moreover, image generator often requires the ability to model multi-modal outputs (see figure \ref{fig:multimodal}) \citep{2017arXiv170100160G}.
+Image generation is extremely useful as many tasks intrinsically require the ability to generate realistic images \citep{2017arXiv170100160G}.
+Moreover, image generation often requires the ability to model multi-modal outputs (see figure \ref{fig:multimodal}) \citep{2017arXiv170100160G}.
 GANs are well suited for both of these tasks.
@@
 These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning.
-The ability to use GAN for semi-supervised learning also offers a quantitative method to rank different GAN models.
+The ability to use GANs for semi-supervised learning also offers a quantitative method to rank different GAN models.
 
@@
 After the GAN training process has completed, the discriminator may be used within classification tasks as a feature extractor.
-A new machine learning model, such as a support vector machine, is trained on the extracted features of some layer $l$ of the discriminator.
+A new machine learning model, such as a support vector machine, may be trained on the extracted features of some layer $l$ of the discriminator.
 Another transfer learning approach makes use of inference GANs.
@@
 Another general approach to semi-supervised learning involves the transformation of the discriminator into a classifier.
-Given that there are $k$ different labels for some classification task, the new classifier will have $k + 1$ classes where the $k + 1$ class is associated with a fake sample.
+Given that there are $k$ different labels for some classification task, a new classifier is created that will have $k + 1$ classes where the $k + 1$ class is associated with a fake sample.
 When a real sample is given to the discriminator, it attempts to classify the sample as one of the $k + 1$ classes; however, when a generated or unlabeled sample is given, the probabilities of the k classes are summed together to represent the probability of the sample being real.
@@
 Today, they are already being applied to many problems \citep{genmodelingopenai}; however, the majority of their applications have yet to be discovered.
-As long as the research effort continues, GANs promise exciting new research avenues within the field of machine learning.
+GANs promise numerous exciting new research avenues within the field of machine learning.
 

### 2017-12-05 cs6735/assignment/report.tex
start assignment report

@@
 
+\section{Objectives}
+\begin{enumerate}
+  \item Implement the following machine learning algorithms:
+  \begin{enumerate}
+    \item ID3
+    \item Adaboost on ID3
+    \item Random Forest
+    \item Naïve Bayes
+    \item Adaboost on Naïve Bayes
+    \item K-nearest neighbors
+  \end{enumerate}
+  \item Evaluate the algorithms on the following datasets:
+  \begin{enumerate}
+    \item Brest Cancer Data
+    \item Car Data
+    \item Ecoli Data
+    \item Mushroom Data
+  \end{enumerate}
+  \item Create report of the experimental study including:
+  \begin{enumerate}
+    \item Description of the learning algorithms you implement.
+    \item Description of the datasets you use (number of examples, number of attribute, number of classes, type of attributes, etc.).
+    \item Technical details of your implementation: pre-processing of data sets (discretization, etc.), parameter setting, etc.
+    \item Design of your programming implementation (data structures, overall program structure).
+    \item Report and analysis of your experimental results using using 10 times 5-fold cross-validation (include mean, standard deviation of accuracies).
+    \item Comparison and discussion of the algorithms with respect to the experimental results.
+  \end{enumerate}
+\end{enumerate}
+
 \section{Algorithms}
@@
 \subsection{ID3}
+The Iterative Dichotomiser 3 (ID3) algorithm is a decision tree algorithm used to efficiently develop decision trees \cite{Quinlan:1986:IDT:637962.637969}.
+This algorithm was developed for situations where there are large amount of attributes and training sets which contain many attributes, but there was the need to be able to efficiently develop relatively well performing decision trees.
+
+The algorithm begins at the root node with a set of catigorical, labled data $S$.
+
 \subsection{Naïve Bayes}

### 2017-12-06 cs6735/assignment/report.tex
finished DT

@@
 
-The algorithm begins at the root node with a set of catigorical, labled data $S$.
+The algorithm as described by Mitchell \cite{Mitchell:1997:ML:541177} was implmented.
+The operations begin at the root node with a set of catigorical, labled data $S$.
+The attribute $A$ which introduces the largest information gain is chosen to split on.
+This is an exhaustive process which checks all remaining attributes.
+This process imediatly stops if there are no possible subsets (identical samples have same class label) or the split is not statistically significant (positive information gain).
+If these stopping conditions are not met, the data $S$ is split using attribute $A$ into subsets ${S1,...,SN}$ where $N$ is the amount of different categories of attribute $A$.
+A new node is then created for each subset.
+If the entropy of a new node is $0$ or the sample count is $1$, then the node is turned into a leaf and the splitting operation ends.
+Furthermore, two additional early stopping conditions are implemented.
+Max tree level and minimum number of samples attributes are initially set at the start of training.
+
+After the initial ID3 algorithm was implemented, furthure enhancements were made to allow for continuous data to be used.
+This enhancement was taken from the C4.5  as developed by Ross Quinlan \citep{c45algorithm}.
+Given a continuous attribute $A$, we temporarily sort the data $S$.
+After the data is sorted, we iteratively determine a threshhold to split the data as the maximize the information gain.
+To test potential threshholds, we find two sequential numbers which are not of the same category and split at the midway point of the two values.
+This enhancements saves an a large amount of time for each continuous attribute found within the datasets as descritization does not need to occur.
+Furthermore, this algorithm chooses the optimal threshhold to split the data which improves classification accuracy.
 
 \subsection{Naïve Bayes}
+The Naive Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independance amougst each attribute.
+
+\hat{y}= \underset{k\;\in\;\{1,..K\}} {\mathrm{argmax}} \;\;P(C_k)\prod_{i=1}^mp\left(x_i\;|\;C_k\right)\prod_{j=m}^nP\left(x_j\;|\;C_k\right)\;\;?
+
 \subsection{Adaboost}

### 2017-12-06 cs6735/assignment/report.tex
finished NB

@@
 This process imediatly stops if there are no possible subsets (identical samples have same class label) or the split is not statistically significant (positive information gain).
-If these stopping conditions are not met, the data $S$ is split using attribute $A$ into subsets ${S1,...,SN}$ where $N$ is the amount of different categories of attribute $A$.
+If these stopping conditions are not met, the data $S$ is split using attribute $A$ into subsets ${S_1,...,S_n}$ where $n$ is the amount of different categories of attribute $A$.
 A new node is then created for each subset.
@@
 \subsection{Naïve Bayes}
-The Naive Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independance amougst each attribute.
+The Naive Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independance amongst each attribute:
 
-\hat{y}= \underset{k\;\in\;\{1,..K\}} {\mathrm{argmax}} \;\;P(C_k)\prod_{i=1}^mp\left(x_i\;|\;C_k\right)\prod_{j=m}^nP\left(x_j\;|\;C_k\right)\;\;?
+$$P(a_1,...,a_n|v_j) = \prod_{i=1}^{n}P(a_i|v_j)$$
+
+and its application of Bayes thereom:
+
+$$P(A|B) = \frac{P(B|A)P(A)}{P(B)}$$
+
+Naive Bayes is a practical learning algorithm, receives relatively good results given its preference bias and is easy to implement.
+This algorithm naturally handles both catigorical and continuous data (given a prior is assumed).
+For each continuous attribute, a Gaussian distribution was assumed.
+The final algorithm implemented was:
+
+$$\hat{y}= \underset{k\;\in\;\{1,..K\}} {\mathrm{argmax}} \;\;P(v_k)\prod_{i=1}^mp\left(a_i\;|\;v_k\right)\prod_{j=m}^nP\left(a_j\;|\;v_k\right)\;\;$$
+
+where $P$ is the probability, $p$ is the gaussian probability density function and $K$ is the number of distinct targets.
+In this equation, the first m attributes are continous whereas the later are catigorical.
+During training, the data $S$ is split by lables into subsets ${S_1,...,S_n}$ where $n$ is the number of different classes.
+For each subset, we estimate the class probability $P(v_k)$.
+Subsequently, for each attribute value $a_i$ of each attribute $a$, we estimate $P(a_i|v_k)$ or $p$.
+We are not able to immidiately calculate $p(a_i|v_k)$ as attribute $a$ is a continous attribute.
 

### 2017-12-06 cs6735/assignment/report.tex
finished a lot more

@@
 
-The algorithm as described by Mitchell \cite{Mitchell:1997:ML:541177} was implmented.
+The algorithm as described by Mitchell \cite{Mitchell:1997:ML:541177} was implmented for this assignment.
 The operations begin at the root node with a set of catigorical, labled data $S$.
@@
 
-\subsection{Adaboost}
+\subsection{Adaboost} \label{adaboost}
+Adaboost is a boosting algorithm that was first introduced in 1995 by Freunb Schapire.
+This type of ensemble learning uses a set of weak learners to reduce bias and become a strong learner.
+It solves many of the difficulties associated with previous boosting algorithms \cite{Schapire:1999:BIB:1624312.1624417}.
+
+The primary part of the algorithm is to maintain a weight value $w$ for every sample within the data $S$.
+This value increases when the sample is misclassified and decreases when the sample is correctly classified.
+The target values are assumed be to in the set ${+1, -1}$.
+The Adaboost algorithm is easily implemented on weak learners which are parameterized by sample weights.
+Neither Naive Bayes or ID3 natively implement weighted training.
+Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights.
+For example, if the weight vector for two samples is ${1, 2}$, the second sample is twice as likely to be picked each time.
+
+Initially, the weights are set to $\frac{1}{|S|}$.
+For a predefined number of iterations, a weak learner is trained on the a subset of the traning data.
+Predictions are made for each training sample and the error is calculated.
+Using the accuracy, a value $\alpha$ is calculated which represents the accuracy of the weak learner.
+This $\alpha$ value is used to update the weights and the weak learner, $\alpha$ pair is added to the list of previous weak learners.
+To make classification, there is a weighted vote between using the weak learners and their associated $\alpha$ values and the sign is used to make the final classification.
+
+To implement multiclass adaboost, $K$ adaboost models are trained where $K$ is the total number of distint classes.
+For each adaboost model, one target is selected as the $+1$ adaboost target and the other become the $-1$ target.
+The target value associated with the most positive prediction becomes the predicted class.
+
+\subsubsection{Adaboost on Naive Bayes}
+Naive Bayes is an inherently weak learner due to its assumption of conditional independance amongst attributes.
+This fact introduces a large amount of preference bias which makes a Naive Bayes and ideal candidate for the Adaboost algorithm.
+
+\subsubsection{Adaboost on ID3}
+The ID3 algorithm does not introduce a large amount of preference bias and often overfits if allowed to train to completion.
+Therefore, to implement Adaboost on ID3, the depth of the trees were limited to one level.
+This type of tree is known as a \textit{decision stump}.
+
 \subsection{Random Forest}
+Random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfititng to the training set.
+This method contains many similarities to the adaboost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests.
+For a predifined number of iterations, a subset of the of the training data is selected with replacement.
+The new training set is then used to train a decision tree to completion and added to tree is added to a list.
+To make a classification, each tree in the forest votes and the most common target value becomes the predicted class.
+As an extension of the base random forest algorithm, weights may be given to each decision tree based on their classification error during training; however, this extension was not added for this implementation.
+
 \subsection{K-Nearest Neighbors}
+The K-Nearest Neighbor algorithm is an instance based learning algorithm which makes predictions by finding the $k$ nearest neighbors of a sample $x$ and using the most common class as the predicted class for that sample.
+This algorithm can be used with both catigorical and continuous data.
+For this implementation, Euclidian distance was used for continous variables and Hamming distance was used for catigorical data.
 
 \section{Data}
+Each algorithm was implemented on five different datasets from the UCI Machine Learning Repository.
+
 \subsection{Breast Cancer Data}
+\begin{enumerate}
+  \item Title: Wisconsin Diagnostic Breast Cancer
+  \item Date: November 1995
+  \item Number of Samples: 569
+  \item Number of Attributes: 10
+  \begin{tabular}{l c c c }
+    Description                  & Value     & Type
+    Sample Code Number           & id number & Discrete \\
+    Clump Thickness              & 1 - 10    & Discrete \\
+    Uniformity of Cell Size      & 1 - 10    & Discrete \\
+    Uniformity of Cell Shape     & 1 - 10    & Discrete \\
+    Marginal Adhesion            & 1 - 10    & Discrete \\
+    Single Epithelial Cell Size  & 1 - 10    & Discrete \\
+    Bare Nuclei                  & 1 - 10    & Discrete \\
+    Bland Chromatin              & 1 - 10    & Discrete \\
+    Normal Nucleoli              & 1 - 10    & Discrete \\
+    Mitoses                      & 1 - 10    & Discrete
+  \end{tabular}
+  \item Class Information
+  \begin{tabular}{l c c c }
+    Description & Value & Likelihood
+    benign      & 2     & 65.5\%
+    malignant   & 4     & 34.5\%
+  \end{tabular}
+  \item Missing Attributes: 16
+\end{enumerate}
+
 \subsection{Car Data}
-Transformed to integer values
-
 \subsection{E. Coli Data}
-Removed categorical values
-
 \subsection{Letter Recognition Data}
@@
 \section{Technical Details}
+Any missing attribute values were each replaced with the mode of the samples of the same class.
+No discretization occured as all base algorithms are able to handle continuous data.
+For all datasets, any sort of identification number or code attributes were removed.
+Within the E.
+Coli dataset, the lip and chg catigorical attributes were also removed as they provided minimal information.
+Furthermore, any string values were converted to integers.
+For example, the ``v-high'', ``high'', ``med'' and ``low'' attribute values would have been converted to 0, 1, 2, 3 respectively.
+
 Identification information was removed ...
@@
 How many neighbors ...
+Transformed to integers
+
+\subsection{ID3}
+\begin{tabular}{ |c|c|c| }
+  Dataset            & Max Level & Minimum # of Samples \\
+  Breast Cancer      & None      & SOMETHING            \\
+  Car Cancer         & None      & SOMETHING            \\
+  Letter Recognition & None      & SOMETHING            \\
+  E. Coli            & None      & SOMETHING            \\
+  Mushroom           & None      & SOMETHING
+\end{tabular}
+
+\subsection{Naive Bayes}
+gaussian
+
+\subsection{Adaboost on Naive Bayes}
+number of learners
+
+\subsection{Adaboost on ID3}
+number of learenrs
+
+\subsection{Random Forest}
+number of trees
+
+\subsection{K-Nearest Neighbors}
+k
+distance
 

### 2017-12-06 cs6735/assignment/report.tex
started package section

@@
 
-Identification information was removed ...
-No discretization was performed ...
-Unknown variables from the breast cancer dataset were replaced ...
-Limitations placed on trees ...
-Distributions used for Naïve Bayes ...
-C4.5 continuous variable implementation ...
-Number of trees for random forest ... & size of datasets
-Number of weak learners for adaboost ... & size of datasets
-How many neighbors ...
-Transformed to integers
-
 \subsection{ID3}
@@
 \section{Project Design}
-A Java machine learning framework was first created ...
-The external dependencies include JUnit for unit tests and slfj4 for logging.
-Both work independently of the code written for the machine learning algorithms.
-They functioned as tools to write code and may be completely removed if necessary ...
+A Java machine learning framework was first created to ease the implementation of the six learning algorithms.
+This framework uses JUnit for unit tests and slfj4 to control logging.
+Both work independently of the machine learning algorithms.
+The package hiarchy was modeled off ...
 
-An `Algorithm` interface and `Model` abstract class were created as the high level objects that all algorithms and models implement.
-This abstraction proved extremely useful for ensemble implementation and general code cleanliness.
-The main class where the algorithms are implemented on the datasets is extremely easy to read.
+\begin{enumerate}
+  \item \br{Algorithm}:
+  \item \br{Dataset}:
+  \item \br{Model}:
+  \item \br{KFold}: Implements the KFold cross validation algorithm.
+  \item \br{Report}: The object returned from a k-fold cross validation test....
+  \item \br{Util}: Utility functions used through the machine learning project.
+\end{enumerate}
 
-A `KFold` object was created which implements the cross validation algorithm. This object generates a `Report` on a given algorithm and dataset ...
+\subsection{dt}
+This package contains all of the objects associated with decision trees.
 
-\subsection{Math Package}
+\begin{enumerate}
+  \item \br{Children}:
+  \item \br{ID3}:
+  \item \br{ID3Model}:
+  \item \br{Node}:
+\end{enumerate}
+
+\subsection{ensemble}
+This package contains all of the objects associated with enseble learners.
+
+\begin{enumerate}
+  \item \br{Adaboost}:
+  \item \br{AdaboostModel}:
+  \item \br{Multi-Adaboost}:
+  \item \br{Multi-AdaboostModel}:
+  \item \br{RandomForest}:
+  \item \br{RandomForstModel}:
+\end{enumerate}
+
+\subsection{exceptions}
+This package contains the common exceptions which occur the learning process.
+
+\begin{enumerate}
+  \item \br{AttributeException}:
+  \item \br{DataException}:
+  \item \br{FileException}:
+  \item \br{PredictionException}:
+\end{enumerate}
+
+\subsection{math}
 Data was particularly difficult to handle.
@@
 To accomplish this task, a simple Tuple data structure was created.
-
 Several other useful objects were implemented within the math package such as distance function objects, distribution objects and an object containing useful static methods.
@@
 
-\subsection{Decision Tree Package}
+\begin{enumerate}
+  \item \br{MathException}:
+  \item \br{Matrix}:
+  \item \br{Tuple}:
+  \item \br{Util}:
+  \item \br{Vector}:
+\end{enumerate}
 
-\subsection{Naïve Bayes Package}
-\subsection{Ensemble Package}
-\subsection{Neighbors Package}
+\subsubsection{distance}
+This package contains distance functions for the KNN classifier.
+
+\begin{enumerate}
+  \item \br{DistanceFunction}:
+  \item \br{Euclidian}:
+  \item \br{Hamming}:
+\end{enumerate}
+
+\subsubsection{distribution}
+This package contains distribution implementations for the Naive Bayes classifier.
+
+\begin{enumerate}
+  \item \br{Distribution}:
+  \item \br{GaussianDistribution}:
+\end{enumerate}
+
+\subsection{nb}
+This package contains all of the objects associated with Naive Bayes.
+
+\begin{enumerate}
+  \item \br{Attribute}:
+  \item \br{BayesException}:
+  \item \br{ClassSummary}:
+  \item \br{ContinuousAttribute}:
+  \item \br{DiscreteAttribute}:
+  \item \br{NaiveBayes}:
+  \item \br{NaiveBayesModel}:
+\end{enumerate}
+
+\subsection{neighbors}
+This package contains all of the objects associated with k-nearest neighbors.
+
+\begin{enumerate}
+  \item \br{KNN}:
+  \item \br{KNNModel}:
+  \item \br{KNNException}:
+\end{enumerate}
 
 \section{Results}
-table of results ...
-graph of hyperparameter search ...
+\begin{tabular}{ |c|c|c|c|c|c| }
+  ID3 & Adaboost on ID3 & Random Forest & Naive Bayes & Adaboost on Naive Bayes & K-Nearest Neighbor
+\end{tabular}
+
+graph of hyperparameter search?
 

### 2017-12-06 cs6735/assignment/report.tex
finished data section

@@
 
+\newcommand{\bb}{\textbf}
+\newcommand{\ii}{\textit}
+
 \usepackage{natbib}
 \usepackage{graphicx}
-\usepackage[options ]{algorithm2e}
+\usepackage{bm}
+\usepackage{algorithm2e}
 \usepackage{parskip}
+\usepackage{geometry}
+\usepackage{enumitem}
 
@@
 Six machine learning algorithms were implemented, including both regular and ensemble learning algorithms.
-Each was evaluated on five datasets from the UCI machine learning data repository using 10 times 5-fold cross validation.
-The technical details of the implementation will be described and the results will be analyzed.
+Each was evaluated on five datasets from the UCI Machine Learning data repository using 10 times 5-fold cross validation.
+The technical details of the implementation will be described in this report and the results will be presented and analyzed.
 
@@
 \subsection{Naïve Bayes}
-The Naive Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independance amongst each attribute:
+The Naïve Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independence amongst each attribute:
 
@@
 
-and its application of Bayes thereom:
+and its application of Bayes thereon:
 
@@
 
-Naive Bayes is a practical learning algorithm, receives relatively good results given its preference bias and is easy to implement.
-This algorithm naturally handles both catigorical and continuous data (given a prior is assumed).
+Naïve Bayes is a practical learning algorithm, receives relatively good results given its preference bias and is easy to implement.
+This algorithm naturally handles both categorical and continuous data (given a prior is assumed).
 For each continuous attribute, a Gaussian distribution was assumed.
@@
 
-$$\hat{y}= \underset{k\;\in\;\{1,..K\}} {\mathrm{argmax}} \;\;P(v_k)\prod_{i=1}^mp\left(a_i\;|\;v_k\right)\prod_{j=m}^nP\left(a_j\;|\;v_k\right)\;\;$$
+$$\hat{y}= \mathrm{argmax}_{k\in\{1,..K\}} P(v_k)\prod_{i=1}^mp\left(a_i|v_k\right)\prod_{j=m}^nP\left(a_j|v_k\right)$$
 
 where $P$ is the probability, $p$ is the gaussian probability density function and $K$ is the number of distinct targets.
-In this equation, the first m attributes are continous whereas the later are catigorical.
+In this equation, the first m attributes are continuous whereas the later are catigorical.
 During training, the data $S$ is split by lables into subsets ${S_1,...,S_n}$ where $n$ is the number of different classes.
@@
 Subsequently, for each attribute value $a_i$ of each attribute $a$, we estimate $P(a_i|v_k)$ or $p$.
-We are not able to immidiately calculate $p(a_i|v_k)$ as attribute $a$ is a continous attribute.
+We are not able to immediately calculate $p(a_i|v_k)$ as attribute $a$ is a continous attribute.
 
@@
 The Adaboost algorithm is easily implemented on weak learners which are parameterized by sample weights.
-Neither Naive Bayes or ID3 natively implement weighted training.
+Neither Naïve Bayes or ID3 natively implement weighted training.
 Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights.
@@
 
-To implement multiclass adaboost, $K$ adaboost models are trained where $K$ is the total number of distint classes.
+To implement multiclass adaboost, $K$ adaboost models are trained where $K$ is the total number of distant classes.
 For each adaboost model, one target is selected as the $+1$ adaboost target and the other become the $-1$ target.
@@
 
-\subsubsection{Adaboost on Naive Bayes}
-Naive Bayes is an inherently weak learner due to its assumption of conditional independance amongst attributes.
-This fact introduces a large amount of preference bias which makes a Naive Bayes and ideal candidate for the Adaboost algorithm.
+\subsubsection{Adaboost on Naïve Bayes}
+Naïve Bayes is an inherently weak learner due to its assumption of conditional independence amongst attributes.
+This fact introduces a large amount of preference bias which makes a Naïve Bayes and ideal candidate for the Adaboost algorithm.
 
 \subsubsection{Adaboost on ID3}
-The ID3 algorithm does not introduce a large amount of preference bias and often overfits if allowed to train to completion.
+The ID3 algorithm does not introduce a large amount of preference bias and often overfitting if allowed to train to completion.
 Therefore, to implement Adaboost on ID3, the depth of the trees were limited to one level.
-This type of tree is known as a \textit{decision stump}.
+This type of tree is known as a \ii{decision stump}.
 
 \subsection{Random Forest}
-Random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfititng to the training set.
+Random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfitting to the training set.
 This method contains many similarities to the adaboost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests.
-For a predifined number of iterations, a subset of the of the training data is selected with replacement.
+For a predefined number of iterations, a subset of the of the training data is selected with replacement.
 The new training set is then used to train a decision tree to completion and added to tree is added to a list.
@@
 The K-Nearest Neighbor algorithm is an instance based learning algorithm which makes predictions by finding the $k$ nearest neighbors of a sample $x$ and using the most common class as the predicted class for that sample.
-This algorithm can be used with both catigorical and continuous data.
-For this implementation, Euclidian distance was used for continous variables and Hamming distance was used for catigorical data.
+This algorithm can be used with both categorical and continuous data.
+For this implementation, Euclidian distance was used for continuous variables and Hamming distance was used for categorical data.
 
@@
 \subsection{Breast Cancer Data}
-\begin{enumerate}
-  \item Title: Wisconsin Diagnostic Breast Cancer
-  \item Date: November 1995
-  \item Number of Samples: 569
-  \item Number of Attributes: 10
+\begin{itemize}[leftmargin=*]
+  \item[] \bb{Title}: Wisconsin Diagnostic Breast Cancer
+  \item[] \bb{Date}: November 1995
+  \item[] \bb{Number of Samples}: 569
+  \item[] \bb{Number of Attributes}: 10
+  \item[] \bb{Attribute Information}:
+  \item[]
   \begin{tabular}{l c c c }
-    Description                  & Value     & Type
+    \bb{Description}             & \bb{Values} & \bb{Type} \\
     Sample Code Number           & id number   & Discrete  \\
@@
   \end{tabular}
-  \item Class Information
-  \begin{tabular}{l c c c }
-    Description & Value & Likelihood
-    benign      & 2     & 65.5\%
-    malignant   & 4     & 34.5\%
+  \item[] \bb{Class Target}: Neoplasm
+  \item[] \bb{Class Information}:
+  \item[]
+  \begin{tabular}{l c c c c }
+    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
+    Benign           & 2          & 357        & 65.5\%          \\
+    Malignant        & 4          & 212        & 34.5\%
   \end{tabular}
-  \item Missing Attributes: 16
-\end{enumerate}
+  \item[] \bb{Missing Attributes}: 16
+\end{itemize}
 
 \subsection{Car Data}
+\begin{itemize}[leftmargin=*]
+  \item[] \bb{Title}: Car Evaluation Database
+  \item[] \bb{Date}: June 1997
+  \item[] \bb{Number of Samples}: 1728
+  \item[] \bb{Number of Attributes}: 6
+  \item[] \bb{Attribute Information}:
+  \item[]
+  \begin{tabular}{l c c c }
+    \bb{Description} & \bb{Values}            & \bb{Type} \\
+    buying           & v-high, high, med, low & Discrete  \\
+    maint            & v-high, high, med, low & Discrete  \\
+    doors            & 2, 3, 4, 5-more        & Discrete  \\
+    persons          & 2, 4, more             & Discrete  \\
+    lug\_boot        & small, med, big        & Discrete  \\
+    safety           & low, med, high         & Discrete
+  \end{tabular}
+  \item[] \bb{Class Target}: Car Quality
+  \item[] \bb{Class Information}:
+  \item[]
+  \begin{tabular}{l c c c c }
+    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
+    Unacceptable     & unacc      & 1210       & 70.023\%        \\
+    Acceptable       & acc        & 384        & 22.222\%        \\
+    Good             & good       & 69         & 3.993\%         \\
+    Very Good        & v-good     & 65         & 3.762\%
+  \end{tabular}
+  \item[] \bb{Missing Attributes}: none
+\end{itemize}
+
 \subsection{E. Coli Data}
+\begin{itemize}[leftmargin=*]
+  \item[] \bb{Title}: Protein Localization Sites
+  \item[] \bb{Date}: September 1997
+  \item[] \bb{Number of Samples}: 336
+  \item[] \bb{Number of Attributes}: 8
+  \item[] \bb{Attribute Information}:
+  \item[]
+  \begin{tabular}{l c c c }
+    \bb{Description} & \bb{Values}       & \bb{Type}  \\
+    Sequence Name    &  Accession Number & Discrete   \\
+    mcg              & 0.00 - 0.89       & Continuous \\
+    gvh              & 0.16 - 1.00       & Continuous \\
+    lip              & 0.48 - 1.00       & Discrete   \\
+    chg              & 0.50 - 1.00       & Discrete   \\
+    aac              & 0.00 - 0.88       & Continuous \\
+    alm1             & 0.03 - 1.00       & Continuous \\
+    alm2             & 0.00 - 0.99       & Continuous
+  \end{tabular}
+  \item[] \bb{Class Target}:  Localization Site
+  \item[] \bb{Class Information}:
+  \item[]
+  \begin{tabular}{l c c c c }
+    \bb{Description}           & \bb{Value} & \bb{Count} & \bb{Percentage} \\
+    Cytoplasm                  & cp         & 143        & 42.56\%         \\
+    Inner Membrane             & im         & 77         & 22.92\%         \\
+    Perisplasm                 & pp         & 52         & 15.48\%         \\
+    Inner Membrane Uncleavable & imU        & 35         & 10.42\%         \\
+    Outer Membrane             & om         & 20         & 5.95\%          \\
+    Outer Membrane             & omL        & 5          & 1.49\%          \\
+    Inner Membrane Lipoprotein & imL        & 2          & 0.59\%          \\
+    Inner Membrane Cleavable   & imS        & 2          & 0.59\%
+  \end{tabular}
+  \item[] \bb{Missing Attributes}: none
+\end{itemize}
+
 \subsection{Letter Recognition Data}
+\begin{itemize}[leftmargin=*]
+  \item[] \bb{Title}: Letter Image Recognition Data
+  \item[] \bb{Date}: January 1991
+  \item[] \bb{Number of Samples}: 20000
+  \item[] \bb{Number of Attributes}: 16
+  \item[] \bb{Attribute Information}:
+  \item[]
+  \begin{tabular}{l c c c }
+    \bb{Description} & \bb{Values}            & \bb{Type}  \\
+    x-box	           & 0 - 9                  & Continuous \\
+    y-box	           & 0 - 9                  & Continuous \\
+    width	           & 0 - 9                  & Continuous \\
+    high 	           & 0 - 9                  & Continuous \\
+    onpix	           & 0 - 9                  & Continuous \\
+    x-bar	           & 0 - 9                  & Continuous \\
+    y-bar	           & 0 - 9                  & Continuous \\
+    x2bar	           & 0 - 9                  & Continuous \\
+    y2bar	           & 0 - 9                  & Continuous \\
+    xybar	           & 0 - 9                  & Continuous \\
+    x2ybr	           & 0 - 9                  & Continuous \\
+    xy2br	           & 0 - 9                  & Continuous \\
+    x-ege	           & 0 - 9                  & Continuous \\
+    xegvy	           & 0 - 9                  & Continuous \\
+    y-ege	           & 0 - 9                  & Continuous \\
+    yegvx	           & 0 - 9                  & Continuous
+  \end{tabular}
+  \item[] \bb{Class Target}: Letter
+  \item[] \bb{Class Information}:
+  \item[]
+  \begin{tabular}{l c c c c }
+    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
+    Letter A                & A          & 789        & 0.04\% \\
+    Letter B                & B          & 766        & 0.04\% \\
+    Letter C                & C          & 736        & 0.04\% \\
+    Letter D                & D          & 805        & 0.04\% \\
+    Letter E                & E          & 768        & 0.04\% \\
+    Letter F                & F          & 775        & 0.04\% \\
+    Letter G                & G          & 773        & 0.04\% \\
+    Letter H                & H          & 734        & 0.04\% \\
+    Letter I                & I          & 755        & 0.04\% \\
+    Letter J                & J          & 747        & 0.04\% \\
+    Letter K                & K          & 739        & 0.04\% \\
+    Letter L                & L          & 761        & 0.04\% \\
+    Letter M                & M          & 792        & 0.04\% \\
+    Letter N                & N          & 783        & 0.04\% \\
+    Letter O                & O          & 753        & 0.04\% \\
+    Letter P                & P          & 803        & 0.04\% \\
+    Letter Q                & Q          & 783        & 0.04\% \\
+    Letter R                & R          & 758        & 0.04\% \\
+    Letter S                & S          & 748        & 0.04\% \\
+    Letter T                & T          & 796        & 0.04\% \\
+    Letter U                & U          & 813        & 0.04\% \\
+    Letter V                & V          & 764        & 0.04\% \\
+    Letter W                & W          & 752        & 0.04\% \\
+    Letter X                & X          & 787        & 0.04\% \\
+    Letter Y                & Y          & 786        & 0.04\% \\
+    Letter Z                & Z          & 734        & 0.04\%
+  \end{tabular}
+  \item[] \bb{Missing Attributes}: none
+\end{itemize}
+
 \subsection{Mushroom Data}
+\begin{itemize}[leftmargin=*]
+  \item[] \bb{Title}: Mushroom Database
+  \item[] \bb{Date}: 27 April 1987
+  \item[] \bb{Number of Samples}: 8124
+  \item[] \bb{Number of Attributes}: 22
+  \item[] \bb{Attribute Information}:
+  \item[]
+  \begin{tabular}{l c c c }
+    \bb{Description}         & \bb{Values}             & \bb{Type} \\
+    cap-shape                & b,c,x,f,k,s             & Discrete  \\
+    cap-surface              & f,g,y,s                 & Discrete  \\
+    cap-color                & n,b,c,g,r,p,u,e,w,y     & Discrete  \\
+    bruises?                 & t,f                     & Discrete  \\
+    odor                     & a,l,c,y,f,m,n,p,s       & Discrete  \\
+    gill-attachment          & a,d,f,n                 & Discrete  \\
+    gill-spacing             & c,w,d                   & Discrete  \\
+    gill-size                & b,n                     & Discrete  \\
+    gill-color               & k,n,b,h,g,r,o,p,u,e,w,y & Discrete  \\
+    stalk-shape              & e,t                     & Discrete  \\
+    stalk-root               & b,c,u,e,z,r,?           & Discrete  \\
+    stalk-surface-above-ring & f,y,k,s                 & Discrete  \\
+    stalk-surface-below-ring & f,y,k,s                 & Discrete  \\
+    stalk-color-above-ring   & n,b,c,g,o,p,e,w,y       & Discrete  \\
+    stalk-color-below-ring   & n,b,c,g,o,p,e,w,y       & Discrete  \\
+    veil-type                & p,u                     & Discrete  \\
+    veil-color               & n,o,w,y                 & Discrete  \\
+    ring-number              & n,o,t                   & Discrete  \\
+    ring-type                & c,e,f,l,n,p,s,z         & Discrete  \\
+    spore-print-color        & k,n,b,h,r,o,u,w,y       & Discrete  \\
+    population               & a,c,n,s,v,y             & Discrete  \\
+    habitat                  & g,l,m,p,u,w,d           & Discrete
+  \end{tabular}
+  \item[] \bb{Class Target}: Edibility
+  \item[] \bb{Class Information}:
+  \item[]
+  \begin{tabular}{l c c c c }
+    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
+    Edible           & e          & 4208       & 51.80\%        \\
+    Poisonous        & p          & 3916       & 48.20\%
+  \end{tabular}
+  \item[] \bb{Missing Attributes}: 2480 (all for attribute \#11)
+\end{itemize}
 
 \section{Technical Details}
-Any missing attribute values were each replaced with the mode of the samples of the same class.
-No discretization occured as all base algorithms are able to handle continuous data.
+Missing attribute values within the breast cancer dataset were replaced with the mode of the samples of the same class.
+For the mushroom dataset, as the amount of missing values for attribute 11 was very large, the missing values themselves were simply treated as another category.
+No discretization occurred as all base algorithms are able to handle continuous data.
 For all datasets, any sort of identification number or code attributes were removed.
 Within the E.
-Coli dataset, the lip and chg catigorical attributes were also removed as they provided minimal information.
+Coli dataset, the lip and chg categorical attributes were also removed as they provided minimal information.
 Furthermore, any string values were converted to integers.
@@
 \begin{tabular}{ |c|c|c| }
-  Dataset            & Max Level & Minimum # of Samples \\
+  Dataset            & Max Level & Minimum \# of Samples \\
   Breast Cancer      & None      & SOMETHING            \\
@@
 
-\subsection{Naive Bayes}
+\subsection{Naïve Bayes}
 gaussian
 
-\subsection{Adaboost on Naive Bayes}
+\subsection{Adaboost on Naïve Bayes}
 number of learners
@@
 
-\begin{enumerate}
-  \item \br{Algorithm}:
-  \item \br{Dataset}:
-  \item \br{Model}:
-  \item \br{KFold}: Implements the KFold cross validation algorithm.
-  \item \br{Report}: The object returned from a k-fold cross validation test....
-  \item \br{Util}: Utility functions used through the machine learning project.
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{Algorithm}:
+  \item[] \bb{Dataset}:
+  \item[] \bb{Model}:
+  \item[] \bb{KFold}: Implements the KFold cross validation algorithm.
+  \item[] \bb{Report}: The object returned from a k-fold cross validation test....
+  \item[] \bb{Util}: Utility functions used through the machine learning project.
 \end{enumerate}
@@
 
-\begin{enumerate}
-  \item \br{Children}:
-  \item \br{ID3}:
-  \item \br{ID3Model}:
-  \item \br{Node}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{Children}:
+  \item[] \bb{ID3}:
+  \item[] \bb{ID3Model}:
+  \item[] \bb{Node}:
 \end{enumerate}
@@
 
-\begin{enumerate}
-  \item \br{Adaboost}:
-  \item \br{AdaboostModel}:
-  \item \br{Multi-Adaboost}:
-  \item \br{Multi-AdaboostModel}:
-  \item \br{RandomForest}:
-  \item \br{RandomForstModel}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{Adaboost}:
+  \item[] \bb{AdaboostModel}:
+  \item[] \bb{Multi-Adaboost}:
+  \item[] \bb{Multi-AdaboostModel}:
+  \item[] \bb{RandomForest}:
+  \item[] \bb{RandomForstModel}:
 \end{enumerate}
@@
 
-\begin{enumerate}
-  \item \br{AttributeException}:
-  \item \br{DataException}:
-  \item \br{FileException}:
-  \item \br{PredictionException}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{AttributeException}:
+  \item[] \bb{DataException}:
+  \item[] \bb{FileException}:
+  \item[] \bb{PredictionException}:
 \end{enumerate}
@@
 
-\begin{enumerate}
-  \item \br{MathException}:
-  \item \br{Matrix}:
-  \item \br{Tuple}:
-  \item \br{Util}:
-  \item \br{Vector}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{MathException}:
+  \item[] \bb{Matrix}:
+  \item[] \bb{Tuple}:
+  \item[] \bb{Util}:
+  \item[] \bb{Vector}:
 \end{enumerate}
@@
 
-\begin{enumerate}
-  \item \br{DistanceFunction}:
-  \item \br{Euclidian}:
-  \item \br{Hamming}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{DistanceFunction}:
+  \item[] \bb{Euclidian}:
+  \item[] \bb{Hamming}:
 \end{enumerate}
@@
 \subsubsection{distribution}
-This package contains distribution implementations for the Naive Bayes classifier.
+This package contains distribution implementations for the Naïve Bayes classifier.
 
-\begin{enumerate}
-  \item \br{Distribution}:
-  \item \br{GaussianDistribution}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{Distribution}:
+  \item[] \bb{GaussianDistribution}:
 \end{enumerate}
@@
 \subsection{nb}
-This package contains all of the objects associated with Naive Bayes.
+This package contains all of the objects associated with Naïve Bayes.
 
-\begin{enumerate}
-  \item \br{Attribute}:
-  \item \br{BayesException}:
-  \item \br{ClassSummary}:
-  \item \br{ContinuousAttribute}:
-  \item \br{DiscreteAttribute}:
-  \item \br{NaiveBayes}:
-  \item \br{NaiveBayesModel}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{Attribute}:
+  \item[] \bb{BayesException}:
+  \item[] \bb{ClassSummary}:
+  \item[] \bb{ContinuousAttribute}:
+  \item[] \bb{DiscreteAttribute}:
+  \item[] \bb{NaïveBayes}:
+  \item[] \bb{NaïveBayesModel}:
 \end{enumerate}
@@
 
-\begin{enumerate}
-  \item \br{KNN}:
-  \item \br{KNNModel}:
-  \item \br{KNNException}:
+\begin{enumerate}[leftmargin=*]
+  \item[] \bb{KNN}:
+  \item[] \bb{KNNModel}:
+  \item[] \bb{KNNException}:
 \end{enumerate}
@@
 \section{Results}
+\begin{table}
   \begin{tabular}{ |c|c|c|c|c|c| }
-  ID3 & Adaboost on ID3 & Random Forest & Naive Bayes & Adaboost on Naive Bayes & K-Nearest Neighbor
+    \hline
+    Breast Cancer           & Car      & Letter   & E. Coli  & Mushroom \\ \hline
+    Adaboost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    ID3                     & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    Random Forest           & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    Naïve Bayes             & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    Adaboost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    K-Nearest Neighbor      & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
   \end{tabular}
+  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
+\end{table}
 

### 2017-12-06 cs6735/assignment/report.tex
few changes

@@
     \item ID3
-    \item Adaboost on ID3
+    \item AdaBoost on ID3
     \item Random Forest
     \item Naïve Bayes
-    \item Adaboost on Naïve Bayes
+    \item AdaBoost on Naïve Bayes
     \item K-nearest neighbors
@@
 
-\subsection{Adaboost} \label{adaboost}
-Adaboost is a boosting algorithm that was first introduced in 1995 by Freunb Schapire.
+\subsection{AdaBoost} \label{adaboost}
+AdaBoost is a boosting algorithm that was first introduced in 1995 by Freunb Schapire.
 This type of ensemble learning uses a set of weak learners to reduce bias and become a strong learner.
@@
 The target values are assumed be to in the set ${+1, -1}$.
-The Adaboost algorithm is easily implemented on weak learners which are parameterized by sample weights.
+The AdaBoost algorithm is easily implemented on weak learners which are parameterized by sample weights.
 Neither Naïve Bayes or ID3 natively implement weighted training.
@@
 
-\subsubsection{Adaboost on Naïve Bayes}
+\subsubsection{AdaBoost on Naïve Bayes}
 Naïve Bayes is an inherently weak learner due to its assumption of conditional independence amongst attributes.
-This fact introduces a large amount of preference bias which makes a Naïve Bayes and ideal candidate for the Adaboost algorithm.
+This fact introduces a large amount of preference bias which makes a Naïve Bayes and ideal candidate for the AdaBoost algorithm.
 
-\subsubsection{Adaboost on ID3}
+\subsubsection{AdaBoost on ID3}
 The ID3 algorithm does not introduce a large amount of preference bias and often overfitting if allowed to train to completion.
-Therefore, to implement Adaboost on ID3, the depth of the trees were limited to one level.
+Therefore, to implement AdaBoost on ID3, the depth of the trees were limited to one level.
 This type of tree is known as a \ii{decision stump}.
@@
 
-\subsection{Adaboost on Naïve Bayes}
+\subsection{AdaBoost on Naïve Bayes}
 number of learners
 
-\subsection{Adaboost on ID3}
-number of learenrs
+\subsection{AdaBoost on ID3}
+number of learners
 
@@
 
-\subsection{dt}
+\subsection{tree}
 This package contains all of the objects associated with decision trees.
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{Adaboost}:
-  \item[] \bb{AdaboostModel}:
-  \item[] \bb{Multi-Adaboost}:
-  \item[] \bb{Multi-AdaboostModel}:
+  \item[] \bb{AdaBoost}:
+  \item[] \bb{AdaBoostModel}:
+  \item[] \bb{Multi-AdaBoost}:
+  \item[] \bb{Multi-AdaBoostModel}:
   \item[] \bb{RandomForest}:
@@
 
-\subsection{nb}
+\subsection{bayes}
 This package contains all of the objects associated with Naïve Bayes.
@@
     Breast Cancer           & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    Adaboost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    AdaBoost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
     ID3                     & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
@@
     Naïve Bayes             & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
-    Adaboost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    AdaBoost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
     K-Nearest Neighbor      & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline

### 2017-12-08 cs6735/assignment/report.tex
almost done results!!

@@
   \end{tabular}
-  \item[] \bb{Missing Attributes}: none
+  \item[] \bb{Missing Attributes}: None
 \end{itemize}
@@
 \section{Technical Details}
-Missing attribute values within the breast cancer dataset were replaced with the mode of the samples of the same class.
-For the mushroom dataset, as the amount of missing values for attribute 11 was very large, the missing values themselves were simply treated as another category.
-No discretization occurred as all base algorithms are able to handle continuous data.
-For all datasets, any sort of identification number or code attributes were removed.
+Missing attribute values within both the breast cancer dataset and mushroom dataset treated as another category.
+Attempts were initially made to replace the missing values; however, no improvements with accuracy were observed.
+Furthermore, no discretization occurred as all base algorithms are able to handle continuous data.
+For each dataset, any sort of identification number or code attributes were removed.
 Within the E.
@@
 \subsection{ID3}
-\begin{tabular}{ |c|c|c| }
-  Dataset            & Max Level & Minimum \# of Samples \\
-  Breast Cancer      & None      & SOMETHING            \\
-  Car Cancer         & None      & SOMETHING            \\
-  Letter Recognition & None      & SOMETHING            \\
-  E. Coli            & None      & SOMETHING            \\
-  Mushroom           & None      & SOMETHING
+\begin{table}
+  \caption{The }
+  \begin{tabular}{ |c|c| } \hline
+    \bb{Dataset}       & \bb{Minimum \# of Samples} \\ \hline
+    Breast Cancer      & 1                          \\ \hline
+    Car                & 1                          \\ \hline
+    E. Coli            & 2                          \\ \hline
+    Letter Recognition & 1                          \\ \hline
+    Mushroom           & 1                          \\ \hline
+  \end{tabular}
+\end{table}
+
+\subsection{Naïve Bayes}
+\begin{tabular}{ |c|c| } \hline
+  \bb{Dataset}       & \bb{Distribution} \\ \hline
+  Breast Cancer      & None              \\ \hline
+  Car                & None              \\ \hline
+  E. Coli            & Gaussian          \\ \hline
+  Letter Recognition & Gaussian          \\ \hline
+  Mushroom           & None              \\ \hline
 \end{tabular}
 
-\subsection{Naïve Bayes}
-gaussian
+\subsection{AdaBoost on ID3}
+\begin{tabular}{ |c|c|c| } \hline
+  \bb{Dataset}       & \bb{Max Level} & \bb{\# of Learners} & Proportion of Samples \\ \hline
+  Breast Cancer      & 1              & 100                 & 0.50                  \\ \hline
+  Car                & 1              & 100                 & 0.70                  \\ \hline
+  E. Coli            & 1              & 100                 & 0.50                   \\ \hline
+  Letter Recognition & 1              & IDK                 & IDK                   \\ \hline
+  Mushroom           & 1              & 10                  & 0.30                   \\ \hline
+\end{tabular}
 
 \subsection{AdaBoost on Naïve Bayes}
-number of learners
-
-\subsection{AdaBoost on ID3}
-number of learners
+\begin{tabular}{ |c|c|c| } \hline
+  \bb{Dataset}       & \bb{Distribution} & \bb{\# of Learners} & Proportion of Samples & \\ \hline
+  Breast Cancer      & None              & 100                 & 0.70                    \\ \hline
+  Car                & None              & 100                 & 0.40                    \\ \hline
+  E. Coli            & Gaussian          & 150                 & 0.30                     \\ \hline
+  Letter Recognition & Gaussian          & IDK                 & IDK                     \\ \hline
+  Mushroom           & None              & 10                  & 0.30                     \\ \hline
+\end{tabular}
 
 \subsection{Random Forest}
-number of trees
+\begin{tabular}{ |c|c| } \hline
+  \bb{Dataset}       & \bb{\# of Learners} & Proportion of Samples \\ \hline
+  Breast Cancer      & 120                 & 0.70                  \\ \hline
+  Car                & 200                 & 0.60                  \\ \hline
+  E. Coli            & 120                 & 0.70                  \\ \hline
+  Letter Recognition & 50                  & 0.30                  \\ \hline
+  Mushroom           & 10                  & 0.30                  \\ \hline
+\end{tabular}
 
 \subsection{K-Nearest Neighbors}
-k
-distance
+\begin{tabular}{ |c|c| } \hline
+  \bb{Dataset}       & \bb{K}    & Distance \\ \hline
+  Breast Cancer      & 1                   & Hamming \\ \hline
+  Car                & 1                   & Hamming \\ \hline
+  E. Coli            & 1                   & Euclidian \\ \hline
+  Letter Recognition & 1                   & Euclidian \\ \hline
+  Mushroom           & 1                   & Hamming \\ \hline
+\end{tabular}
 
@@
     \hline
-    Breast Cancer           & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    AdaBoost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
-    ID3                     & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
-    Random Forest           & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
-    Naïve Bayes             & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
-    AdaBoost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
-    K-Nearest Neighbor      & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
+    Algorithm               Breast Cancer   & Car      & Letter   & E. Coli  & Mushroom \\ \hline
+    ID3                     & 97.994\%      & 90.634\% & 81.909\% & 100.00\% & 99.998\% \\ \hline
+    Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 100.00\% & 95.952\% \\ \hline
+    AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 97.590\% \\ \hline
+    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 77.725\% & 100.00\% & 100.00\% \\ \hline
+    Random Forest           & 97.592\%      & 91.175\% & 84.316\% & 100.00\% & 100.00\% \\ \hline
+    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 87.886\% & 100.00\% & 100.00\% \\ \hline
+  \end{tabular}
+  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
+\end{table}
+
+\begin{table}
+  \begin{tabular}{ |c|c|c|c|c|c| }
+    \hline
+    Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
+    ID3                     & 1.465\%       & 4.061\%  & 8.981\%  & 100.00\% & 0.017\% \\ \hline
+    Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 100.00\% & 2.128\% \\ \hline
+    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 2.038\% \\ \hline
+    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 9.275\%  & 100.00\% & 100.00\% \\ \hline
+    Random Forest           & 1.597\%       & 5.171\%  & 9.711\%  & 100.00\% & 100.00\% \\ \hline
+    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 7.001\%  & 100.00\% & 100.00\% \\ \hline
   \end{tabular}

### 2017-12-08 cs6735/assignment/report.tex
finished mush results

@@
     Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 100.00\% & 95.952\% \\ \hline
-    AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 97.590\% \\ \hline
-    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 77.725\% & 100.00\% & 100.00\% \\ \hline
-    Random Forest           & 97.592\%      & 91.175\% & 84.316\% & 100.00\% & 100.00\% \\ \hline
-    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 87.886\% & 100.00\% & 100.00\% \\ \hline
+    AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 99.446\% \\ \hline
+    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 77.725\% & 100.00\% & 99.744\% \\ \hline
+    Random Forest           & 97.592\%      & 91.175\% & 84.316\% & 100.00\% & 99.865\% \\ \hline
+    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 87.886\% & 100.00\% & 99.826\% \\ \hline
   \end{tabular}
@@
     Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 100.00\% & 2.128\%  \\ \hline
-    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 2.038\% \\ \hline
-    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 9.275\%  & 100.00\% & 100.00\% \\ \hline
-    Random Forest           & 1.597\%       & 5.171\%  & 9.711\%  & 100.00\% & 100.00\% \\ \hline
-    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 7.001\%  & 100.00\% & 100.00\% \\ \hline
+    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 1.081\%  \\ \hline
+    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 9.275\%  & 100.00\% & 0.652\%  \\ \hline
+    Random Forest           & 1.597\%       & 5.171\%  & 9.711\%  & 100.00\% & 0.702\%  \\ \hline
+    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 7.001\%  & 100.00\% & 0.433\%  \\ \hline
   \end{tabular}

### 2017-12-09 cs6735/assignment/report.tex
add ece labs

@@
     Algorithm               Breast Cancer   & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    ID3                     & 97.994\%      & 90.634\% & 81.909\% & 100.00\% & 99.998\% \\ \hline
-    Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 100.00\% & 95.952\% \\ \hline
+    ID3                     & 97.994\%      & 90.634\% & 81.909\% & 88.234\% & 99.998\% \\ \hline
+    Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 65.048\% & 95.952\% \\ \hline
     AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 99.446\% \\ \hline
@@
     Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    ID3                     & 1.465\%       & 4.061\%  & 8.981\%  & 100.00\% & 0.017\%  \\ \hline
-    Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 100.00\% & 2.128\%  \\ \hline
+    ID3                     & 1.465\%       & 4.061\%  & 8.981\%  & 3.492\% & 0.017\%  \\ \hline
+    Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 1.328\% & 2.128\%  \\ \hline
     AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 1.081\%  \\ \hline

### 2017-12-09 ece3221/lab5/lab5.c

@@ -1,0 +1,97 @@
+//=========================================
+// ECE 3221 CODE25 Reader - R.Tervo 2016
+//=========================================
+// requires barcode wand on DE2 PS2 port
+//=========================================
+//=========================================
+// global pointers to DE2 Board I/O ports
+volatile unsigned int *leds = (unsigned int *) 0x8880;
+volatile unsigned int *hexdisplay = (unsigned int *) 0x88A0;
+volatile unsigned int *hexcontrol = (unsigned int *) 0x88B0;
+volatile unsigned int *ps2 = (unsigned int *) 0x88F0;
+
+volatile int *MONITOR = (char *)0x00008840;
+volatile int *WAVAIL = (int *)0x00008844;
+//=================================================
+// this program reads the barcode wand and
+// display the width (time) of the most
+// recent two bars together as white:black
+// on the hex display. The total number of
+// black bars counted appears on the LEDs.
+//=================================================
+main( ){
+  int whitetime, blacktime, count = 0;
+  double ratio;
+
+  *hexcontrol = 0x01FF; // enable hex display with 8 digits
+  *hexdisplay = 0x0000; // initial hex display value
+
+  char bars[100];
+  char tmp;
+
+  char lookup[10] = {6, 17, 9, 24, 5, 20, 12, 3, 18, 10};
+
+  while(1) {
+	count = 0;
+    do {
+      while( (*ps2 & 0x10) ){ }; // wait for ps2 LOW
+      whitetime = *ps2 >> 8; // read the white bar time / 16
+      while( !(*ps2 & 0x10)){ }; // wait for ps2 HIGH
+      blacktime = *ps2 >> 8; // read the black bar time / 16
+
+	  ratio = ((double)blacktime)/whitetime;
+	  if(ratio > 1.5) {
+		  outchar('1');
+		  bars[count] = 1;
+	  } else {
+		  outchar('0');
+		  bars[count] = 0;
+	  }
+
+      *hexdisplay = (whitetime << 16) | blacktime; // update white:black display
+	  count++;
+    } while(whitetime < 0x1000);
+    outchar('\n');
+
+	int index = 2, i, j, k;
+	for(i = 0; i < (count-6)/5; i++) {
+		tmp = 0;
+		int ans = -1;
[…]

### 2017-12-10 cs6735/assignment/report.tex
almost finished report

@@
     \item Car Data
-    \item Ecoli Data
+    \item E Coli. Data
     \item Mushroom Data
   \end{enumerate}
-  \item Create report of the experimental study including:
+  \item Create a report of the experimental study including:
   \begin{enumerate}
@@
     \item Design of your programming implementation (data structures, overall program structure).
-    \item Report and analysis of your experimental results using using 10 times 5-fold cross-validation (include mean, standard deviation of accuracies).
+    \item Report and analysis of your experimental results using 10 times 5-fold cross-validation (include mean, standard deviation of accuracies).
     \item Comparison and discussion of the algorithms with respect to the experimental results.
@@
 \section{Algorithms}
-For this study, six different algorithms; however, only the five unique algorithms are described in this section.
-Both the ID3 decision tree and Naïve Bayes algorithms were applied to the adaboost ensemble algorithm as weak learners.
+For this study, we used six different algorithms; however, only the five unique algorithms were implemented.
+Due to the design of the program, both the ID3 decision tree and Naïve Bayes algorithms could be given to the AdaBoost ensemble algorithm as a weak learner.
 
 \subsection{ID3}
-The Iterative Dichotomiser 3 (ID3) algorithm is a decision tree algorithm used to efficiently develop decision trees \cite{Quinlan:1986:IDT:637962.637969}.
-This algorithm was developed for situations where there are large amount of attributes and training sets which contain many attributes, but there was the need to be able to efficiently develop relatively well performing decision trees.
+The Iterative Dichotomiser 3 (ID3) algorithm is an algorithm used to efficiently create decision trees \cite{Quinlan:1986:IDT:637962.637969}.
+ID3 was developed for situations with large datasets and the need for the efficient creation of a decision tree.
 
-The algorithm as described by Mitchell \cite{Mitchell:1997:ML:541177} was implmented for this assignment.
-The operations begin at the root node with a set of catigorical, labled data $S$.
-The attribute $A$ which introduces the largest information gain is chosen to split on.
-This is an exhaustive process which checks all remaining attributes.
-This process imediatly stops if there are no possible subsets (identical samples have same class label) or the split is not statistically significant (positive information gain).
-If these stopping conditions are not met, the data $S$ is split using attribute $A$ into subsets ${S_1,...,S_n}$ where $n$ is the amount of different categories of attribute $A$.
-A new node is then created for each subset.
-If the entropy of a new node is $0$ or the sample count is $1$, then the node is turned into a leaf and the splitting operation ends.
-Furthermore, two additional early stopping conditions are implemented.
-Max tree level and minimum number of samples attributes are initially set at the start of training.
+Initially, the ID3 algorithm described by Thomas Mitchell \cite{Mitchell:1997:ML:541177} was implemented.
+It begins at the root node with a set of categorical, labeled data $S$.
+The attribute $a$ which introduces the largest information gain is chosen and the node splits on that attribute.
+Subsets ${S_1,...,S_n}$ are used to create $n$ children nodes where $n$ is the amount of distinct values for attribute $a$.
+This continues recursively until one of several terminating conditions are met.
+For example, the process ends if there are no more possible subsets, the split is not statistically significant (does not introduce positive information gain) or the entropy is $0$.
+Furthermore, two early stopping conditions were implemented including a max tree level and a minimum number of samples.
 
-After the initial ID3 algorithm was implemented, furthure enhancements were made to allow for continuous data to be used.
+After this initial ID3 algorithm was implemented, further enhancements were made to allow for continuous data to be used.
 This enhancement was taken from the C4.5 as developed by Ross Quinlan \citep{c45algorithm}.
-Given a continuous attribute $A$, we temporarily sort the data $S$.
-After the data is sorted, we iteratively determine a threshhold to split the data as the maximize the information gain.
-To test potential threshholds, we find two sequential numbers which are not of the same category and split at the midway point of the two values.
-This enhancements saves an a large amount of time for each continuous attribute found within the datasets as descritization does not need to occur.
+Given a continuous attribute $a$, we temporarily sort the data $S$.
+After the data is sorted, we iteratively determine the threshold to split the data that maximizes the information gain.
+To test potential thresholds, we find two sequential numbers which are not of the same class and split at the midway point of the two values.
+This enhancements saves an a large amount of time for each continuous attribute found within the datasets as discretization does not need to occur.
 Furthermore, this algorithm chooses the optimal threshhold to split the data which improves classification accuracy.
@@
 
-To implement multiclass adaboost, $K$ adaboost models are trained where $K$ is the total number of distant classes.
-For each adaboost model, one target is selected as the $+1$ adaboost target and the other become the $-1$ target.
-The target value associated with the most positive prediction becomes the predicted class.
+To multiclass classification problems, the SAMME AdaBoost algorithm \cite{samme} was implemented.
+This algorithm sees the addition of $log(|v|-1)$, where $|v|$ is the number of classes, to the alpha value.
+Furthermore, the classification procedure calculates a map of the class and the total votes and returns the class with the highest vote.
 
@@
 \subsubsection{AdaBoost on ID3}
-The ID3 algorithm does not introduce a large amount of preference bias and often overfitting if allowed to train to completion.
-Therefore, to implement AdaBoost on ID3, the depth of the trees were limited to one level.
-This type of tree is known as a \ii{decision stump}.
+The ID3 algorithm does not introduce a large amount of preference bias and may overfit if allowed to train to completion. Therefore, to implement AdaBoost on ID3, the depth of the trees was limited.
 
 \subsection{Random Forest}
-Random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfitting to the training set.
+The random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfitting to the training set.
 This method contains many similarities to the adaboost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests.
@@
 
-\section{Technical Details}
+\section{Technical Details} \label{sec:details}
 Missing attribute values within both the breast cancer dataset and mushroom dataset treated as another category.
@@
 This framework uses JUnit for unit tests and slfj4 to control logging.
-Both work independently of the machine learning algorithms.
-The package hiarchy was modeled off ...
+Both work independently of the machine learning algorithms and may be completely removed without affecting the functionality of the code.
+
+\subsection{jml}
+This is the root package of the project and contains several useful objects which are used through the various sub-packages.
 
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{Algorithm}:
-  \item[] \bb{Dataset}:
-  \item[] \bb{Model}:
-  \item[] \bb{KFold}: Implements the KFold cross validation algorithm.
-  \item[] \bb{Report}: The object returned from a k-fold cross validation test....
-  \item[] \bb{Util}: Utility functions used through the machine learning project.
+  \item[] \bb{Algorithm} An interface that all algorithms implement. These objects fit a Model to a DataSet.
+  \item[] \bb{Dataset} An object which abstracts away from the data and provides several useful behaviors such as splitting into subsets using both continuous or discrete attributes.
+  \item[] \bb{Model} An abstract classes which every trained model implements. Objects which extend this class must implement the predict method.
+  \item[] \bb{KFold} Implements the KFold cross validation algorithm. The object is initialized with set number of folds and is then able to generate reports given an algorithm and dataset.
+  \item[] \bb{Report} An object which summarizes the results of a particular algorithm on a particular dataset.
+A report contains a list of accuracies and can calculate information such as the mean accuracy of standard deviations.
+  \item[] \bb{Util} This object contains several useful static methods. These include reading from CSV files, converting primitive arrays to Lists and calculating entropy amongst others.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{Children}:
-  \item[] \bb{ID3}:
-  \item[] \bb{ID3Model}:
-  \item[] \bb{Node}:
+  \item[] \bb{ID3} The implementation of the ID3 algorithm.
+Fits a DataSet to a tree of decision Nodes and creates a ID3Model.
+The algorithm is parameterized by the max level and minimum number of samples.
+  \item[] \bb{ID3Model} A trained ID3 model. It uses the trained decision tree to make classification given a sample of new data.
+  \item[] \bb{Node} A node within a decision tree. Contains the logic to choose the best continuous or discrete attribute to split on. Each node has an associated attribute
+  \item[] \bb{Children} A Pluggable Object which both ContinuousChildren and DiscreteChildren implement.
+This allows for the abstraction of most of the discrete and continuous variable logic associated with splitting and classifying.
+  \item[] \bb{ContinuousChildren} The children of a Node which split on a continuous attribute.
+  \item[] \bb{DiscreteChildren} The children of a Node which split on a discrete attribute.
 \end{enumerate}
@@
 \subsection{ensemble}
-This package contains all of the objects associated with enseble learners.
+This package contains all of the objects associated with ensemble learners.
 
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{AdaBoost}:
-  \item[] \bb{AdaBoostModel}:
-  \item[] \bb{Multi-AdaBoost}:
-  \item[] \bb{Multi-AdaBoostModel}:
-  \item[] \bb{RandomForest}:
-  \item[] \bb{RandomForstModel}:
+  \item[] \bb{AdaBoost} The implementation of the SAMME AdaBoost algorithm.
+This algorithm is able to handle both binary and multiclass classification problems and is parameterized by the number of weak learners, proportion of samples and base learning algorithm.
+  \item[] \bb{AdaBoostModel} A trained AdaBoost model. It classifies a new instance using a weighted vote mechanism and returns the most likely class.
+  \item[] \bb{RandomForest} The implementation of the Random Forest algorithm. This algorithm is parameterized by the number of strong learners, proportion of samples and base learning algorithm.
+  \item[] \bb{RandomForestModel} A trained Random Forest model. It classifies a new instances using a voting mechanism and returning the most common classification.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{AttributeException}:
-  \item[] \bb{DataException}:
-  \item[] \bb{FileException}:
-  \item[] \bb{PredictionException}:
+  \item[] \bb{AttributeException} This exception is thrown when an error arises due to the attribute types (continuous, discrete).
+  \item[] \bb{DataException} This exception is thrown when there is an error associated with the data.
+  \item[] \bb{FileException} This exception is thrown when there is an issue with the data file, particularly while reading CSV files.
+  \item[] \bb{PredictionException} This exception is thrown when an error occurs during classification.
 \end{enumerate}
@@
 \subsection{math}
-Data was particularly difficult to handle.
-Whereas Java is a statically typed language, difficulties arose in handling both floating point and integer values.
-To manage this, a math package was created which implements useful data structures such as vectors and matrices.
-These object were used to abstract away from the underlying data structures.
-Furthermore, the `Vector` object provided many useful methods for vector arithmetic such as element-wise multiplication, division and exponents.
-These methods also support broadcasting, where a vector can be multiplied by a single number.
-These objects are used throughout the library in place of primitive arrays and ArrayLists and have were essential to the code quality.
-Often, methods it was necessary to have two associated objects held in one data structure.
-For example, there exists a method within the DataSet object which splits itself into two parts based on a pivot point.
-This method would preferably return a pair of datasets; however, many common data structures such as arrays, lists and maps seemed did not seem to adequate.
-To accomplish this task, a simple Tuple data structure was created.
-Several other useful objects were implemented within the math package such as distance function objects, distribution objects and an object containing useful static methods.
-The purpose of these objects will be elaborated within Naïve Bayes package design section.
-The utility object implemented useful functions not available within the Java math package.
+This package contains objects associated with mathematics. For
 
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{MathException}:
-  \item[] \bb{Matrix}:
-  \item[] \bb{Tuple}:
-  \item[] \bb{Util}:
-  \item[] \bb{Vector}:
+  \item[] \bb{MathException} This exception occurs when an error occurs during a mathematical operation.
+  \item[] \bb{Matrix} An object which representation of a matrix. It contains useful operations for manipulating matrices such as retrieving, modifying and adding rows and columns.
+  \item[] \bb{Tuple} A tuple object which uses Generics to hold two objects. This object is useful for moving associated objects throughout the code.
+  \item[] \bb{Util} A utility class that contains several useful mathematical operations such as logarithmic and exponential functions.
+For example, an $exp$ function is implemented which is parameterized by a Vector and returns a Vector.
+  \item[] \bb{Vector} is an object representation of a vector.
+Similar to the Matrix class, it contains several useful operation for manipulating its values.
+Furthermore, several vector arithmetic operations are implemented such as multiplication, addition and the dot product.
+The Vector class abstracts away from the underlying data representation.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{DistanceFunction}:
-  \item[] \bb{Euclidian}:
-  \item[] \bb{Hamming}:
+  \item[] \bb{Distance} is an interface which all distance functions must implement.
+  \item[] \bb{Euclidian} An object which represents the Euclidian distance function $\sqrt{\sum_{i=1}^{n}(q_i-p_i)^2}$.
+This object can be used to calculate the Euclidian distance between two real valued Vectors while classifying an new instance in a KNN classifier.
+  \item[] \bb{Hamming} An object which represents the Hamming distance function $\sum_{i=1}^{n}f_i(q, p)$ where $f_i(q, p) = 0$ if $q_i = p_i$ and $0$ otherwise.
+This object can be used to calculate the Hamming distance between two discrete Vectors while classifying an new instance in a KNN classifier.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{Distribution}:
-  \item[] \bb{GaussianDistribution}:
+  \item[] \bb{Distribution} is an interface which each distribution object must implement.
+  \item[] \bb{Gaussian} An object which reprints a Gaussian distribution. It is used be the Naïve Bayes classifier for continuous attributes.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{Attribute}:
-  \item[] \bb{BayesException}:
-  \item[] \bb{ClassSummary}:
-  \item[] \bb{ContinuousAttribute}:
-  \item[] \bb{DiscreteAttribute}:
-  \item[] \bb{NaïveBayes}:
-  \item[] \bb{NaïveBayesModel}:
+  \item[] \bb{Attribute} is an interface which the Continuous and Discrete attribute types must implement.
+  \item[] \bb{BayesException} is an RuntimeException which is thrown when no Distribution is supplied and there are continuous attributes within the DataSet.
+  \item[] \bb{ClassSummary} is an object created during the NaiveBayes learning process.
+It contains the class probability $P(v_k)$ and all of the necessary information to calculate either $p(a_i|v_k)$ or $P(a_j|v_k)$ given a new value.
+  \item[] \bb{Continuous} represents a continuous attribute.
+It is parameterized by a mean, standard deviation and Distribution.
+Given a new value, the value of the probability density function of the given distribution is calculated.
+  \item[] \bb{Discrete} represents a discrete attribute.
+It is parametrized by a map of conditional probabilities and the sum of the class length and probability of an unseen value.
+The parameters of the discrete attribute were carefully chosen for performance reasons.
+  \item[] \bb{NaïveBayes} is the implementation of the Naïve Bayes algorithm. It is optionally parameterized by a Distribution. The algorithm create a ClassSummary for each distinct class.
+  \item[] \bb{NaïveBayesModel} is a trained Naïve Bayes model. It classifies new samples by calculating the probability of each class and returning the most likely classification.
 \end{enumerate}
+
+$$\hat{y}= \mathrm{argmax}_{k\in\{1,..K\}} P(v_k)\prod_{i=1}^mp\left(a_i|v_k\right)\prod_{j=m}^nP\left(a_j|v_k\right)$$
 
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{KNN}:
-  \item[] \bb{KNNModel}:
-  \item[] \bb{KNNException}:
+  \item[] \bb{KNN} is the implementation of the k-nearest neighbor algorithm.
+It is parameterized by the number of neighbors to check.
+The learning process simply consist of providing the DataSet and parameters to a KNNModel.
+  \item[] \bb{KNNModel} is a trained KNN classifier. It classifies new samples by finding the k-closest neighbors and returning the most common classification.
+  \item[] \bb{KNNException} is the exception thrown when $k$ is greater than the data sample count.
 \end{enumerate}
@@
     \hline
-    Algorithm               Breast Cancer   & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    ID3                     & 97.994\%      & 90.634\% & 81.909\% & 88.234\% & 99.998\% \\ \hline
-    Naïve Bayes             & 97.663\%      & 81.940\% & 79.455\% & 65.048\% & 95.952\% \\ \hline
-    AdaBoost on ID3         & 98.715\%      & 88.822\% & 83.389\% & 100.00\% & 99.446\% \\ \hline
-    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 77.725\% & 100.00\% & 99.744\% \\ \hline
-    Random Forest           & 97.592\%      & 91.175\% & 84.316\% & 100.00\% & 99.865\% \\ \hline
-    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 87.886\% & 100.00\% & 99.826\% \\ \hline
+    Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
+    ID3                     & 97.994\%      & 90.634\% & 87.930\% & 79.678\% & 99.998\% \\ \hline
+    Naïve Bayes             & 97.663\%      & 81.940\% & 64.570\% & 80.556\% & 95.952\% \\ \hline
+    AdaBoost on ID3         & 98.715\%      & 88.822\% & 100000\% & 84.460\% & 99.446\% \\ \hline
+    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 100000\% & 78.803\% & 99.744\% \\ \hline
+    Random Forest           & 97.592\%      & 91.175\% & 91.949\% & 84.021\% & 99.865\% \\ \hline
+    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 93.923\% & 87.779\% & 99.826\% \\ \hline
   \end{tabular}
   \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
+  \label{table:accuracies}
 \end{table}
@@
     Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    ID3                     & 1.465\%       & 4.061\%  & 8.981\%  & 3.492\% & 0.017\%  \\ \hline
-    Naïve Bayes             & 1.678\%       & 3.373\%  & 10.388\% & 1.328\% & 2.128\%  \\ \hline
-    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 6.678\%  & 100.00\% & 1.081\%  \\ \hline
-    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 9.275\%  & 100.00\% & 0.652\%  \\ \hline
-    Random Forest           & 1.597\%       & 5.171\%  & 9.711\%  & 100.00\% & 0.702\%  \\ \hline
-    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 7.001\%  & 100.00\% & 0.433\%  \\ \hline
+    ID3                     & 1.465\%       & 4.061\%  & 3.392\%  & 8.952\%  & 0.017\%  \\ \hline
+    Naïve Bayes             & 1.678\%       & 3.373\%  & 1.357\% & 11.199\%  & 2.128\%  \\ \hline
+    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 10000\%  & 8.246\% & 1.081\%  \\ \hline
+    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 10000\%  & 8.802\% & 0.652\%  \\ \hline
+    Random Forest           & 1.597\%       & 5.171\%  & 2.622\%  & 8.325\% & 0.702\%  \\ \hline
+    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 2.284\%  & 8.089\% & 0.433\%  \\ \hline
   \end{tabular}
@@
 
-graph of hyperparameter search?
+The ID3 algorithm generally outperformed the Naïve Bayes algorithm as seen in table \ref{table:accuracies}.
+This is especially true when considering the letter recognition dataset.
+One possibility for this discrepancy is the type of distribution used for continuous attributes.
+No other probability density functions were experimented with.
+Furthermore, the letter recognition dataset likely expresses high correlation amongst the attributes.
+However, the two algorithms perform identically for the E Coli.
+and breast cancer datasets.
+
+The AdaBoost algorithm when using either ID3 or Naïve Bayes as a base model either improves or maintains the same accuracy as their base models.
+For example, AdaBoost on ID3 only improves the classification accuracy for E.
+Coli and breast cancer datasets.
+Additionally, AdaBoost on Naïve Bayes only improved the classification accuracy on the breast cancer and car datasets.
+The random forest algorithm also either improved or maintained the same accuracy as their base models.
+I believe the classification accuracy for each ensemble algorithm and dataset pair could be improved given more time for hyperparameter tuning.
+The larger datasets proved difficult for experimentation as they required much larger training times.
+In section \ref{sec:details}, we see that both the mushroom and letter recognition datasets tend to have much lower learner counts than their counterparts.
+Optimization was considered during the algorithm implementations; however, training time was not drastically reduced.
 

### 2017-12-10 cs6735/assignment/report.tex
almost finished report

@@
     \item AdaBoost on Naïve Bayes
-    \item K-nearest neighbors
+    \item K-Nearest Neighbors
   \end{enumerate}
@@
 \subsection{ID3}
-The Iterative Dichotomiser 3 (ID3) algorithm is an algorithm used to efficiently create decision trees \cite{Quinlan:1986:IDT:637962.637969}.
-ID3 was developed for situations with large datasets and the need for the efficient creation of a decision tree.
-
-Initially, the ID3 algorithm described by Thomas Mitchell \cite{Mitchell:1997:ML:541177} was implemented.
-It begins at the root node with a set of categorical, labeled data $S$.
-The attribute $a$ which introduces the largest information gain is chosen and the node splits on that attribute.
+The Iterative Dichotomiser 3 (ID3) algorithm is used to efficiently create decision trees \cite{Quinlan:1986:IDT:637962.637969}.
+Initially, the algorithm as described by Thomas Mitchell \cite{Mitchell:1997:ML:541177} was implemented.
+ID3 begins by creating a root node with a set of categorical, labeled data $S$.
+The node iteratively finds the attribute $a$ which introduces the largest information gain and the node splits on that attribute.
 Subsets ${S_1,...,S_n}$ are used to create $n$ children nodes where $n$ is the amount of distinct values for attribute $a$.
 This continues recursively until one of several terminating conditions are met.
-For example, the process ends if there are no more possible subsets, the split is not statistically significant (does not introduce positive information gain) or the entropy is $0$.
-Furthermore, two early stopping conditions were implemented including a max tree level and a minimum number of samples.
+For example, the process ends if there are no more possible subsets, the split is not statistically significant or the entropy of a node is $0$.
+Furthermore, two early stopping conditions were implemented including a max tree level and a minimum number of samples per node.
 
 After this initial ID3 algorithm was implemented, further enhancements were made to allow for continuous data to be used.
-This enhancement was taken from the C4.5 as developed by Ross Quinlan \citep{c45algorithm}.
+The moderations made were based on the C4.5 algorithm developed by Ross Quinlan \citep{c45algorithm}.
 Given a continuous attribute $a$, we temporarily sort the data $S$.
 After the data is sorted, we iteratively determine the threshold to split the data that maximizes the information gain.
-To test potential thresholds, we find two sequential numbers which are not of the same class and split at the midway point of the two values.
-This enhancements saves an a large amount of time for each continuous attribute found within the datasets as discretization does not need to occur.
-Furthermore, this algorithm chooses the optimal threshhold to split the data which improves classification accuracy.
+To test potential thresholds, we find two sequential, distinct numbers and split at the midway point of the two values.
+This enhancements removes the need for discretization of the data.
+Furthermore, this enhancement chooses the optimal threshold to split the data which improves classification accuracy.
 
 \subsection{Naïve Bayes}
-The Naïve Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independence amongst each attribute:
+The Naïve Bayes algorithm is implemented as described by Mitchell in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independence amongst each attribute:
 
@@
 
-Naïve Bayes is a practical learning algorithm, receives relatively good results given its preference bias and is easy to implement.
-This algorithm naturally handles both categorical and continuous data (given a prior is assumed).
-For each continuous attribute, a Gaussian distribution was assumed.
+Naïve Bayes is a fast learning algorithm and receives relatively good results despite its preference for bias.
+The algorithm naturally inherently works with both categorical and continuous data.
+For this implementation, a Gaussian distribution was assumed for all continuous attributes.
 The final algorithm implemented was:
@@
 
-where $P$ is the probability, $p$ is the gaussian probability density function and $K$ is the number of distinct targets.
-In this equation, the first m attributes are continuous whereas the later are catigorical.
-During training, the data $S$ is split by lables into subsets ${S_1,...,S_n}$ where $n$ is the number of different classes.
+where $P$ is the probability, $p$ is the Gaussian probability density function and $K$ is the number of distinct classes.
+In this equation, the first $m$ attributes are continuous whereas the later are categorical.
+During training, the dataset $S$ is split by class into subsets ${S_1,...,S_n}$ where $n$ is the number of distinct classes.
 For each subset, we estimate the class probability $P(v_k)$.
-Subsequently, for each attribute value $a_i$ of each attribute $a$, we estimate $P(a_i|v_k)$ or $p$.
-We are not able to immediately calculate $p(a_i|v_k)$ as attribute $a$ is a continous attribute.
+Subsequently, for each attribute value $a_i$, we estimate $P(a_i|v_k)$.
+We are not able to immediately calculate $p(a_i|v_k)$ if attribute $a$ is continuous; however, we determine the mean and standard deviation.
 
 \subsection{AdaBoost} \label{adaboost}
-AdaBoost is a boosting algorithm that was first introduced in 1995 by Freunb Schapire.
+AdaBoost is a boosting algorithm that was first introduced in 1995 by Freund Schapire.
 This type of ensemble learning uses a set of weak learners to reduce bias and become a strong learner.
@@
 
-The primary part of the algorithm is to maintain a weight value $w$ for every sample within the data $S$.
-This value increases when the sample is misclassified and decreases when the sample is correctly classified.
-The target values are assumed be to in the set ${+1, -1}$.
-The AdaBoost algorithm is easily implemented on weak learners which are parameterized by sample weights.
-Neither Naïve Bayes or ID3 natively implement weighted training.
+The key of the AdaBoost algorithm is to maintain a weight value $w_i$ for every sample within the dataset $S$.
+This weight increases when its sample is misclassified and decreases when its sample is correctly classified.
+The AdaBoost algorithm is easily implemented on weak learners who are parameterized by sample weights; however, neither Naïve Bayes or ID3 natively implement weighted training.
 Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights.
-For example, if the weight vector for two samples is ${1, 2}$, the second sample is twice as likely to be picked each time.
+For example, if the weight values for two samples are ${1, 2}$, the second sample would be twice as likely to be picked each time.
 
 Initially, the weights are set to $\frac{1}{|S|}$.
-For a predefined number of iterations, a weak learner is trained on the a subset of the traning data.
+For a predefined number of iterations, a weak learner is trained on the a subset of the training data.
 Predictions are made for each training sample and the error is calculated.
@@
 
-To multiclass classification problems, the SAMME AdaBoost algorithm \cite{samme} was implemented.
-This algorithm sees the addition of $log(|v|-1)$, where $|v|$ is the number of classes, to the alpha value.
-Furthermore, the classification procedure calculates a map of the class and the total votes and returns the class with the highest vote.
+One limitation of the AdaBoost algorithm is its assumption of a binary classification.
+The class values are assumed be to either $+1$ or $-1$.
+One solution includes training $n$ AdaBoost models where $n$ is the number of distinct classes.
+For each different model, we reduce one class to $+1$ and the others to $-1$.
+To make classifications, we query each model and choose the class associated with the post positive prediction.
+This enhancement was initially implemented; however, it proved incredibly difficult to train these models with large datasets due to time and memory constraints.
+
+As an alternative, the SAMME AdaBoost algorithm \cite{samme} was implemented.
+This algorithm which naturally manages multiclass classification problems.
+It sees the addition of $log(|v|-1)$, where $|v|$ is the number of classes, to the $\alpha$ value and slightly.
+This is a very slight modification to the initial algorithm; however, it proves very useful for multiclass problems.
+Typically, the error must be less than $1/2$ in order for $\alpha$ to be positive.
+With the modification to the equation, $\alpha$ is positive when $1-error > 1/n$ \cite{samme}.
 
@@
 Naïve Bayes is an inherently weak learner due to its assumption of conditional independence amongst attributes.
-This fact introduces a large amount of preference bias which makes a Naïve Bayes and ideal candidate for the AdaBoost algorithm.
+This fact introduces a large amount of preference bias which makes Naïve Bayes an ideal candidate for the AdaBoost algorithm.
 
@@
 \subsection{Random Forest}
-The random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfitting to the training set.
-This method contains many similarities to the adaboost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests.
+The random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce the effects of overfitting to the training set.
+This method contains similarities to the AdaBoost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests.
 For a predefined number of iterations, a subset of the of the training data is selected with replacement.
-The new training set is then used to train a decision tree to completion and added to tree is added to a list.
-To make a classification, each tree in the forest votes and the most common target value becomes the predicted class.
-As an extension of the base random forest algorithm, weights may be given to each decision tree based on their classification error during training; however, this extension was not added for this implementation.
+The new training set subsequently used to train a decision tree and the trained model is added to the \ii{forest}.
+To make a classification, each tree in the forest votes and the most common class becomes the predicted class.
+As an extension of the random forest algorithm, weights may be given to each decision tree based on their classification accuracy; however, this extension was not added.
 
 \subsection{K-Nearest Neighbors}
-The K-Nearest Neighbor algorithm is an instance based learning algorithm which makes predictions by finding the $k$ nearest neighbors of a sample $x$ and using the most common class as the predicted class for that sample.
+The k-nearest neighbors algorithm is an instance based learning algorithm which makes predictions by finding the $k$ nearest neighbors of a sample $x$ and using the most common class as the predicted class for that sample.
 This algorithm can be used with both categorical and continuous data.
 For this implementation, Euclidian distance was used for continuous variables and Hamming distance was used for categorical data.
+A weighted classifier may be used; however, this extension was not added as the $k$ value was usually set to $1$.
 
 \section{Data}
-Each algorithm was implemented on five different datasets from the UCI Machine Learning Repository.
+Each algorithm was implemented on the following five datasets from the UCI Machine Learning Repository.
 
@@
 \section{Technical Details} \label{sec:details}
-Missing attribute values within both the breast cancer dataset and mushroom dataset treated as another category.
+Missing attribute values within the breast cancer and mushroom datasets were simply treated as distinct categories.
 Attempts were initially made to replace the missing values; however, no improvements with accuracy were observed.
@@
 Furthermore, any string values were converted to integers.
-For example, the ``v-high'', ``high'', ``med'' and ``low'' attribute values would have been converted to 0, 1, 2, 3 respectively.
+For example, the ``v-high'', ``high'', ``med'' and ``low'' attribute values of the car dataset would have been converted to 0, 1, 2, 3 respectively.
+
+The following subsections outline the hyperparameters used for each algorithm. Various testing logic was used to find the optimal hyperparameter set for each dataset algorithm pair.
 
 \subsection{ID3}
-\begin{table}
-  \caption{The }
 \begin{tabular}{ |c|c| } \hline
@@
 \end{tabular}
-\end{table}
 
@@
 \subsection{AdaBoost on ID3}
-\begin{tabular}{ |c|c|c| } \hline
+\begin{tabular}{ |c|c|c|c| } \hline
   \bb{Dataset}       & \bb{Max Level} & \bb{\# of Learners} & Proportion of Samples \\ \hline
@@
 \subsection{AdaBoost on Naïve Bayes}
-\begin{tabular}{ |c|c|c| } \hline
-  \bb{Dataset}       & \bb{Distribution} & \bb{\# of Learners} & Proportion of Samples & \\ \hline
+\begin{tabular}{ |c|c|c|c| } \hline
+  \bb{Dataset}       & \bb{Distribution} & \bb{\# of Learners} & Proportion of Samples \\ \hline
   Breast Cancer      & None              & 100                 & 0.70                  \\ \hline
@@
 \subsection{Random Forest}
-\begin{tabular}{ |c|c| } \hline
+\begin{tabular}{ |c|c|c| } \hline
   \bb{Dataset}       & \bb{\# of Learners} & Proportion of Samples \\ \hline
@@
 \subsection{K-Nearest Neighbors}
-\begin{tabular}{ |c|c| } \hline
+\begin{tabular}{ |c|c|c| } \hline
   \bb{Dataset}       & \bb{K} & Distance  \\ \hline
@@
 Both work independently of the machine learning algorithms and may be completely removed without affecting the functionality of the code.
+The project is divided up into various packages which will be described in the following subsections.
 
 \subsection{jml}
-This is the root package of the project and contains several useful objects which are used through the various sub-packages.
+This is the root package of the project and contains several of the main classes that are used throughout the various sub-packages.
 
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{Algorithm} An interface that all algorithms implement. These objects fit a Model to a DataSet.
-  \item[] \bb{Dataset} An object which abstracts away from the data and provides several useful behaviors such as splitting into subsets using both continuous or discrete attributes.
-  \item[] \bb{Model} An abstract classes which every trained model implements. Objects which extend this class must implement the predict method.
-  \item[] \bb{KFold} Implements the KFold cross validation algorithm. The object is initialized with set number of folds and is then able to generate reports given an algorithm and dataset.
-  \item[] \bb{Report} An object which summarizes the results of a particular algorithm on a particular dataset.
-A report contains a list of accuracies and can calculate information such as the mean accuracy of standard deviations.
-  \item[] \bb{Util} This object contains several useful static methods. These include reading from CSV files, converting primitive arrays to Lists and calculating entropy amongst others.
+  \item[] \bb{Algorithm} is the interface that all algorithms implement. These objects fit a Model to a DataSet.
+  \item[] \bb{Dataset} is an object which represents a dataset. It abstracts away from the data and provides several useful behaviors.
+  \item[] \bb{Model} is an abstract class that all models implement. Objects which extend this class must be able to make a prediction given a new data instance.
+  \item[] \bb{KFold} implements the k-fold cross validation algorithm. The object is parameterized by the number of folds and generates a Report given an Algorithm and Dataset.
+  \item[] \bb{Report} is an object which summarizes the results of a particular algorithm on a particular dataset.
+A report contains a list of accuracies and can calculate information such as the mean accuracy of standard deviation.
+  \item[] \bb{Util} is a utility object that contains several useful static methods.
+For example, Util contains methods to read from CSV files, convert primitive arrays to Lists and calculating information entropy.
 \end{enumerate}
@@
 \subsection{tree}
-This package contains all of the objects associated with decision trees.
+This package contains the objects associated with decision trees.
 
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{ID3} The implementation of the ID3 algorithm.
-Fits a DataSet to a tree of decision Nodes and creates a ID3Model.
-The algorithm is parameterized by the max level and minimum number of samples.
-  \item[] \bb{ID3Model} A trained ID3 model. It uses the trained decision tree to make classification given a sample of new data.
-  \item[] \bb{Node} A node within a decision tree. Contains the logic to choose the best continuous or discrete attribute to split on. Each node has an associated attribute
-  \item[] \bb{Children} A Pluggable Object which both ContinuousChildren and DiscreteChildren implement.
-This allows for the abstraction of most of the discrete and continuous variable logic associated with splitting and classifying.
-  \item[] \bb{ContinuousChildren} The children of a Node which split on a continuous attribute.
-  \item[] \bb{DiscreteChildren} The children of a Node which split on a discrete attribute.
+  \item[] \bb{ID3} is the implementation of the ID3 algorithm.
+It fits a DataSet to a tree of Nodes to create an ID3Model.
+The algorithm is parameterized by the max tree level and minimum number of samples per Node.
+  \item[] \bb{ID3Model} is a trained ID3 model. It uses the trained decision tree nodes to make a classification given a new sample.
+  \item[] \bb{Node} is a node within a decision tree. It contains the logic to choose the attribute which maximizes information gain.
+  \item[] \bb{Children} is an abstract class which both ContinuousChildren and DiscreteChildren implement.
+This allows for the abstraction of most of the logic associated with splitting and classifying using continuous and discrete attributes.
+  \item[] \bb{ContinuousChildren} The children of a Node that split on a continuous attribute.
+  \item[] \bb{DiscreteChildren} The children of a Node that split on a discrete attribute.
 \end{enumerate}
@@
 \subsection{ensemble}
-This package contains all of the objects associated with ensemble learners.
+This package contains the objects associated with ensemble learning.
 
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{AdaBoost} The implementation of the SAMME AdaBoost algorithm.
+  \item[] \bb{AdaBoost} is the implementation of the SAMME AdaBoost algorithm.
 This algorithm is able to handle both binary and multiclass classification problems and is parameterized by the number of weak learners, proportion of samples and base learning algorithm.
-  \item[] \bb{AdaBoostModel} A trained AdaBoost model. It classifies a new instance using a weighted vote mechanism and returns the most likely class.
-  \item[] \bb{RandomForest} The implementation of the Random Forest algorithm. This algorithm is parameterized by the number of strong learners, proportion of samples and base learning algorithm.
-  \item[] \bb{RandomForestModel} A trained Random Forest model. It classifies a new instances using a voting mechanism and returning the most common classification.
+  \item[] \bb{AdaBoostModel} is a trained AdaBoost model. It classifies a new instance using a weighted vote mechanism and returns the most likely class.
+  \item[] \bb{RandomForest} is the implementation of the random forest algorithm. This algorithm is parameterized by the number of strong learners, proportion of samples and base learning algorithm.
+  \item[] \bb{RandomForestModel} is a trained random forest model. It classifies a new instance using a voting mechanism and returns the most common classification.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{AttributeException} This exception is thrown when an error arises due to the attribute types (continuous, discrete).
-  \item[] \bb{DataException} This exception is thrown when there is an error associated with the data.
-  \item[] \bb{FileException} This exception is thrown when there is an issue with the data file, particularly while reading CSV files.
-  \item[] \bb{PredictionException} This exception is thrown when an error occurs during classification.
+  \item[] \bb{AttributeException} is the runtime exception thrown when an error arises due to the attribute types (continuous, discrete).
+  \item[] \bb{DataException} is the runtime exception thrown when there is an error associated with the data.
+  \item[] \bb{FileException} is the runtime exception thrown when there is an issue with the data file, particularly while reading CSV files.
+  \item[] \bb{PredictionException} is the runtime exception thrown when an error occurs during classification.
 \end{enumerate}
@@
 \subsection{math}
-This package contains objects associated with mathematics. For
+This package contains objects associated with mathematics.
 
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{MathException} This exception occurs when an error occurs during a mathematical operation.
-  \item[] \bb{Matrix} An object which representation of a matrix. It contains useful operations for manipulating matrices such as retrieving, modifying and adding rows and columns.
-  \item[] \bb{Tuple} A tuple object which uses Generics to hold two objects. This object is useful for moving associated objects throughout the code.
-  \item[] \bb{Util} A utility class that contains several useful mathematical operations such as logarithmic and exponential functions.
-For example, an $exp$ function is implemented which is parameterized by a Vector and returns a Vector.
+  \item[] \bb{MathException} is the runtime exception thrown when an error occurs during a mathematical operation.
+  \item[] \bb{Matrix} is an object which represents a matrix. It contains useful operations for manipulating matrices such as retrieving, modifying and adding rows and columns.
+  \item[] \bb{Tuple} is a tuple object which uses Generics to hold a pair of objects. This object is useful for moving associated objects throughout the code.
+  \item[] \bb{Util} is a utility class that contains several useful mathematical operations such as logarithmic and exponential functions.
   \item[] \bb{Vector} is an object representation of a vector.
@@
 The Vector class abstracts away from the underlying data representation.
+Although it uses a List of Doubles as the data structure, it may be treated as a vector of integers if desired.
 \end{enumerate}
@@
   \item[] \bb{Distance} is an interface which all distance functions must implement.
-  \item[] \bb{Euclidian} An object which represents the Euclidian distance function $\sqrt{\sum_{i=1}^{n}(q_i-p_i)^2}$.
-This object can be used to calculate the Euclidian distance between two real valued Vectors while classifying an new instance in a KNN classifier.
-  \item[] \bb{Hamming} An object which represents the Hamming distance function $\sum_{i=1}^{n}f_i(q, p)$ where $f_i(q, p) = 0$ if $q_i = p_i$ and $0$ otherwise.
-This object can be used to calculate the Hamming distance between two discrete Vectors while classifying an new instance in a KNN classifier.
+  \item[] \bb{Euclidian} is an object which represents the Euclidian distance function $\sqrt{\sum_{i=1}^{n}(q_i-p_i)^2}$.
+This object is used to calculate the Euclidian distance between two continuous Vectors while classifying an new instance in a KNNModel.
+  \item[] \bb{Hamming} is an object which represents the Hamming distance function $\sum_{i=1}^{n}f_i(q, p)$ where $f_i(q, p) = 0$ if $q_i = p_i$ and $0$ otherwise.
+This object is used to calculate the Hamming distance between two discrete Vectors while classifying an new instance in a KNNModel.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{Distribution} is an interface which each distribution object must implement.
-  \item[] \bb{Gaussian} An object which reprints a Gaussian distribution. It is used be the Naïve Bayes classifier for continuous attributes.
+  \item[] \bb{Distribution} is an interface which all distribution objects must implement.
+  \item[] \bb{Gaussian} An object which reprints a Gaussian distribution. It is used by the Naïve Bayes classifier for continuous attributes.
 \end{enumerate}
@@
   \item[] \bb{Attribute} is an interface which the Continuous and Discrete attribute types must implement.
-  \item[] \bb{BayesException} is an RuntimeException which is thrown when no Distribution is supplied and there are continuous attributes within the DataSet.
-  \item[] \bb{ClassSummary} is an object created during the NaiveBayes learning process.
-It contains the class probability $P(v_k)$ and all of the necessary information to calculate either $p(a_i|v_k)$ or $P(a_j|v_k)$ given a new value.
-  \item[] \bb{Continuous} represents a continuous attribute.
-It is parameterized by a mean, standard deviation and Distribution.
-Given a new value, the value of the probability density function of the given distribution is calculated.
+  \item[] \bb{BayesException} is a runtime exception which is thrown when no Distribution is supplied and there are continuous attributes within the DataSet.
+  \item[] \bb{ClassSummary} is the object created during the NaiveBayes learning process.
+It is parameterized by a class probability $P(v_k)$ and a List of Attributes so that it can calculate $P(v_k|x)$.
+  \item[] \bb{Continuous} represents a continuous attribute. It is parameterized by a mean, standard deviation and Distribution. Given a new value, the probability $p(a_i|v_k)$ is calculated.
   \item[] \bb{Discrete} represents a discrete attribute.
-It is parametrized by a map of conditional probabilities and the sum of the class length and probability of an unseen value.
+It is parametrized by a map of attribute values to conditional probabilities and the sum of the class length and probability of an unseen value.
 The parameters of the discrete attribute were carefully chosen for performance reasons.
+Given a new value, the conditional probability $P(a_j|v_k)$ is found from the map.
   \item[] \bb{NaïveBayes} is the implementation of the Naïve Bayes algorithm. It is optionally parameterized by a Distribution. The algorithm create a ClassSummary for each distinct class.
-  \item[] \bb{NaïveBayesModel} is a trained Naïve Bayes model. It classifies new samples by calculating the probability of each class and returning the most likely classification.
+  \item[] \bb{NaïveBayesModel} is a trained Naïve Bayes model.
+It classifies new samples by calculating the conditional probability of each class $P(v_k|x)$ and returning the most likely classification.
 \end{enumerate}
-
-$$\hat{y}= \mathrm{argmax}_{k\in\{1,..K\}} P(v_k)\prod_{i=1}^mp\left(a_i|v_k\right)\prod_{j=m}^nP\left(a_j|v_k\right)$$
 
@@
 \begin{enumerate}[leftmargin=*]
-  \item[] \bb{KNN} is the implementation of the k-nearest neighbor algorithm.
-It is parameterized by the number of neighbors to check.
-The learning process simply consist of providing the DataSet and parameters to a KNNModel.
-  \item[] \bb{KNNModel} is a trained KNN classifier. It classifies new samples by finding the k-closest neighbors and returning the most common classification.
-  \item[] \bb{KNNException} is the exception thrown when $k$ is greater than the data sample count.
+  \item[] \bb{KNN} is the implementation of the k-nearest neighbors algorithm. The learning process simply consist of providing the parameters to the KNNModel.
+  \item[] \bb{KNNModel} is a trained KNN classifier.
+It is parameterized by the number of neighbors to use for the classification and a DataSet.
+It classifies new samples by finding the $k$ closest neighbors and returning the most common classification.
+  \item[] \bb{KNNException} is the exception thrown when $k$ exceeds the DataSet sample count.
 \end{enumerate}
@@
     \hline
-    Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    ID3                     & 97.994\%      & 90.634\% & 87.930\% & 79.678\% & 99.998\% \\ \hline
-    Naïve Bayes             & 97.663\%      & 81.940\% & 64.570\% & 80.556\% & 95.952\% \\ \hline
-    AdaBoost on ID3         & 98.715\%      & 88.822\% & 100000\% & 84.460\% & 99.446\% \\ \hline
-    AdaBoost on Naïve Bayes & 98.626\%      & 91.367\% & 100000\% & 78.803\% & 99.744\% \\ \hline
-    Random Forest           & 97.592\%      & 91.175\% & 91.949\% & 84.021\% & 99.865\% \\ \hline
-    K-Nearest Neighbor      & 98.050\%      & 89.763\% & 93.923\% & 87.779\% & 99.826\% \\ \hline
+    \bb{Algorithm}               & \bb{Breast Cancer} & \bb{Car} & \bb{Letter} & \bb{E. Coli}  & \bb{Mushroom} \\ \hline
+    \bb{ID3}                     & 97.994\%           & 90.634\% & 87.930\%    & 79.678\%      & 99.998\%      \\ \hline
+    \bb{Naïve Bayes}             & 97.663\%           & 81.940\% & 64.570\%    & 80.556\%      & 95.952\%      \\ \hline
+    \bb{AdaBoost on ID3}         & 98.715\%           & 88.822\% & 96.125\%    & 84.460\%      & 99.446\%      \\ \hline
+    \bb{AdaBoost on Naïve Bayes} & 98.626\%           & 91.367\% & 56.960\%    & 78.803\%      & 99.744\%      \\ \hline
+    \bb{Random Forest}           & 97.592\%           & 91.175\% & 91.949\%    & 84.021\%      & 99.865\%      \\ \hline
+    \bb{K-Nearest Neighbors}     & 98.050\%           & 89.763\% & 93.923\%    & 87.779\%      & 99.826\%      \\ \hline
   \end{tabular}
-  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
+  \caption{Accuracy of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
   \label{table:accuracies}
@@
     \hline
-    Algorithm               & Breast Cancer & Car      & Letter   & E. Coli  & Mushroom \\ \hline
-    ID3                     & 1.465\%       & 4.061\%  & 3.392\%  & 8.952\%  & 0.017\%  \\ \hline
-    Naïve Bayes             & 1.678\%       & 3.373\%  & 1.357\% & 11.199\%  & 2.128\%  \\ \hline
-    AdaBoost on ID3         & 1.216\%       & 3.085\%  & 10000\%  & 8.246\% & 1.081\%  \\ \hline
-    AdaBoost on Naïve Bayes & 1.394\%       & 1.987\%  & 10000\%  & 8.802\% & 0.652\%  \\ \hline
-    Random Forest           & 1.597\%       & 5.171\%  & 2.622\%  & 8.325\% & 0.702\%  \\ \hline
-    K-Nearest Neighbor      & 1.118\%       & 3.967\%  & 2.284\%  & 8.089\% & 0.433\%  \\ \hline
+    \bb{Algorithm}               & \bb{Breast Cancer} & \bb{Car} & \bb{Letter} & \bb{E. Coli}  & \bb{Mushroom} \\ \hline
+    \bb{ID3}                     & 1.465\%            & 4.061\%  & 3.392\%     & 8.952\%       & 0.017\%       \\ \hline
+    \bb{Naïve Bayes}             & 1.678\%            & 3.373\%  & 1.357\%     & 11.199\%      & 2.128\%       \\ \hline
+    \bb{AdaBoost on ID3}         & 1.216\%            & 3.085\%  & 1.066\%     & 8.246\%       & 1.081\%       \\ \hline
+    \bb{AdaBoost on Naïve Bayes} & 1.394\%            & 1.987\%  & 1.780\%     & 8.802\%       & 0.652\%       \\ \hline
+    \bb{Random Forest}           & 1.597\%            & 5.171\%  & 2.622\%     & 8.325\%       & 0.702\%       \\ \hline
+    \bb{K-Nearest Neighbors}     & 1.118\%            & 3.967\%  & 2.284\%     & 8.089\%       & 0.433\%       \\ \hline
   \end{tabular}
-  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
+  \caption{Standard deviation of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
 \end{table}
 
-The ID3 algorithm generally outperformed the Naïve Bayes algorithm as seen in table \ref{table:accuracies}.
+The ID3 algorithm generally outperformed the Naïve Bayes algorithm as seen in Table \ref{table:accuracies}.
 This is especially true when considering the letter recognition dataset.
@@
 
-The AdaBoost algorithm when using either ID3 or Naïve Bayes as a base model either improves or maintains the same accuracy as their base models.
-For example, AdaBoost on ID3 only improves the classification accuracy for E.
-Coli and breast cancer datasets.
-Additionally, AdaBoost on Naïve Bayes only improved the classification accuracy on the breast cancer and car datasets.
-The random forest algorithm also either improved or maintained the same accuracy as their base models.
-I believe the classification accuracy for each ensemble algorithm and dataset pair could be improved given more time for hyperparameter tuning.
-The larger datasets proved difficult for experimentation as they required much larger training times.
-In section \ref{sec:details}, we see that both the mushroom and letter recognition datasets tend to have much lower learner counts than their counterparts.
+The AdaBoost algorithm when using either ID3 or Naïve Bayes as a base model either improved or maintained the same accuracy as their base models.
+For example, AdaBoost on ID3 improved the classification accuracy for E.
+Coli, letter recognition and breast cancer datasets; however, it maintains the same accuracy as the ID3 algorithm for the other datasets.
+Additionally, AdaBoost on Naïve Bayes improved the classification accuracy on the breast cancer and car datasets and maintained similar accuracies to Naïve Bayes on the other datasets.
+One exception to this is the letter dataset where AdaBoost on Naïve Bayes which scored 10\% lower.
+The random forest algorithm maintained a similar performance to the AdaBoost on ID3 algorithm.
+It outperformed AdaBoost on the car dataset; however, the standard deviation for each algorithm is too high to make any conclusions.
+
+I believe the classification accuracy for each ensemble algorithm, dataset pair could be improved given more time for hyperparameter tuning.
+The larger datasets proved extremely difficult for experimentation as they required much longer training times.
+When experimenting with various hyperparameters for the letter dataset, it often took more than 10 minutes to complete one 5-fold cross validation iteration.
 Optimization was considered during the algorithm implementations; however, training time was not drastically reduced.
+
+The most surprising results received were from the k-nearest neighbors algorithm.
+It almost always outperformed the other algorithms and even received the highest accuracy for the car dataset.
+An interesting feature of the hyperparameters for this classifier is that all $k$ values were set to $1$.
+This was an unexpected result of the hyperparameter search.
+The most prominent flaw with the k-nearest neighbors algorithm was the extremely long classification times, especially for the larger datasets.
 

### 2017-12-11 cs2383/practice.go
some data/alg practice

@@ -1,0 +1,169 @@
+package main
+
+import (
+	"errors"
+	"fmt"
+)
+
+func main() {
+	fmt.Println("Practicing Data Structures & Algorithms")
+}
+
+// Node a node in a binary tree
+type Node struct {
+	data  int
+	left  *Node
+	right *Node
+}
+
+// Stack a stack
+type Stack struct {
+	head *Item
+}
+
+// List a List
+type List struct {
+	head *Item
+}
+
+// Item an item in a stack, queue or linked-list
+type Item struct {
+	data int
+	next *Item
+}
+
+// Push pushes the value onto the list
+func (s *Stack) Push(value int) {
+	item := Item{value, s.head}
+	s.head = &item
+}
+
+// Pop pops the top item off the list
+func (s *Stack) Pop() error {
+	if s.head == nil {
+		return errors.New("the stack is empty")
+	}
+
+	s.head = s.head.next
+	return nil
+}
+
+// Top returns the item at the top of the list
+func (s *Stack) Top() (int, error) {
+	if s.head == nil {
+		return 0, errors.New("the stack is empty")
+	}
+
+	return s.head.data, nil
+}
+
+// Add adds the value to the end of the list
+func (l *List) Add(value int) {
+	item := l.head
+	if item == nil {
+		l.head = &Item{value, nil}
+		return
+	}
+
+	for item.next != nil {
+		item = item.next
+	}
+	item.next = &Item{value, nil}
+}
+
+// Del deletes all instances of value in the list
+func (l *List) Del(value int) {
+	item := l.head
+	if item == nil {
+		return
+	}
+
+	if item.next == nil {
+		if item.data == value {
+			l.head = nil
+		}
+
+		return
+	}
+
+	for item.next != nil {
+		if item.next.data == value {
+			item.next = item.next.next
+		} else {
+			item = item.next
+		}
+	}
+}
+
+// Get returns the item at the given index, -1 if > length of the list
+func (l *List) Get(index int) int {
+	i := 0
+	item := l.head
+	for item != nil {
+		if i == index {
+			return item.data
+		}
+
+		item = item.next
+		i++
+	}
+
+	return -1
+}
+
+// Length returns the length of the list
+func (l *List) Length() int {
+	length := 0
+	item := l.head
+	for item != nil {
+		length++
+		item = item.next
+	}
+
+	return length
+}
+
+// Front returns the front value in the list
+func (l *List) Front() int {
[…]

### 2017-12-11 cs2383/practice_test.go

@@ -1,0 +1,60 @@
+package main
+
+import (
+	"testing"
+
+	"github.com/stretchr/testify/assert"
+)
+
+var a []int
+
+func initArray() {
+	a = []int{1, 2, 3, 4, 5}
+}
+
+func TestStack(t *testing.T) {
+	s := Stack{}
+	s.Push(1)
+	s.Push(2)
+	err := s.Pop()
+	assert.Nil(t, err)
+
+	value, err := s.Top()
+	assert.Equal(t, 1, value)
+	assert.Nil(t, err)
+
+	err = s.Pop()
+	assert.Nil(t, err)
+	err = s.Pop()
+	assert.NotNil(t, err)
+}
+
+func TestList(t *testing.T) {
+	l := List{}
+	l.Add(1)
+	l.Add(2)
+	l.Add(2)
+	l.Add(3)
+	assert.Equal(t, 4, l.Length())
+
+	l.Del(2)
+	assert.Equal(t, 2, l.Length())
+	assert.Equal(t, 1, l.Front())
+	assert.Equal(t, 3, l.End())
+	assert.Equal(t, 1, l.Get(0))
+	assert.Equal(t, 3, l.Get(1))
+}
+
+func TestBinarySearchFound(t *testing.T) {
+	initArray()
+	k := 4
+	index := BinarySearch(a, k)
+	assert.Equal(t, 3, index)
+}
+
+func TestBinarySearchNotFound(t *testing.T) {
+	initArray()
+	k := 10
+	index := BinarySearch(a, k)
+	assert.Equal(t, -1, index, "BinarySearch should return -1 for not found")
+}

### 2017-12-11 cs6735/assignment/report.tex
updating accuracies
preparing submission

@@
 
-\title{Generative Adversarial Networks}
+\title{CS6735 Programming Assignment}
 \author{Jacob Smith}
@@
 Initially, the weights are set to $\frac{1}{|S|}$.
-For a predefined number of iterations, a weak learner is trained on the a subset of the training data.
+For a predefined number of iterations, a new weak learner is trained on the a subset of the training data.
 Predictions are made for each training sample and the error is calculated.
@@
   \bb{Dataset}            & \bb{Minimum \# of Samples} \\ \hline
-  Breast Cancer      & 1                          \\ \hline
-  Car                & 1                          \\ \hline
-  E. Coli            & 2                          \\ \hline
-  Letter Recognition & 1                          \\ \hline
-  Mushroom           & 1                          \\ \hline
+  \bb{Breast Cancer}      & 1                          \\ \hline
+  \bb{Car}                & 1                          \\ \hline
+  \bb{E. Coli}            & 2                          \\ \hline
+  \bb{Letter Recognition} & 1                          \\ \hline
+  \bb{Mushroom}           & 1                          \\ \hline
 \end{tabular}
@@
   \bb{Dataset}            & \bb{Distribution} \\ \hline
-  Breast Cancer      & None              \\ \hline
-  Car                & None              \\ \hline
-  E. Coli            & Gaussian          \\ \hline
-  Letter Recognition & Gaussian          \\ \hline
-  Mushroom           & None              \\ \hline
+  \bb{Breast Cancer}      & None              \\ \hline
+  \bb{Car}                & None              \\ \hline
+  \bb{E. Coli}            & Gaussian          \\ \hline
+  \bb{Letter Recognition} & Gaussian          \\ \hline
+  \bb{Mushroom}           & None              \\ \hline
 \end{tabular}
@@
 \begin{tabular}{ |c|c|c|c| } \hline
-  \bb{Dataset}       & \bb{Max Level} & \bb{\# of Learners} & Proportion of Samples \\ \hline
-  Breast Cancer      & 1              & 100                 & 0.50                  \\ \hline
-  Car                & 1              & 100                 & 0.70                  \\ \hline
-  E. Coli            & 1              & 100                 & 0.50                  \\ \hline
-  Letter Recognition & 1              & IDK                 & IDK                   \\ \hline
-  Mushroom           & 1              & 10                  & 0.30                  \\ \hline
+  \bb{Dataset}            & \bb{Max Level} & \bb{\# of Learners} & \bb{Proportion of Samples} \\ \hline
+  \bb{Breast Cancer}      & 1              & 100                 & 0.50                       \\ \hline
+  \bb{Car}                & 4              & 200                 & 0.30                       \\ \hline
+  \bb{E. Coli}            & 3              & 100                 & 0.20                       \\ \hline
+  \bb{Letter Recognition} & 8              & 300                 & 0.25                       \\ \hline
+  \bb{Mushroom}           & 3              & 10                  & 0.30                       \\ \hline
 \end{tabular}
@@
 \begin{tabular}{ |c|c|c|c| } \hline
-  \bb{Dataset}       & \bb{Distribution} & \bb{\# of Learners} & Proportion of Samples \\ \hline
-  Breast Cancer      & None              & 100                 & 0.70                  \\ \hline
-  Car                & None              & 100                 & 0.40                  \\ \hline
-  E. Coli            & Gaussian          & 150                 & 0.30                  \\ \hline
-  Letter Recognition & Gaussian          & IDK                 & IDK                   \\ \hline
-  Mushroom           & None              & 10                  & 0.30                  \\ \hline
+  \bb{Dataset}            & \bb{Distribution} & \bb{\# of Learners} & \bb{Proportion of Samples} \\ \hline
+  \bb{Breast Cancer}      & None              & 100                 & 0.70                       \\ \hline
+  \bb{Car}                & None              & 100                 & 0.40                       \\ \hline
+  \bb{E. Coli}            & Gaussian          & 250                 & 0.10                       \\ \hline
+  \bb{Letter Recognition} & Gaussian          & 10                  & 0.30                       \\ \hline
+  \bb{Mushroom}           & None              & 10                  & 0.50                       \\ \hline
 \end{tabular}
@@
 \begin{tabular}{ |c|c|c| } \hline
-  \bb{Dataset}       & \bb{\# of Learners} & Proportion of Samples \\ \hline
-  Breast Cancer      & 120                 & 0.70                  \\ \hline
-  Car                & 200                 & 0.60                  \\ \hline
-  E. Coli            & 120                 & 0.70                  \\ \hline
-  Letter Recognition & 50                  & 0.30                  \\ \hline
-  Mushroom           & 10                  & 0.30                  \\ \hline
+  \bb{Dataset}            & \bb{\# of Learners} & \bb{Proportion of Samples} \\ \hline
+  \bb{Breast Cancer}      & 120                 & 0.70                       \\ \hline
+  \bb{Car}                & 200                 & 0.60                       \\ \hline
+  \bb{E. Coli}            & 250                 & 0.60                       \\ \hline
+  \bb{Letter Recognition} & 100                 & 0.60                       \\ \hline
+  \bb{Mushroom}           & 10                  & 0.50                       \\ \hline
 \end{tabular}
@@
   \bb{Dataset}            & \bb{K} & Distance  \\ \hline
-  Breast Cancer      & 1      & Hamming   \\ \hline
-  Car                & 1      & Hamming   \\ \hline
-  E. Coli            & 1      & Euclidian \\ \hline
-  Letter Recognition & 1      & Euclidian \\ \hline
-  Mushroom           & 1      & Hamming   \\ \hline
+  \bb{Breast Cancer}      & 1      & Hamming   \\ \hline
+  \bb{Car}                & 1      & Hamming   \\ \hline
+  \bb{E. Coli}            & 1      & Euclidian \\ \hline
+  \bb{Letter Recognition} & 1      & Euclidian \\ \hline
+  \bb{Mushroom}           & 1      & Hamming   \\ \hline
 \end{tabular}
@@
 \section{Results}
-\begin{table}
+\begin{table} [!htbp]
   \begin{tabular}{ |c|c|c|c|c|c| }
@@
     \bb{Naïve Bayes}             & 97.663\%           & 81.940\% & 64.570\%    & 80.556\%      & 95.952\%      \\ \hline
-    \bb{AdaBoost on ID3}         & 98.715\%           & 88.822\% & 96.125\%    & 84.460\%      & 99.446\%      \\ \hline
-    \bb{AdaBoost on Naïve Bayes} & 98.626\%           & 91.367\% & 56.960\%    & 78.803\%      & 99.744\%      \\ \hline
-    \bb{Random Forest}           & 97.592\%           & 91.175\% & 91.949\%    & 84.021\%      & 99.865\%      \\ \hline
+    \bb{AdaBoost on ID3}         & 98.715\%           & 93.295\% & 97.050\%    & 86.918\%      & 99.828\%      \\ \hline
+    \bb{AdaBoost on Naïve Bayes} & 98.626\%           & 91.367\% & 59.540\%    & 78.803\%      & 99.744\%      \\ \hline
+    \bb{Random Forest}           & 98.585\%           & 91.175\% & 93.120\%    & 84.021\%      & 99.865\%      \\ \hline
     \bb{K-Nearest Neighbors}     & 98.050\%           & 89.763\% & 93.923\%    & 87.779\%      & 99.826\%      \\ \hline
@@
 
-\begin{table}
+\begin{table} [!htbp]
   \begin{tabular}{ |c|c|c|c|c|c| }
@@
     \bb{Naïve Bayes}             & 1.678\%            & 3.373\%  & 1.357\%     & 11.199\%      & 2.128\%       \\ \hline
-    \bb{AdaBoost on ID3}         & 1.216\%            & 3.085\%  & 1.066\%     & 8.246\%       & 1.081\%       \\ \hline
-    \bb{AdaBoost on Naïve Bayes} & 1.394\%            & 1.987\%  & 1.780\%     & 8.802\%       & 0.652\%       \\ \hline
+    \bb{AdaBoost on ID3}         & 1.216\%            & 3.143\%  & 0.989\%     & 6.908\%       & 0.293\%       \\ \hline
+    \bb{AdaBoost on Naïve Bayes} & 1.394\%            & 1.987\%  & 0.716\%     & 8.802\%       & 0.652\%       \\ \hline
     \bb{Random Forest}           & 1.597\%            & 5.171\%  & 2.622\%     & 8.325\%       & 0.702\%       \\ \hline

### 2017-12-11 cs6735/assignment/code/Assignment.java

@@ -1,0 +1,148 @@
+import ca.jacob.jml.Algorithm;
+import ca.jacob.jml.Dataset;
+import ca.jacob.jml.KFold;
+import ca.jacob.jml.bayes.NaiveBayes;
+import ca.jacob.jml.ensemble.AdaBoost;
+import ca.jacob.jml.math.Tuple;
+import ca.jacob.jml.math.distance.Euclidean;
+import ca.jacob.jml.math.distance.Hamming;
+import ca.jacob.jml.math.distribution.Gaussian;
+import ca.jacob.jml.tree.ID3;
+import ca.jacob.jml.ensemble.RandomForest;
+import ca.jacob.jml.neighbors.KNN;
+import ca.jacob.jml.Report;
+
+import java.util.ArrayList;
+import java.util.List;
+import java.util.concurrent.ExecutionException;
+import java.util.concurrent.ExecutorService;
+import java.util.concurrent.Executors;
+import java.util.concurrent.Future;
+
+import static ca.jacob.cs6735.DataUtil.*;
+
+public class Assignment {
+    private static int NUMBER_OF_K_FOLD_ITERATIONS = 10;
+    private static final KFold K_FOLD = new KFold(5, false);
+    private static boolean MULTITHREADED = false;
+
+    public static void main(String[] args) throws Throwable {
+        // Parsing the optional arguments
+        for(String arg : args) {
+            if(arg.equals("verbose")) {
+                K_FOLD.setVerbose(true);
+                continue;
+            }
+
+            if(arg.equals("multithreaded")) {
+                MULTITHREADED = true;
+                continue;
+            }
+
+            try {
+                NUMBER_OF_K_FOLD_ITERATIONS = Integer.parseInt(arg);
+            } catch (Exception e) {
+                // Do nothing
+            }
+        }
+
+        // init
+        List<Tuple<Dataset, List<Algorithm>>> datasetsAndAlgorithms  = new ArrayList<>();
+        List<Algorithm> algorithms;
+
+        // Breast Cancer Data
+        algorithms = new ArrayList<>();
+        algorithms.add(new ID3(ID3.MAX_LEVEL_NONE, 1));
+        algorithms.add(new NaiveBayes());
+        algorithms.add(new AdaBoost(new ID3(1), 100, 0.5));
+        algorithms.add(new AdaBoost(new NaiveBayes(), 100, 0.7));
+        algorithms.add(new RandomForest(new ID3(), 120, 0.7));
+        algorithms.add(new KNN(1, new Hamming()));
[…]

### 2017-12-11 cs6735/assignment/code/run.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+# Compiling the Java file with the proper classpath
+javac -classpath ".:jml.jar" Assignment.java
+
+# Running the compiled file
+java -classpath ".:jml.jar" Assignment
+
+# Run with optional parameters (verbose, multithreaded or # of iterations)
+# java -classpath ".;jml.jar" Assignment verbose multithreaded 10

### 2017-12-11 cs6735/assignment/report.tex
finished report!!!!

@@
-\documentclass[11pt]{article}
+\documentclass[11pt,titlepage]{article}
 \usepackage[utf8]{inputenc}
@@
 \maketitle
+% No chapter numbers
 
 \section{Introduction}
-This report details the experimental study conducted for the CS6735 programming project.
-Six machine learning algorithms were implemented, including both regular and ensemble learning algorithms.
-Each was evaluated on five datasets from the UCI Machine Learning data repository using 10 times 5-fold cross validation.
-The technical details of the implementation will be described in this report and the results will be presented and analyzed.
+This report details the experimental study conducted for the CS6735 programming assignment.
+Six machine learning algorithms were implemented.
+Each was evaluated on five datasets from the UCI Machine Learning Repository using 10 times 5-fold cross validation.
+The technical details of the implementation are described in this report and the results are be presented and analyzed.
 
@@
   \begin{enumerate}
-    \item Brest Cancer Data
+    \item Breast Cancer Data
     \item Car Data
@@
   \end{enumerate}
-  \item Create a report of the experimental study including:
+  \item Create a report of the experimental study, including:
   \begin{enumerate}
-    \item Description of the learning algorithms you implement.
-    \item Description of the datasets you use (number of examples, number of attribute, number of classes, type of attributes, etc.).
-    \item Technical details of your implementation: pre-processing of data sets (discretization, etc.), parameter setting, etc.
-    \item Design of your programming implementation (data structures, overall program structure).
-    \item Report and analysis of your experimental results using 10 times 5-fold cross-validation (include mean, standard deviation of accuracies).
-    \item Comparison and discussion of the algorithms with respect to the experimental results.
+    \item A description of the learning algorithms
+    \item A description of the datasets
+    \item The technical details of the implementation
+    \item The design of the program
+    \item A report and analysis of the experimental results
   \end{enumerate}
@@
 
-\section{Algorithms}
+\section{Algorithms} \label{algorithms}
 For this study, we used six different algorithms; however, only the five unique algorithms were implemented.
-Due to the design of the program, both the ID3 decision tree and Naïve Bayes algorithms could be given to the AdaBoost ensemble algorithm as a weak learner.
+The AdaBoost on ID3 and AdaBoost on Naïve Bayes algorithms did not need to be implemented independently.
 
@@
 The node iteratively finds the attribute $a$ which introduces the largest information gain and the node splits on that attribute.
-Subsets ${S_1,...,S_n}$ are used to create $n$ children nodes where $n$ is the amount of distinct values for attribute $a$.
+Subsets ${S_1,...,S_n}$ are used to create $n$ children nodes where $n$ is the amount of distinct values of attribute $a$.
 This continues recursively until one of several terminating conditions are met.
@@
 
-After this initial ID3 algorithm was implemented, further enhancements were made to allow for continuous data to be used.
-The moderations made were based on the C4.5 algorithm developed by Ross Quinlan \citep{c45algorithm}.
+After the ID3 algorithm was implemented, further enhancements were made to allow for continuous data to be used.
+These modifications were based off the C4.5 algorithm which was also developed by Ross Quinlan \citep{c45algorithm}.
 Given a continuous attribute $a$, we temporarily sort the data $S$.
-After the data is sorted, we iteratively determine the threshold to split the data that maximizes the information gain.
-To test potential thresholds, we find two sequential, distinct numbers and split at the midway point of the two values.
-This enhancements removes the need for discretization of the data.
+After this occurs, we iteratively determine the threshold to split the data that maximizes the information gain.
+To test potential thresholds, we find two sequential, distinct values of some attribute $a$ and split at the midway point of the two values.
+This enhancements removes the need for discretization of data.
 Furthermore, this enhancement chooses the optimal threshold to split the data which improves classification accuracy.
@@
 \subsection{Naïve Bayes}
-The Naïve Bayes algorithm is implemented as described by Mitchell in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independence amongst each attribute:
+The Naïve Bayes algorithm was also implemented as described by Thomas Mitchell \cite{Mitchell:1997:ML:541177}.
+This algorithm is a probabilistic classifier named due to its assumption of conditional independence amongst each attribute:
 
@@
 
-and its application of Bayes thereon:
+and its application of Bayes theorem:
 
@@
 
-Naïve Bayes is a fast learning algorithm and receives relatively good results despite its preference for bias.
-The algorithm naturally inherently works with both categorical and continuous data.
-For this implementation, a Gaussian distribution was assumed for all continuous attributes.
+Naïve Bayes is a fast learning algorithm that receives relatively good results despite its large bias.
+The algorithm inherently works with both categorical and continuous data.
+For this assignment, a Gaussian distribution was assumed for all continuous attributes.
 The final algorithm implemented was:
@@
 For each subset, we estimate the class probability $P(v_k)$.
-Subsequently, for each attribute value $a_i$, we estimate $P(a_i|v_k)$.
-We are not able to immediately calculate $p(a_i|v_k)$ if attribute $a$ is continuous; however, we determine the mean and standard deviation.
+Subsequently, for each categorical attribute value $a_i$, we estimate $P(a_i|v_k)$.
+We are not able to immediately calculate $p(a_i|v_k)$ for continuous attributes; however, we are able to determine the mean and standard deviation.
 
@@
 
-The key of the AdaBoost algorithm is to maintain a weight value $w_i$ for every sample within the dataset $S$.
+The key insight of the AdaBoost algorithm is to maintain a weight value $w_i$ for every sample within the dataset $S$.
 This weight increases when its sample is misclassified and decreases when its sample is correctly classified.
 The AdaBoost algorithm is easily implemented on weak learners who are parameterized by sample weights; however, neither Naïve Bayes or ID3 natively implement weighted training.
-Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights.
-For example, if the weight values for two samples are ${1, 2}$, the second sample would be twice as likely to be picked each time.
+Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on their associated weights.
+For example, if the weight values for two samples are $<1, 2>$, the second sample would be twice as likely to be chosen each time.
 
-Initially, the weights are set to $\frac{1}{|S|}$.
-For a predefined number of iterations, a new weak learner is trained on the a subset of the training data.
+Initially, the weights are set to $\frac{1}{n}$ where $n$ is the amount of samples in the dataset $S$.
+For a predefined number of iterations, a new weak learner is trained on the a weighted subset of the training data.
 Predictions are made for each training sample and the error is calculated.
-Using the accuracy, a value $\alpha$ is calculated which represents the accuracy of the weak learner.
-This $\alpha$ value is used to update the weights and the weak learner, $\alpha$ pair is added to the list of previous weak learners.
-To make classification, there is a weighted vote between using the weak learners and their associated $\alpha$ values and the sign is used to make the final classification.
+A new value $\alpha$ is calculated that represents the weight that will associated with the weak classifier.
+$\alpha$ is also used to update the weights of each sample.
+To make classification, there is a weighted vote between the weak learners.
+The sign of the summed votes is used to make the final classification as either $+1$ or $-1$.
 
 One limitation of the AdaBoost algorithm is its assumption of a binary classification.
-The class values are assumed be to either $+1$ or $-1$.
 One solution includes training $n$ AdaBoost models where $n$ is the number of distinct classes.
 For each different model, we reduce one class to $+1$ and the others to $-1$.
-To make classifications, we query each model and choose the class associated with the post positive prediction.
+To make classifications, we query each model and choose the class associated with the most positive prediction.
 This enhancement was initially implemented; however, it proved incredibly difficult to train these models with large datasets due to time and memory constraints.
@@
 This algorithm which naturally manages multiclass classification problems.
-It sees the addition of $log(|v|-1)$, where $|v|$ is the number of classes, to the $\alpha$ value and slightly.
-This is a very slight modification to the initial algorithm; however, it proves very useful for multiclass problems.
+The only difference to the learning process is the addition of $log(|v|-1)$, where $|v|$ is the number of classes, to the $\alpha$ value.
 Typically, the error must be less than $1/2$ in order for $\alpha$ to be positive.
-With the modification to the equation, $\alpha$ is positive when $1-error > 1/n$ \cite{samme}.
+With the SAMME modification, $\alpha$ is positive when $1-error > 1/n$ \cite{samme}.
 
@@
 Naïve Bayes is an inherently weak learner due to its assumption of conditional independence amongst attributes.
-This fact introduces a large amount of preference bias which makes Naïve Bayes an ideal candidate for the AdaBoost algorithm.
+This fact introduces a large amount of bias which makes Naïve Bayes an ideal candidate for the AdaBoost algorithm.
 
 \subsubsection{AdaBoost on ID3}
-The ID3 algorithm does not introduce a large amount of preference bias and may overfit if allowed to train to completion. Therefore, to implement AdaBoost on ID3, the depth of the trees was limited.
+The ID3 algorithm does not introduce a large amount of bias and may overfit if allowed to train to completion. Therefore, to implement AdaBoost on ID3, the depth of the trees was limited.
 
@@
 The random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce the effects of overfitting to the training set.
-This method contains similarities to the AdaBoost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests.
+This method contains similarities to the AdaBoost algorithm as described in section \ref{adaboost}; however, no weights are used for random forest.
 For a predefined number of iterations, a subset of the of the training data is selected with replacement.
-The new training set subsequently used to train a decision tree and the trained model is added to the \ii{forest}.
+The new training set is subsequently used to train a decision tree which is added to the \ii{forest}.
 To make a classification, each tree in the forest votes and the most common class becomes the predicted class.
-As an extension of the random forest algorithm, weights may be given to each decision tree based on their classification accuracy; however, this extension was not added.
+As an extension of the random forest algorithm, weights may be given to each decision tree based on their classification accuracy; however, this extension was not implemented.
 
@@
 For this implementation, Euclidian distance was used for continuous variables and Hamming distance was used for categorical data.
-A weighted classifier may be used; however, this extension was not added as the $k$ value was usually set to $1$.
+A weighted classifier may be used; however, this extension was not added as the $k$ values were usually set to $1$.
 
 \section{Data}
-Each algorithm was implemented on the following five datasets from the UCI Machine Learning Repository.
+Each algorithm described in section \ref{algorithms} was implemented on the following five datasets from the UCI Machine Learning Repository.
 
@@
 Missing attribute values within the breast cancer and mushroom datasets were simply treated as distinct categories.
-Attempts were initially made to replace the missing values; however, no improvements with accuracy were observed.
-Furthermore, no discretization occurred as all base algorithms are able to handle continuous data.
+Attempts were initially made to replace the missing values; however, no accuracy improvements were observed.
+Furthermore, no discretization occurred as all base algorithms were able to handle continuous data.
 For each dataset, any sort of identification number or code attributes were removed.
@@
 
-The following subsections outline the hyperparameters used for each algorithm. Various testing logic was used to find the optimal hyperparameter set for each dataset algorithm pair.
+The following subsections outline the hyperparameters used for each algorithm. Various testing logic was used to find the optimal hyperparameters each dataset and algorithm.
 
@@
 \begin{tabular}{ |c|c|c| } \hline
-  \bb{Dataset}            & \bb{K} & Distance  \\ \hline
+  \bb{Dataset}            & \bb{K} & \bb{Distance} \\ \hline
   \bb{Breast Cancer}      & 1      & Hamming       \\ \hline
@@
 A Java machine learning framework was first created to ease the implementation of the six learning algorithms.
-This framework uses JUnit for unit tests and slfj4 to control logging.
-Both work independently of the machine learning algorithms and may be completely removed without affecting the functionality of the code.
+The framework uses Maven to build the project, JUnit for unit tests and slfj4 to control logging.
+All work independently of the machine learning algorithms and may be completely removed without affecting the functionality of the code.
 The project is divided up into various packages which will be described in the following subsections.
@@
   \item[] \bb{ID3} is the implementation of the ID3 algorithm.
-It fits a DataSet to a tree of Nodes to create an ID3Model.
+It fits a DataSet to a tree of Nodes and creates an ID3Model.
 The algorithm is parameterized by the max tree level and minimum number of samples per Node.
@@
 This allows for the abstraction of most of the logic associated with splitting and classifying using continuous and discrete attributes.
-  \item[] \bb{ContinuousChildren} The children of a Node that split on a continuous attribute.
-  \item[] \bb{DiscreteChildren} The children of a Node that split on a discrete attribute.
+  \item[] \bb{ContinuousChildren} are the children of a Node that split on a continuous attribute.
+  \item[] \bb{DiscreteChildren} are the children of a Node that split on a discrete attribute.
 \end{enumerate}
@@
 This object is used to calculate the Euclidian distance between two continuous Vectors while classifying an new instance in a KNNModel.
-  \item[] \bb{Hamming} is an object which represents the Hamming distance function $\sum_{i=1}^{n}f_i(q, p)$ where $f_i(q, p) = 0$ if $q_i = p_i$ and $0$ otherwise.
+  \item[] \bb{Hamming} is an object which represents the Hamming distance function $\sum_{i=1}^{n}f_i(q, p)$ where $f_i(q, p) = 0$ if $q_i = p_i$ and $1$ otherwise.
 This object is used to calculate the Hamming distance between two discrete Vectors while classifying an new instance in a KNNModel.
@@
   \item[] \bb{Distribution} is an interface which all distribution objects must implement.
-  \item[] \bb{Gaussian} An object which reprints a Gaussian distribution. It is used by the Naïve Bayes classifier for continuous attributes.
+  \item[] \bb{Gaussian} An object which represents a Gaussian distribution. It is used by the Naïve Bayes classifier for continuous attributes.
 \end{enumerate}
@@
   \item[] \bb{Attribute} is an interface which the Continuous and Discrete attribute types must implement.
-  \item[] \bb{BayesException} is a runtime exception which is thrown when no Distribution is supplied and there are continuous attributes within the DataSet.
+  \item[] \bb{BayesException} is a runtime exception thrown when no Distribution is supplied and there are continuous attributes within the DataSet.
   \item[] \bb{ClassSummary} is the object created during the NaiveBayes learning process.
@@
   \item[] \bb{Discrete} represents a discrete attribute.
-It is parametrized by a map of attribute values to conditional probabilities and the sum of the class length and probability of an unseen value.
-The parameters of the discrete attribute were carefully chosen for performance reasons.
-Given a new value, the conditional probability $P(a_j|v_k)$ is found from the map.
+It is parametrized by a map of attribute values to conditional probabilities.
+Given a new value, the conditional probability $P(a_j|v_k)$ is found in the map.
   \item[] \bb{NaïveBayes} is the implementation of the Naïve Bayes algorithm. It is optionally parameterized by a Distribution. The algorithm create a ClassSummary for each distinct class.
@@
   \item[] \bb{KNNModel} is a trained KNN classifier.
-It is parameterized by the number of neighbors to use for the classification and a DataSet.
+It is parameterized by the number of neighbors $k$ and a DataSet.
 It classifies new samples by finding the $k$ closest neighbors and returning the most common classification.
@@
   \end{tabular}
-  \caption{Accuracy of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
+  \caption{The accuracies of the six implemented algorithms on the five UCI Machine Learning Repository datasets. Results were calculated using 10 times 5-fold cross validation.}
   \label{table:accuracies}
@@
   \end{tabular}
-  \caption{Standard deviation of the six implemented algorithms on five UCI Machine Learning repositories. Results calculated using 10 times 5-fold cross validation.}
+  \caption{The standard deviations of the six implemented algorithms on the five UCI Machine Learning Repository datasets. Results were calculated using 10 times 5-fold cross validation.}
 \end{table}
@@
 Furthermore, the letter recognition dataset likely expresses high correlation amongst the attributes.
-However, the two algorithms perform identically for the E Coli.
+However, the two algorithms perform almost identically on the E Coli.
 and breast cancer datasets.
 
-The AdaBoost algorithm when using either ID3 or Naïve Bayes as a base model either improved or maintained the same accuracy as their base models.
-For example, AdaBoost on ID3 improved the classification accuracy for E.
-Coli, letter recognition and breast cancer datasets; however, it maintains the same accuracy as the ID3 algorithm for the other datasets.
-Additionally, AdaBoost on Naïve Bayes improved the classification accuracy on the breast cancer and car datasets and maintained similar accuracies to Naïve Bayes on the other datasets.
-One exception to this is the letter dataset where AdaBoost on Naïve Bayes which scored 10\% lower.
-The random forest algorithm maintained a similar performance to the AdaBoost on ID3 algorithm.
-It outperformed AdaBoost on the car dataset; however, the standard deviation for each algorithm is too high to make any conclusions.
+The AdaBoost algorithms generally maintained or improved the accuracy as their base models.
+For example, AdaBoost on ID3 greatly improved the classification accuracy for the E.
+Coli and letter recognition datasets while maintaining similar performance on the other datasets.
+Additionally, AdaBoost on Naïve Bayes improved the classification accuracy on the car and mushroom datasets while maintaining similar accuracies on the others.
+One exception to this is the letter recognition dataset where AdaBoost on Naïve Bayes scored 10\% lower than regular Naïve Bayes.
+The random forest algorithm also improved the classification accuracy of ID3; however, it generally underperformed AdaBoost on ID3.
 
-I believe the classification accuracy for each ensemble algorithm, dataset pair could be improved given more time for hyperparameter tuning.
+I believe the classification accuracy for each algorithm, dataset pair could be improved given more time for hyperparameter tuning, especially the ensemble algorithms.
 The larger datasets proved extremely difficult for experimentation as they required much longer training times.
-When experimenting with various hyperparameters for the letter dataset, it often took more than 10 minutes to complete one 5-fold cross validation iteration.
-Optimization was considered during the algorithm implementations; however, training time was not drastically reduced.
+When experimenting with various hyperparameters for the letter dataset, it often took longer than 10 minutes to complete one 5-fold cross validation iteration.
+Although this is not an extremely long time, tuning became much more difficult.
+Optimization was considered after the initial algorithm implementations; however, training time was not drastically reduced.
 
 The most surprising results received were from the k-nearest neighbors algorithm.
-It almost always outperformed the other algorithms and even received the highest accuracy for the car dataset.
-An interesting feature of the hyperparameters for this classifier is that all $k$ values were set to $1$.
+It almost always outperformed the other algorithms and nearly received the highest accuracy for each.
+The amount of neighbors was set to $1$ for each dataset.
 This was an unexpected result of the hyperparameter search.
-The most prominent flaw with the k-nearest neighbors algorithm was the extremely long classification times, especially for the larger datasets.
+The most prominent flaw of the k-nearest neighbors algorithm was the extremely long classification times, especially for the larger datasets.
 
+\clearpage
 \bibliographystyle{plain}

### 2017-12-12 cs6735/assignment/code/Assignment.java
fixed accuracy

@@ -55,7 +55,7 @@ public class Assignment {
         algorithms.add(new ID3(ID3.MAX_LEVEL_NONE, 1));
         algorithms.add(new NaiveBayes());
         algorithms.add(new AdaBoost(new ID3(1), 100, 0.5));
-        algorithms.add(new AdaBoost(new NaiveBayes(), 100, 0.7));
+        algorithms.add(new AdaBoost(new NaiveBayes(), 100, 0.1));
         algorithms.add(new RandomForest(new ID3(), 120, 0.7));
         algorithms.add(new KNN(1, new Hamming()));
         datasetsAndAlgorithms.add(new Tuple<>(loadBreastCancerData(Assignment.class), algorithms));
